# Prerequisites {#prerequisites}

The analysis presented in this book requires a basic understanding of the 
`R` programing language. An introduction to `R` can be found [here](https://cran.r-project.org/doc/manuals/r-release/R-intro.pdf) and
in the book [R for Data Science](https://r4ds.had.co.nz/index.html).

Furthermore, it is beneficial to be familiar with single-cell data analysis
using the [Bioconductor](https://www.bioconductor.org/) framework. The 
[Orchestrating Single-Cell Analysis with Bioconductor](https://bioconductor.org/books/release/OSCA/) 
gives an excellent overview on data containers and basic analysis that are being
used here.

Before we get started on IMC data analysis, we will need to make sure that
software dependencies are installed and the needed example data is downloaded.

## Software requirements

```{r load-libraries, echo = FALSE, message = FALSE}
library(CATALYST)
library(SpatialExperiment)
library(SingleCellExperiment)
library(scuttle)
library(scater)
library(imcRtools)
library(cytomapper)
library(dittoSeq)
library(tidyverse)
```

Throughout the analysis, we rely on different R software packages.
This section lists the most commonly used packages in this workflow.

Data containers:

* [SpatialExperiment](https://bioconductor.org/packages/release/bioc/html/SpatialExperiment.html) version `r packageVersion("SpatialExperiment")`
* [SingleCellExperiment](https://bioconductor.org/packages/release/bioc/html/SingleCellExperiment.html) version `r packageVersion("SingleCellExperiment")`

Data processing:

* [CATALYST](https://bioconductor.org/packages/release/bioc/html/CATALYST.html) version `r packageVersion("CATALYST")`
* [imcRtools](https://github.com/BodenmillerGroup/imcRtools) version `r packageVersion("imcRtools")` from [Github](https://github.com/BodenmillerGroup/imcRtools)
* [scuttle](https://bioconductor.org/packages/release/bioc/html/scuttle.html) version `r packageVersion("scuttle")`
* [scater](https://bioconductor.org/packages/release/bioc/html/scater.html) version `r packageVersion("scater")`

Data visualization:

* [cytomapper](https://bioconductor.org/packages/release/bioc/html/cytomapper.html) version `r packageVersion("cytomapper")` from [Github](https://github.com/BodenmillerGroup/cytomapper)
* [dittoSeq](https://bioconductor.org/packages/release/bioc/html/dittoSeq.html) version `r packageVersion("dittoSeq")`

Tidy R:

* [tidyverse](https://www.tidyverse.org/) version `r packageVersion("tidyverse")`

## Download example data {#download-data}

TODO: Explain what the example data is (raw data, processed data).

Throughout this tutorial, we will access a number of different data types. 
To declutter the analysis scripts, we will already download all needed data here.

### Processed multiplexed imaging data

**Steinbock output**

**IMC Segmentation Pipeline output**

### Files for spillover matrix estimation

To highlight the estimation and correction of channel-spillover as described by
[@Chevrier2017], we can access an example spillover-acquisition from:

TODO: enter link here

```{r download-spillover-data}
# sm_url <- "https://data.mendeley.com/public-files/datasets/v58yj49pfr/files/b39223d2-2825-4e79-9875-86fa0e1c55d2/file_downloaded?dl=1"

#download.file(sm_url, "data/IMMUcan_Batch20201113_compensation_corrected.zip")
#unzip("data/IMMUcan_Batch20201113_compensation_corrected.zip", exdir="data", overwrite=TRUE)
#unlink("data/Figure_S5.zip")
```

## Software versions {#sessionInfo}

<details>
   <summary>SessionInfo</summary>
   
```{r, echo = FALSE, message = FALSE}
sessionInfo()
```
</details>



