# Spillover correction

**Original scripts:** *Vito Zanotelli*, **adapted/maintained by:** *Nils Eling*

This section highlights how to generate a spillover matrix from individually
acquired single metal spots on an agarose slide. Each spot needs to be imaged as
its own acquisition/ROI and individual .txt files containing the pixel
intensities per spot need to be available. For complete details on the spillover
correction approach, please refer to [the original
publication](https://www.cell.com/cell-systems/fulltext/S2405-4712(18)30063-2) [@Chevrier2017].

The original code is available on Github
[here](https://github.com/BodenmillerGroup/cyTOFcompensation), however, due to
changes in the
[CATALYST](https://bioconductor.org/packages/release/bioc/html/CATALYST.html)
package, users were not able to reproduce the analysis using the newest software
versions. The following workflow uses the newest package versions to generate a
spillover matrix.

In brief, the highlighted workflow comprises 5 steps:

1. Reading in the data
2. Quality control 
3. (Optional) pixel binning
4. "Debarcoding" for pixel assignment
5. Pixel selection for spillover matrix estimation
6. Spillover matrix generation
7. Saving the results

## Generate the spillover matrix

In the first step, we will generate a spillover matrix based on the single-metal
spots and save it for later use.

### Read in the data

Here, we will read in the individual .txt files into a `SingleCellExperiment`
object. This object can be used directly by the `CATALYST` package to estimate
the spillover.

For this to work, the .txt file names need to contain the spotted metal isotope
name. By default, the first occurrence of the isotope in the format `(mt)(mass)`
(e.g. `Sm152` for Samarium isotope with the atomic mass 152) will be used as
spot identifier. Alternatively, a named list of already read-in pixel intensities
can be provided. For more inforation, please refer to the man page `?readSCEfromTXT`.

For further downstream analysis, we will asinh-transform the data using a
cofactor of 5; a common transformation for CyTOF data [@Bendall2011].

```{r read-txts, message=FALSE}
library(imcRtools)

# Create SingleCellExperiment from .txt files
sce <- readSCEfromTXT("data/Figure_S5/Spillover_Matrix_2/") 
assay(sce, "exprs") <- asinh(counts(sce)/5)
```

### Quality control

In the next step, we will observe the median pixel intensities per spot and
threshold on medians < 200 counts.
These types of visualization serve two purposes:

1. Small median pixel intensities (< 200 counts) might hinder the robust
estimation of the channel spillover. In that case, consecutive pixels can be
summed (see [Optional pixel binning](#pixel_binning)).

2. Each spotted metal (row) should show the highest median pixel intensity in its
corresponding channel (column). If this is not the case, either the naming of the
.txt files was incorrect or the incorrect metal was spotted.

```{r QC-heatmap, message = FALSE, fig.width=7, fig.height=7}
# Log10 median pixel counts per spot and channel
plotSpotHeatmap(sce)

# Thresholded on 200 pixel counts
plotSpotHeatmap(sce, log = FALSE, threshold = 200)
```

As we can see, all median pixel intensities are > 200 counts for each spot.
We also observe acquired channels for which no spot was placed (Xe134, Ir191, Ir193). 

### Optional pixel binning {#pixel_binning}

In cases where median pixel intensities are low (< 200 counts), consecutive
pixels can be summed to increase the robustness of the spillover estimation.
The `imcRtools` package provides the `binAcrossPixels` function,
which performs aggregation for each channel across `bin_size` consecutive pixels 
per spotted metal.

```{r binning, message=FALSE, fig.width=7, fig.height=7}
# Define grouping
bin_size = 10

sce2 <- binAcrossPixels(sce, bin_size = bin_size)

# Log10 median pixel counts per spot and channel
plotSpotHeatmap(sce2)

# Thresholded on 200 pixel counts
plotSpotHeatmap(sce2, log = FALSE, threshold = 200)
```

Here, we can see an increase in the median pixel intensities and accumulation of
off-diagonal signal. Due to already high original pixel intensities, we will
refrain from aggregating across consecutive pixels for this demonstration.

### Filtering incorrectly assigned pixels

The following step uses functions provided by the `CATALYST` package to
"debarcode" the pixels. Based on the intensity distribution of all channel,
pixels are assigned to their corresponding barcode; here this is the already
known metal spot. This procedure serves the purpose to identify pixels that
cannot be robustly assigned to the spotted metal. Pixels of such kind can be
regarded as "noisy", "background" or "artefacts" that should be removed prior to
spillover estimation.

We will also need to specify which channels were spotted (argument `bc_key`).
This information is directly contained in the `colData(sce)` slot.
To facilitate visualization, we will order the `bc_key` by mass.

The general workflow for pixel debarcoding is as follows:

1. assign a preliminary metal mass to each pixel
2. for each pixel, estimate a cutoff parameter for the distance between 
positive and negative pixel sets
3. apply the estimated cutoffs to identify truly positive pixels

```{r debarcoding, message=FALSE}
library(CATALYST)

bc_key <- as.numeric(unique(sce$sample_mass))
bc_key <- bc_key[order(bc_key)]

sce <- assignPrelim(sce, bc_key = bc_key)
sce <- estCutoffs(sce)
sce <- applyCutoffs(sce)
```

The obtained `SingleCellExperiment` now contains the additional `bc_id` entry.
For each pixel, this vector indicates the assigned mass (e.g. `161`) or
`0`, meaning unassigned. 

This information can be visualized in form of a heatmap:

```{r assignment-heatmap, fig.width=7, fig.height=7}
library(pheatmap)
cur_table <- table(sce$bc_id, sce$sample_mass)

pheatmap(log10(cur_table + 1),
         cluster_rows = FALSE,
         cluster_cols = FALSE)
```

We can see here, that all pixels were assigned to the right mass and that all
pixel sets are made up if > 1000 pixels.

However, in cases where incorrect assignment occurred or where few pixels were
measured for some spots, the `imcRtools` package exports a simple helper
function to exclude pixels based on these criteria:

```{r pixel-filtering}
sce <- filterPixels(sce, minevents = 40, correct_pixels = TRUE)
```

### Compute spillover matrix

Based on the single-positive pixels, we use the `CATALYST::computeSpillmat()`
function to compute the spillover matrix and `CATALYST::plotSpillmat()` to
visualize it:

```{r compute-spillover, fig.width=7, fig.height=7}
sce <- computeSpillmat(sce)

plotSpillmat(sce)
```

As we can see, the largest spillover appears in `In113 --> In115` and we also
observe the `+16` oxide impurities for e.g. `Nd148 --> Dy164`.

Please follow the [CATALYST vignette](https://bioconductor.org/packages/release/bioc/vignettes/CATALYST/inst/doc/preprocessing.html#compensation)
to learn how to apply this spillover matrix for single-cell based spillover
compensation. Here, we will save the spillover matrix as .csv and as image for
use in the [IMC segmentation
pipeline](https://github.com/BodenmillerGroup/ImcSegmentationPipeline) as part
of the `CorrectSpilloverApply` and `CorrectSpilloverMeasurements` module
[here](https://github.com/BodenmillerGroup/ImcPluginsCP).

### Save spillover matrix as csv

Next, we will write out the spillover matrix as .csv file for possible later use.

```{r write_sm_csv}
cur_sm <- metadata(sce)$spillover_matrix
write.csv(cur_sm, "data/Figure_S5/new_version_Spillover_Matrix_2_sm.csv")
```

### Save spillover matrix as image

When using the [ImcPluginsCP](https://github.com/BodenmillerGroup/ImcPluginsCP)
CellProfiler modules for spillover correction, the spillover matrix needs to 
be saved as 32-bit .tiff image.

For this to work, the channels need to be ordered in the same way that
CellProfiler orders them. When using the [IMC segmentation pipeline](https://github.com/BodenmillerGroup/ImcSegmentationPipeline), for each
image, the order of the channels is written out as .csv file. This file contains
a single column listing the metal isotopes in the correct order. Here, we will
read this file in. 

```{r read-metal-order}
ordered_chs <- read.csv("data/Figure_4/IMC_image/analysis/imc_example_image_a0_full.csv",
                        header = FALSE)
ordered_chs$V1 <- paste0(ordered_chs$V1, "Di")
head(ordered_chs)
```

The `CATALYST` package provides the `adaptSpillmat` function that corrects the
spillover matrix in a way that rows and columns match a predefined set of metals.
Please refer to `?compCytof` for more information how metals in the spillover
matrix are matched to acquired channels in the `SingleCellExperiment` object.

```{r adaptSM}
adapted_sm <- CATALYST::adaptSpillmat(cur_sm, 
                                      out_chs = as.character(ordered_chs$V1))
```

The adapted spillover matrix can now be saved as .tiff image for the use with CellProfiler.

```{r save-sm-as-tiff, message=FALSE}
library(tiff)
writeTIFF(adapted_sm, "data/Figure_4/new_imc_full_sm.tiff", 
          bits.per.sample = 32)
```

## Compensate the mean pixel intensities

**This section is under development**

## Compensate images

**This section is under development**

```{r integration-test-original_sm, include = FALSE}
library(testthat)
correct_sm <- as.matrix(read.csv("data/Figure_S5/paper_version_Spillover_Matrix_2_sm.csv", row.names = 1))
current_sm <- metadata(sce)$spillover_matrix
correct_sm <- correct_sm[rownames(current_sm), colnames(current_sm)]

expect_equal(correct_sm, current_sm, tolerance = 0.001)
```

```{r integration-test-tiff_sm, include = FALSE}
correct_sm <- readTIFF("data/Figure_4/IMC_image/analysis/imc_full_sm.tiff")
current_sm <- adapted_sm
dimnames(current_sm) <- NULL

expect_equal(correct_sm, current_sm, tolerance = 0.0005)
```

## Session Info

<details>
   <summary>SessionInfo</summary>
   
```{r, echo = FALSE}
sessionInfo()
```
</details>

