# Spillover correction

**Original scripts:** *Vito Zanotelli*, **adapted/maintained by:** *Nils Eling*

This section highlights how to generate a spillover matrix from individually
acquired single metal spots on an agarose slide. Each spot needs to be imaged as
its own acquisition/ROI and individual TXT files containing the pixel
intensities per spot need to be available. For complete details on the spillover
correction approach, please refer to [the original
publication](https://www.cell.com/cell-systems/fulltext/S2405-4712(18)30063-2) [@Chevrier2017].

**Spillover slide preparation:**  

* Prepare 2% agarose in double distilled H$_2$O in a beaker and melt it in a microwave until well dissolved. 
* Dip a blank superfrost plus glass microscope slide into the agarose and submerge it until the label. 
* Remove the slide and prop it up against a support to allow the excess agarose to run off onto paper towels.  
* Allow the slide to dry completely (at least 30 minutes).  
* Retrieve all the antibody conjugates used in the panel for which the spillover matrix is to be generated and place them on ice. 
* Arrange them in a known order (e.g., mass of the conjugated metal).  
* Pipette 0.3 µl spots of 0.4% trypan blue dye into an array on the slide. Prepare one spot per antibody, and make sure the spots are well separated. 
* Pipette 0.3 µl of each antibody conjugate (usually at 0.5 mg/ml) onto a unique blue spot, taking care to avoid different antibodies bleeding into each other. Note the exact location of each conjugate on the slide. 
* Let the spots dry completely, at least 1 hour. 

**Spillover slide acquisition:**  

* Create a JPEG or PNG image of the slide using a mobile phone camera or flat-bed scanner.  
* In the CyTOF software, create a new file and import the slide image into it. 
* Create a panorama across all the spots to visualize their locations.  
* Within each spot, create a region of interest (ROI) with a width of 200 pixels and a height of 10 pixels.  
* Name each ROI with the mass and name of the metal conjugate contained in the spot, e.g "Ir193" or "Ho165". This will be how each TXT file is named. 
* Set the profiling type of each ROI to "Local".  
* Apply the antibody panel to all the ROIs. This panel should contain all (or more) of the isotopes in the panel, with the correct metal specified. For example: if the metal used is Barium 138, make sure this, rather than Lanthanum 138, is selected. 
* Save the file, make sure "Generate Text File" is selected, and start the acquisition. 

This procedure will generate an MCD file similar to the one available on zenodo:
[10.5281/zenodo.5949115](https://doi.org/10.5281/zenodo.5949115)

The original code of the spillover correction manuscript is available on Github
[here](https://github.com/BodenmillerGroup/cyTOFcompensation); however, due to
changes in the
[CATALYST](https://bioconductor.org/packages/release/bioc/html/CATALYST.html)
package, users were not able to reproduce the analysis using the newest software
versions. The following workflow uses the newest package versions to generate a
spillover matrix and perform spillover correction.

In brief, the highlighted workflow comprises 9 steps:

1. Reading in the data
2. Quality control 
3. (Optional) pixel binning
4. "Debarcoding" for pixel assignment
5. Pixel selection for spillover matrix estimation
6. Spillover matrix generation
7. Saving the results
8. Single-cell compensation
9. Image compensation

## Generate the spillover matrix

In the first step, we will generate a spillover matrix based on the single-metal
spots and save it for later use.

### Read in the data

Here, we will read in the individual TXT files into a `SingleCellExperiment`
object. This object can be used directly by the `CATALYST` package to estimate
the spillover.

For this to work, the TXT file names need to contain the spotted metal isotope
name. By default, the first occurrence of the isotope in the format `(mt)(mass)`
(e.g. `Sm152` for Samarium isotope with the atomic mass 152) will be used as
spot identifier. Alternatively, a named list of already read-in pixel intensities
can be provided. For more information, please refer to the man page `?readSCEfromTXT`.

For further downstream analysis, we will asinh-transform the data using a
cofactor of 5; a common transformation for CyTOF data [@Bendall2011].
As the pixel intensities are larger than the cell intensities, the cofactor
here is larger than the cofactor when transforming the mean cell intensities.

```{r read-txts, message=FALSE}
library(imcRtools)

# Create SingleCellExperiment from TXT files
sce <- readSCEfromTXT("data/compensation/") 
assay(sce, "exprs") <- asinh(counts(sce)/5)
```

### Quality control

In the next step, we will observe the median pixel intensities per spot and
threshold on medians < 200 counts.
These types of visualization serve two purposes:

1. Small median pixel intensities (< 200 counts) might hinder the robust
estimation of the channel spillover. In that case, consecutive pixels can be
summed (see [Optional pixel binning](#pixel_binning)).

2. Each spotted metal (row) should show the highest median pixel intensity in its
corresponding channel (column). If this is not the case, either the naming of the
TXT files was incorrect or the incorrect metal was spotted.

```{r QC-heatmap, message = FALSE, fig.width=7, fig.height=7}
# Log10 median pixel counts per spot and channel
plotSpotHeatmap(sce)

# Thresholded on 200 pixel counts
plotSpotHeatmap(sce, log = FALSE, threshold = 200)
```

As we can see, nearly all median pixel intensities are > 200 counts for each spot.
We also observe acquired channels for which no spot was placed (e.g., Xe134, Ir191, Ir193). 

### Optional pixel binning {#pixel_binning}

In cases where median pixel intensities are low (< 200 counts), consecutive
pixels can be summed to increase the robustness of the spillover estimation.
The `imcRtools` package provides the `binAcrossPixels` function,
which performs aggregation for each channel across `bin_size` consecutive pixels 
per spotted metal.

```{r binning, message=FALSE, fig.width=7, fig.height=7}
# Define grouping
bin_size = 10

sce2 <- binAcrossPixels(sce, bin_size = bin_size)

# Log10 median pixel counts per spot and channel
plotSpotHeatmap(sce2)

# Thresholded on 200 pixel counts
plotSpotHeatmap(sce2, log = FALSE, threshold = 200)
```

Here, we can see an increase in the median pixel intensities and accumulation of
off-diagonal signal. Due to already high original pixel intensities, we will
refrain from aggregating across consecutive pixels for this demonstration.

### Filtering incorrectly assigned pixels

The following step uses functions provided by the `CATALYST` package to
"debarcode" the pixels. Based on the intensity distribution of all channels,
pixels are assigned to their corresponding barcode; here this is the already
known metal spot. This procedure serves the purpose to identify pixels that
cannot be robustly assigned to the spotted metal. Pixels of such kind can be
regarded as "noisy", "background" or "artefacts" that should be removed prior to
spillover estimation.

We will also need to specify which channels were spotted (argument `bc_key`).
This information is directly contained in the `colData(sce)` slot.
To facilitate visualization, we will order the `bc_key` by mass.

The general workflow for pixel debarcoding is as follows:

1. assign a preliminary metal mass to each pixel
2. for each pixel, estimate a cutoff parameter for the distance between 
positive and negative pixel sets
3. apply the estimated cutoffs to identify truly positive pixels

```{r debarcoding, message=FALSE}
library(CATALYST)

bc_key <- as.numeric(unique(sce$sample_mass))
bc_key <- bc_key[order(bc_key)]

sce <- assignPrelim(sce, bc_key = bc_key)
sce <- estCutoffs(sce)
sce <- applyCutoffs(sce)
```

The obtained `SingleCellExperiment` now contains the additional `bc_id` entry.
For each pixel, this vector indicates the assigned mass (e.g. `161`) or
`0`, meaning unassigned. 

This information can be visualized in form of a heatmap:

```{r assignment-heatmap, fig.width=7, fig.height=7}
library(pheatmap)
cur_table <- table(sce$bc_id, sce$sample_mass)

# Visualize the correctly and incorrectly assigned pixels
pheatmap(log10(cur_table + 1),
         cluster_rows = FALSE,
         cluster_cols = FALSE)

# Compute the fraction of unassigned pixels per spot
cur_table["0",] / colSums(cur_table)
```

We can see here, that all pixels were assigned to the right mass and that all
pixel sets are made up of > 800 pixels.

However, in cases where incorrect assignment occurred or where few pixels were
measured for some spots, the `imcRtools` package exports a simple helper
function to exclude pixels based on these criteria:

```{r pixel-filtering}
sce <- filterPixels(sce, minevents = 40, correct_pixels = TRUE)
```

In the `filterPixels` function, the `minevents` parameter specifies the threshold
under which correctly assigned pixel sets are excluded from spillover
estimation. The `correct_pixels` parameter indicates whether pixels that were
assigned to masses other than the spotted mass should be excluded from spillover
estimation. The default values often result in sufficient pixel filtering;
however, if very few pixels (~100) are measured per spot, the `minevents`
parameter value needs to be lowered.

### Compute spillover matrix

Based on the single-positive pixels, we use the `CATALYST::computeSpillmat()`
function to compute the spillover matrix and `CATALYST::plotSpillmat()` to
visualize it. The `plotSpillmat` function checks the spotted and acquired
metal isotopes against a pre-defined `CATALYST::isotope_list()`. In this data,
the `Ar80` channel was additionally acquired to check for deviations in signal
intensity. `Ar80` needs to be added to a custom `isotope_list` object for
visualization.

```{r compute-spillover, fig.width=7, fig.height=7}
sce <- computeSpillmat(sce)

isotope_list <- CATALYST::isotope_list
isotope_list$Ar <- 80

plotSpillmat(sce, isotope_list = isotope_list)

# Save spillover matrix in variable
sm <- metadata(sce)$spillover_matrix
```

**Of note: the visualization of the spillover matrix using CATALYST does currently
not visualize spillover between the larger channels.** In this case, the 
spillover matrix is clipped at Yb171.

As we can see, the largest spillover appears in `In113 --> In115` and we also
observe the `+16` oxide impurities for e.g. `Nd148 --> Dy164`.

We can save the spillover matrix for external use.

```{r save-sm, message=FALSE}
write.csv(sm, "data/sm.csv")
```

## Single-cell data compensation

The `CATALYST` package can be used to perform spillover compensation on the
**single-cell mean intensities**. Here, the `SpatialExperiment` object generated
in Section \@ref(read-data) is read in. The `CATALYST` package requires an entry
to `rowData(spe)$channel_name` for the `compCytof` function to run. This entry
should contain the metal isotopes in the form (mt)(mass)Di (e.g., `Sm152Di` for
Samarium isotope with the atomic mass 152). 

The `compCytof` function performs channel spillover compensation on the mean
pixel intensities per channel and cell. Here, we will not overwrite the assays
in the `SpatialExperiment` object to later highlight the effect of compensation.
As shown in Section \@ref(read-data), also the compensated counts are
asinh-transformed using a cofactor of 1.

```{r single-cell-compensation}
spe <- readRDS("data/spe.rds")
rowData(spe)$channel_name <- paste0(rowData(spe)$channel, "Di")

spe <- compCytof(spe, sm, 
                 transform = TRUE, cofactor = 1,
                 isotope_list = isotope_list, 
                 overwrite = FALSE)
```

To check the effect of channel spillover compensation, the expression of markers
that are affected by spillover (e.g., E-cadherin in channel Yb173 and CD303 in
channel Yb174) can be visualized in form of scatter plots before and after
compensation.

```{r visualize-single-cell-spillover, message=FALSE}
library(dittoSeq)
library(patchwork)
before <- dittoScatterPlot(spe, x.var = "Ecad", y.var = "CD303",
                           assay.x = "exprs", assay.y = "exprs") +
    ggtitle("Before compensation")

after <- dittoScatterPlot(spe, x.var = "Ecad", y.var = "CD303",
                          assay.x = "compexprs", assay.y = "compexprs") +
    ggtitle("After compensation")
before + after
```

We observe that the spillover Yb173 --> Yb174 was successfully corrected.
To facilitate further downstream analysis, the non-compensated assays can now be
replaced by their compensated counterparts:

```{r overwrite-assays}
assay(spe, "counts") <- assay(spe, "compcounts") 
assay(spe, "exprs") <- assay(spe, "compexprs") 
assay(spe, "compcounts") <- assay(spe, "compexprs") <- NULL
```

## Image compensation

The [cytomapper](https://github.com/BodenmillerGroup/cytomapper) package allows channel
spillover compensation directly on **multi-channel images**. 
The `compImage` function takes a `CytoImageList` object and the estimated
spillover matrix as input. More info on how to work with `CytoImageList`
objects can be seen in Section \@ref(image-visualization).

At this point, we can read in the `CytoImageList` object containing multi-channel
images as generated in Section \@ref(read-data).
The `channelNames` need to be set according to their metal isotope in the form
(mt)(mass)Di and therefore match `colnames(sm)`.

```{r read-in-image, message=FALSE}
library(cytomapper)

images <- readRDS("data/images.rds")
channelNames(images) <- rowData(spe)$channel_name
```

The CATALYST package provides the `adaptSpillmat` function that corrects the
spillover matrix in a way that rows and columns match a predefined set of
metals. Please refer to `?compCytof` for more information how metals in the
spillover matrix are matched to acquired channels in the `SingleCellExperiment`
object.

The spillover matrix can now be adapted to exclude channels that were not kept
for downstream analysis.

```{r}
adapted_sm <- adaptSpillmat(sm, channelNames(images), 
                            isotope_list = isotope_list)
```

The adapted spillover matrix now matches the `channelNames` of the
`CytoImageList` object and can be used to perform pixel-level spillover
compensation. Here, we parallelise the image compensation on all available minus 2 cores. When
working on Windows, you will need to use the `SnowParam` function instead of
`MultiCoreParam`.

```{r image-compensation, message = FALSE}
library(BiocParallel)

images_comp <- compImage(images, adapted_sm, 
                         BPPARAM = MulticoreParam())
```

As a sanity check, we will visualize the image before and after compensation:

```{r image-visualization}
# Before compensation
plotPixels(images[5], colour_by = "Yb173Di", 
           image_title = list(text = "Yb173 (Ecad) - before", position = "topleft"), 
           legend = NULL, bcg = list(Yb173Di = c(0, 4, 1)))
plotPixels(images[5], colour_by = "Yb174Di", 
           image_title = list(text = "Yb174 (CD303) - before", position = "topleft"), 
           legend = NULL, bcg = list(Yb174Di = c(0, 4, 1)))

# After compensation
plotPixels(images_comp[5], colour_by = "Yb173Di",
           image_title = list(text = "Yb173 (Ecad) - after", position = "topleft"), 
           legend = NULL, bcg = list(Yb173Di = c(0, 4, 1)))
plotPixels(images_comp[5], colour_by = "Yb174Di", 
           image_title = list(text = "Yb174 (CD303) - after", position = "topleft"),
           legend = NULL, bcg = list(Yb174Di = c(0, 4, 1)))
```

For convenience, we will re-set the `channelNames` to their biological targtes:

```{r re-set-channels}
channelNames(images_comp) <- rownames(spe)
```

```{r, include=FALSE}
rm(images)
```

## Write out compensated images

In the final step, the compensated images are written out as 16-bit TIFF
files:

```{r write-images, message=FALSE, results='hide', error=TRUE}
library(tiff)
dir.create("data/comp_img")
lapply(names(images_comp), function(x){
  writeImage(as.array(images_comp[[x]])/(2^16 - 1), 
             paste0("data/comp_img/", x, ".tiff"),
             bits.per.sample = 16)
})
```

## Save objects

For further downstream analysis, the compensated `SpatialExperiment` and
`CytoImageList` objects are saved replacing the former objects:

```{r save-objects-spill, error=TRUE}
saveRDS(spe, "data/spe.rds")
saveRDS(images_comp, "data/images.rds")
```

```{r testing, include = FALSE}
library(testthat)

expect_equal(assayNames(spe), c("counts", "exprs"))

expect_equal(as.vector(counts(spe)[, 1:5]), c(0.575106422106415, 3.12546056341781, 0, 2.03477470080057, 0.124981637293892, 
4.05394642526013, 2.03407155895996, 7.24215554765113, 1.0932749542015, 
2.14923853310107, 10.7293431375289, 1.27514025145857, 6.52606181633078, 
3.46455915152879, 0.847209433500473, 1.69084576947787, 2.85285833110381, 
1.06100223993509, 3.93635664758419, 4.50457032420379, 4.24048433325923, 
2.28153928389187, 3.53594279997212, 7.75006023879224, 1.56712491053119, 
2.02848897940089, 0.88061556449426, 4.54846086364113, 11.1211535613305, 
65.1236444925541, 5.13622944056114, 4.64871219577157, 6.84274090332239, 
16.8591260008099, 139.855974735937, 2.20420624806308, 1.44860060661138, 
0, 75.1953114668528, 142.235328356425, 0.416666666666647, 11.3597883482774, 
0.651920023480555, 2.58805358409882, 0.498412651740732, 7.57204860917109, 
1.17800997057393, 8.75006675928456, 1.76187446947939, 6.24727775117516, 
11.7321311159045, 1.23112744116456, 11.4595183792866, 6.02148249707505, 
1.37462818879883, 1.09913163841707, 1.49827531188507, 1.67776849835344, 
2.17294068252018, 4.60638133280225, 4.78351446504898, 4.27064819622529, 
2.74480618140905, 11.9576644455689, 2.03321792063284, 2.62025884977045, 
1.59864823765644, 18.8596672046382, 4.50995406829917, 144.358529484433, 
3.72116723333359, 4.45816692334628, 7.07007557018944, 30.6167835053301, 
64.6082616341566, 0.719037974767079, 9.22149099525802, 0.520891737749721, 
73.576642965277, 129.302666882674, 0.497549358536219, 2.37874742793283, 
0, 2.29430737214929, 0.954340069362395, 13.1133917091627, 2.14480578312121, 
4.90445182963192, 1.24572625487141, 8.15775848329467, 10.4145660680798, 
1.07247184034205, 16.4943583937027, 4.97409832155597, 1.52338688060226, 
0.911098298193017, 2.91043343182068, 1.58728689686045, 1.18552032666124, 
3.50302988793065, 4.7467558961812, 1.84685703862674, 3.49590967824283, 
6.72180429147077, 1.26211941470369, 1.1621873937194, 1.94629053537765, 
17.8010040232964, 6.333672314951, 57.989573490226, 4.06623546359915, 
5.39811023409794, 7.37949670964192, 21.8390462140383, 106.231635235582, 
0.674928321743819, 4.14857273346801, 0.575560560053978, 71.2559066660264, 
119.832059299245, 0.890154048800461, 7.71296111742655, 0.501317439202833, 
15.6290833055973, 0.543961487556748, 138.350558325953, 2.27033926757904, 
5.31429689853498, 1.4059103198355, 19.5075144690285, 15.4594645946615, 
0.726400170906667, 86.6936506212141, 6.76163911360482, 4.30316030769258, 
1.53262713193679, 16.6918445379505, 2.39619794635051, 2.53020240520715, 
8.55460688650394, 7.00578577802601, 4.0629296895003, 4.21283728283173, 
24.5015444320026, 1.50262589595442, 2.55508961502349, 9.27390355359496, 
3.99562569286061, 16.9025516879736, 10.0523651197176, 4.69582878529041, 
15.0100917583645, 23.9408730335394, 75.8952435757283, 94.4443218517994, 
2.20895788367862, 6.57925846749339, 0.658265045477455, 59.181262900432, 
99.8480299214522, 0.181818181818181, 1.45127152854746, 0.168344887080694, 
0.608421959660271, 0.179363735216379, 5.87150119635366, 0.661623123689662, 
8.71591777384505, 1.08049948081296, 0.520019263953429, 6.4976994502295, 
0.545180653987267, 2.8164432186119, 5.73337821956446, 1.9111959163043, 
0.613063990762242, 0.281463365611794, 0.522461153582682, 1.8556326229401, 
2.89671016374663, 2.04796288879988, 2.18996071968542, 1.75072339353548, 
2.40066248566611, 1.27977085187346, 1.79191670398777, 1.97108668105786, 
1.37455029016178, 2.84954434286801, 0.832643667575474, 2.79187948320988, 
1.28959897714697, 3.98418936239011, 5.28076639113396, 74.1324628235861, 
0.9253804562018, 1.26404029907818, 0.132927853156696, 10.164272275838, 
12.8066278804432))

expect_equal(as.vector(assay(spe, "exprs")[, 1:5]), c(0.547361972030769, 1.85739120590678, 0, 1.4590799040046, 0.124658525993827, 
2.10771411298377, 1.45876972756069, 2.67779889847326, 0.945815593369642, 
1.50845209315985, 3.06829414720948, 1.06320223889123, 2.5747698235456, 
1.95593827263519, 0.769109726633635, 1.29616974314404, 1.77085979502395, 
0.923857679644378, 2.07916006269261, 2.21033867166338, 2.15144639341539, 
1.56289282844126, 1.97554812629072, 2.74498431392133, 1.23142981840737, 
1.45630402004209, 0.794388991645488, 2.21980676135235, 3.10401144464935, 
4.86949380839468, 2.33881104905663, 2.24111011760825, 2.62163253244378, 
3.51891770392935, 5.63377310289589, 1.53139967523187, 1.1659095892332, 
0, 5.01328027299006, 5.65064246551019, 0.405465108108147, 3.12515866853811, 
0.612833438933858, 1.67944602661283, 0.479791607073098, 2.72194285715744, 
1.00181897895256, 2.86545788904241, 1.33177412879387, 2.53163788289854, 
3.15728987321107, 1.03574892380014, 3.13386618971081, 2.49530541585996, 
1.12314596808388, 0.949762680353855, 1.19380615152883, 1.28949355746997, 
1.51840585012769, 2.232168866198, 2.26907348679391, 2.15834656632067, 
1.73450115306095, 3.17626348790025, 1.45839304663909, 1.69099106822525, 
1.24826667759625, 3.63087493723713, 2.21150477646422, 5.66545917013447, 
2.02476870658448, 2.20023241106199, 2.6539826433656, 4.11496211178483, 
4.8615493581869, 0.66819333216633, 2.91761097234615, 0.499819464750524, 
4.99152098236756, 5.55531804421915, 0.479018831081479, 1.60123286608999, 
0, 1.56800637877874, 0.848715837498785, 3.26823181396784, 1.50658053490075, 
2.29352555195463, 1.04492043967795, 2.79585225185085, 3.03864959131559, 
0.931701947652182, 3.4970832253877, 2.30734591156441, 1.20766630168915, 
0.817093506230501, 1.78973594426823, 1.24222608814223, 1.00667036562408, 
1.96655251295532, 2.26152383910993, 1.37297271350709, 1.96459616636674, 
2.60399152561986, 1.05514163160341, 0.991539192666868, 1.41935458538892, 
3.57319006281633, 2.54520194960983, 4.75348474226405, 2.1106530723543, 
2.387667157982, 2.69641210652631, 3.77737041793074, 5.35879128083352, 
0.632006120108253, 2.13013076132081, 0.547755610339449, 4.95947413097012, 
5.47925584663204, 0.801530560849474, 2.74022551398308, 0.48238986791444, 
3.44330257094523, 0.520182669200208, 5.62295098318641, 1.55838747878086, 
2.37228475869318, 1.14141255501909, 3.66460323861465, 3.43241300074073, 
0.674160304416511, 5.15556108941629, 2.60983629562226, 2.16573236703522, 
1.21272628454337, 3.50896351133545, 1.60797459633989, 1.65838999892952, 
2.84301593519032, 2.64493866242313, 2.10986331107627, 2.14508099421734, 
3.89229951489402, 1.19621892018722, 1.66749882239005, 2.9232457718972, 
2.09365107560374, 3.52148568741842, 3.00342001332098, 2.25097116664323, 
3.40297771454293, 3.86917023676443, 5.02254459530079, 5.24118568124364, 
1.53336105194387, 2.58279527719055, 0.618140996920859, 4.77382353882958, 
5.29682158506151, 0.18083104406935, 1.16742600509862, 0.167559710742631, 
0.576033240430446, 0.178415668447857, 2.4704316194559, 0.620943752549097, 
2.86157292946877, 0.937165560133545, 0.49904553569216, 2.57046480248775, 
0.521253367401973, 1.75874499865655, 2.44697212382536, 1.40320082428437, 
0.579994849530276, 0.27787359172362, 0.501210920774003, 1.37714348531497, 
1.78526719983685, 1.46488165283259, 1.52549833795289, 1.32625661469155, 
1.60969268465267, 1.06605656338623, 1.34650839614044, 1.43062976594636, 
1.12310014135671, 1.76976298580441, 0.757956231425614, 1.7504941575978, 
1.07209346765007, 2.09087075448086, 2.36606512303493, 4.99904619936365, 
0.827613431193833, 1.05633397553219, 0.13253946512478, 3.01443714170894, 
3.24463084707751))

expect_equal(as.array(images_comp$Patient1_001)[1:10,1:10,],
             structure(c(0, 0, 0, 1.01836941657218e-14, 1.76359105110167, 
0, 1, 0, 1, 0, 0, 0, 5.87724313660942e-15, 1.68342781066894, 
0.999999999999991, 2, 0, 0, 0, 0, 3.87602276667002e-16, 3.06884312629699, 
0, 0, 0, 0, 0.999999999999995, 7.91033905045424e-16, 0, 0, 0, 
0, 0, 1.68342781066895, 9.43689570931383e-16, 0, 0, 0, 2.69882869720458, 
0, 0, 1, 0, 0, 0, 1, 0, 2, 0, 0, 1, 1.2024484872818, 0, 0, 0, 
1.45751466451571e-14, 3.45903861109775e-15, 0, 2.51014486973844e-15, 
1.63150742915619e-15, 0, 0, 0, 0, 1, 1, 0, 0, 1, 0, 0, 2.49638032913208, 
0, 1, 0, 0, 0.999999999999994, 0, 0, 0.999999999999998, 0, 4.17980813980103, 
0, 2.25589060783386, 0, 1.00000000000003, 0, 6.18949336228525e-15, 
5.01551924991794e-15, 0, 0, 1, 1.68342781066895, 3.27168847569226e-15, 
1.00000000000001, 0, 0, 0.99999999999999, 0, 0, 21.6329703311034, 
35.9079054423042, 21.2939852959344, 11.2590744332055, 2.49452284180398, 
11.0606184005737, 15.4343643188477, 29.8051862774271, 23.5386071963338, 
21.2102621850598, 1.47484206173012, 6.20999037303417, 5.10317705332791, 
3.00000000000002, 0.992000324397243, 1.00000000000001, 3.74314810516246, 
2.60933607362433, 2.4952047039044, 5.04781590546332, 1.38975499014332, 
6.1512201511788, 8.6331272125244, 2.20082473754882, 0.992682186497657, 
5.92568486014062, 0, 1, 2.35407485886391, 1.0210445042747, 1.13449389363855, 
13.5759449005127, 6.88769769668582, 5.66034412384036, 1.99039211250834e-15, 
3.09149583060116, 0.992000324397234, 1.50320437950717, 1, 2.34446740150452, 
1.98400064879446, 14.6341939145998, 22.1778970956018, 7.00206184387207, 
9.37512016296387, 0.992000324397245, 3.17223358154297, 5.05845365594837e-15, 
2.89227762580572, 1.68962066560141e-15, 0, 27.1825447082519, 
13.3472166061401, 7.57457065582275, 8.64710695369496, 6.80559963763048, 
5.55697461078332, 2.21226315172301, 0, 1.19121852919265, 2.80719055421891, 
43.384441041151, 18.9405937182388, 25.3875154053178, 10.0020618438721, 
3.96800129758891, 0, 0.99200032439723, 1.71740430541084e-15, 
8.88178419700125e-16, 1.60109972953796, 25.4949836730957, 31.6778288440622, 
14.9698649722482, 10.2056710619988, 6.32275801855326, 3.00000000000001, 
1.00000000000001, 1, 3.93088339656345e-15, 2.72555864364748e-15, 
25.0404483246627, 16.4643306732178, 11.371256495651, 8.08783531188967, 
2.97668283529211, 4.90464047412159, 0, 0, 1.98400064879447, 0, 
11.9448795318603, 5.34378004074097, 7.7125131269522, 5.08783531188964, 
4.67978728169512, 2.22941589355468, 0, 2.00000000000001, 5.8564264548977e-15, 
0, 0, 0, 0, 0, 2.30035468177852, 0.971221457852793, 0, 0, 0, 
0, 0, 0, 0.276787278662907, 0, 0.910199184421298, 0, 0, 0, 0, 
0, 0, 2.63947154520221, 0.802364143622347, 0, 0, 0, 0.910199184421299, 
0, 0, 0, 0.131969997313286, 0.381479129378059, 0.491696481223012, 
0, 0, 0, 0, 0.910199184421297, 0.789464915247212, 0, 0, 0, 0.371209135687777, 
1.71657418978916, 0, 1.35370007297299, 2.29360723495483, 0, 2.20736694335938, 
0, 0.146199785604084, 1.24488955470119, 0.354683260779899, 0, 
0, 0, 0, 0.999999999999997, 0, 0, 0, 0, 0, 0.101806688951662, 
0, 1.69309011255336e-15, 0, 0, 1.57169760266145e-15, 0.85621993846465, 
1.06163059462113, 0, 0, 0, 0, 0.730597553263897, 2.26743914604545, 
1.11756600857138, 1, 0, 0, 1.82123595253574, 0, 0.273705792726096, 
0, 0, 0, 0, 0, 1.4373414516449, 3.49194674261453, 1.72749113742762, 
0, 0.543108239462213, 0, 2.0934038694495, 0.999999999999986, 
1.63144854546307, 0.999999999999984, 5.88418203051333e-15, 4.00000000000001, 
9.00049591064453, 12.1390991210938, 13.8473749160767, 5.50787925720215, 
4.35401391983031, 8.43769498715119e-15, 5.10702591327572e-15, 
0.999999999999996, 3.96947479248047, 22.5403881072998, 22.1866207122803, 
10.6777515411377, 14.6319637298584, 4.75431156158447, 1.16937577724457, 
1.47104550762833e-15, 0, 1.03389519168218e-15, 1, 0, 3.38478708267214, 
2.50787925720215, 4.63097143173218, 0, 1.63757896132211e-15, 
0, 9.1029614401883e-16, 0, 1.0998146837693e-15, 10.3242321014404, 
3.677255153656, 6.32348918914795, 0.999999999999994, 0, 2.90792894363403, 
0, 1.07705664634705, 1.0321604682062e-16, 0, 3.86189341545105, 
2, 6.04628372192382, 1.41556012630462, 1.2616949081421, 3.64648199081421, 
1, 2.93870186805725, 1.99840144432528e-15, 0, 2, 2.13860273361205, 
2, 2.7232904434204, 6.29296398162842, 2.46184372901917, 0, 1.2924679517746, 
0, 1.00180280737661e-16, 0, 1, 6.95446014404296, 6.80034732818603, 
2.44633316993714, 2, 3, 1.60019838809967, 2, 0, 0, 6.89266633987427, 
15.0322608947754, 6.40054559707641, 6.77007007598877, 1, 11.8468790054321, 
3, 3.80009913444519, 0, 14.9394464492798, 15.67799949646, 12.6777505874633, 
9.52363777160642, 7.43131828308105, 9.8163537979126, 22.1248283386231, 
6.10807752609254, 13.5701694488525, 2.15411329269409, 39.9109039306641, 
20.1248283386231, 15.570665359497, 9.37002086639404, 6.93870162963867, 
1, 8.37001991271973, 22.109317779541, 21.217643737793, 0, 0, 
0, 0, 4.9400748684518, 0.994128986745819, 1.18989487396511, 0.713408533571729, 
0, 0, 0, 0, 5.95076506158749, 0.305910597626057, 2.47975753103384, 
0.534086728112572, 0, 0, 0, 0, 0.968772935095449, 0, 0.167327081104592, 
0, 0, 0, 0, 0, 0, 0, 0, 3.72118302191389, 0.452579410239765, 
0.370610499550046, 0, 0, 1.32159224357832, 0, 0, 0, 0.972369753365681, 
0, 0.625501620559069, 0, 0.224056904108889, 0.591551683758832, 
0, 0, 0, 0, 0, 0.934661465014079, 0, 0.764049767619882, 0.0688047234582775, 
5.57236169451795, 0, 0, 0, 0, 0, 0.182291246019779, 0, 1.06826629797128, 
0, 0, 0.910530463077146, 0.881868711354036, 0, 0, 0, 0.238612803712305, 
5.21058668616031, 1.9011435474774, 0.28842456322338, 1.62875694763535, 
0, 0, 0.71600366034066, 0, 0, 2.02330178467086, 0.133720262002288, 
0, 0.108837533499259, 0, 1.61777585608709, 0, 1.1844587059012, 
0, 1.90881288787215, 2.40861130997302, 0.971374708553732, 4.49375796249132, 
0.064383702829031, 1.47263013294457, 2.88005246806881, 1.4747045919004, 
0.178390616028507, 0.770271769947544, 11.8336555607087, 19.5299017100874, 
28.7770987850759, 72.9521599530497, 112.721108282323, 101.644854905545, 
36.7210055372457, 23.476833766393, 10.2304829287801, 3.98021348208977, 
3.6709808221819, 149.733523043111, 176.438921736178, 102.636050639282, 
73.5600214634632, 46.6017722291492, 22.3081595142284, 11.306989778813, 
3.9959029830979, 2.00323222448068, 2.1594714144623, 36.2004459443357, 
92.6266262770497, 58.2487139275958, 45.1979477341524, 15.4800401098234, 
10.7592083884104, 10.2631372555433, 5.39474290506308, 0, 4.07441818434081, 
102.465580117957, 85.8804781115595, 96.4033670182434, 81.1680933832488, 
55.3442333950515, 26.4210160913212, 11.9356392555518, 12.3870460605184, 
0, 2.2239526738048, 71.7985527351031, 81.6806412950702, 82.388078731197, 
75.7443203976173, 39.7055196647917, 13.8728503723912, 16.2481917066191, 
1.79608605473186, 6.5473441955016, 1.995153844598, 35.6191462907649, 
60.3429925404287, 82.2095079072421, 86.2098939368646, 62.6910859606014, 
22.921593632744, 9.84177903015905, 3.38082720905604, 0.981474018403885, 
4.05899216619502, 79.3859768073722, 61.3033812383582, 103.808436594232, 
82.0610986858434, 30.0750204612894, 24.807551366481, 11.0160199610462, 
19.3460041896345, 6.80493214923344, 2.29489577949083, 59.7355528291325, 
93.077246409707, 88.9216932986781, 64.6070017140406, 49.8956163188232, 
51.9155675015562, 36.5985577652249, 29.7957126945251, 2.64954035176464, 
12.5498140127041, 142.29445730902, 112.784715084287, 137.35544664414, 
90.5290733924823, 101.416608324059, 61.4511718574384, 69.9568326961668, 
62.7530065894991, 43.7733580581769, 6.92624314176245, 223.60125002348, 
178.076552654056, 109.698178615108, 116.886213344587, 54.3004500793292, 
40.6670584961748, 51.6325425461905, 83.9893077085631, 37.5417705673707, 
1.37086563474632, 0, 3.18351863482798, 1.71226124000496, 0.299506674079596, 
0, 0, 3.27380818757194, 0.816298948417998, 2.30529104128234, 
1.09933324249402, 8.21674203908649, 6.25418939759934, 5.90232299747393, 
0, 1.76825795328005, 0.403698090733198, 2.11095739880271, 0, 
0, 0, 1.35427811509729, 0, 0.696960674651686, 0, 0, 0, 0.686058434534861, 
0.861564248043055, 0, 0, 4.24035351530444, 0, 2.95584641088592, 
0.264987220006608, 0.71017312999187, 0.590560577773813, 0, 0, 
0, 0, 0, 0.543082317352414, 0.193947158508634, 1.19810342550516, 
0, 0, 0.536730924608599, 0, 0, 0, 5.10240619565951, 5.29520832721497, 
2.31376182722905, 0, 0, 0, 0.732747685499162, 0, 0, 0, 3.39588527353227, 
0.0588055901192831, 5.37179305336941, 0.535945849713535, 0.221699329685026, 
0.32917290267769, 3.4211977233316, 0.650998037081475, 0, 0, 4.31739309833246, 
1.97475206845552, 0, 0.292300447588026, 0.648152889032705, 4.89060869101944, 
1.0214511554417, 0, 0.918867463581964, 0, 3.28931753203902, 1.51571833057365, 
0, 5.80766550106661, 0.436654068729663, 0, 2.82262813142505, 
0.576709439499843, 0, 0, 3.76804923643981, 7.43575934298634, 
0.238283760283301, 0, 1.39235300109927, 0, 0, 0, 0, 20.8206525932583, 
6.58186259171461, 3.04877570618022, 0.712306822913665, 1.73798840409308, 
1.09173668033889, 0.838566597868331, 4.553412056952, 2.90659228660857, 
2.23287146083945, 0.975394293278337, 2.44384367045334, 5.10483187890436, 
2.99561207577433, 0, 3.36166780929846, 0, 0, 0, 0.98880358534348, 
0, 10.01905413065, 7.88635888893228, 0.757125501903464, 0.82720693789032, 
0, 0.956190617318246, 1.9466997240334, 0, 0, 1.22383773511307, 
3.74118521927028, 0, 0, 0, 2.34156155208384, 0, 0, 0, 9.64563981220674, 
0, 5.13754779441915, 10.566907338203, 2.88721386205535, 5.35853572706669, 
1.84167461672252, 0, 3.9358856411625, 1.3421883295472, 1.06072185064044, 
0, 2.82277019388539, 4.07943326798992, 2.79530329420166, 1.72432545794274, 
1.77775997950135, 4.28115391264998, 0.95610980486938, 5.18380905491189, 
3.97919003577249, 0, 4.72697269738953, 1.50443642985118, 4.14572314246093, 
5.55826770640653, 0, 1.33078607544058, 0.932589953336177, 0, 
0, 0, 4.58968220512854, 4.30587751580117, 3.69240628934414, 0.723321131932492, 
1.376916666664, 0, 5.84992610456527, 1.28834142709068, 0, 1.40211948828081, 
3.48581237331298, 3.00743799081102, 3.90936724045108, 0, 1.10590703971377, 
1.7144177678333, 0.825122994975845, 3.91350684526862, 0, 1.05978738529521, 
8.10541138926582, 4.57696419735175, 4.26395796255819, 0.604747484699441, 
2.79514589393604, 0.432029109584588, 0.790345196448247, 0, 0, 
0, 5.72520156182964, 2.11433846436893, 1.40505812431262, 0, 1.80707535135715, 
2.88197596663982, 1.05486472205126, 0, 2.94837780114189, 0.931109802265821, 
1.31730855002737, 2.41441758693291, 0.605259737248857, 0.735927692816479, 
0, 0.873620265678083, 0, 0.989181366324564, 1.03337421282234, 
1.6957208992854, 0.834633692192905, 0.2627153818349, 4.34313433793093, 
0, 0, 0, 1.52776694340043, 0, 0, 0, 1.29505781339617, 1.56971830927057, 
0.555901910228425, 0, 0, 1.11583001043331, 0, 0, 0, 0, 3.90266330872446, 
1.15469209713752, 2.71063589477189, 0, 0.742594469615027, 0, 
0, 0.882953289637362, 0, 0.990608076694186, 0, 1.54067488767273, 
1.51218557945396, 1.53120233156352, 0.678095864661417, 0, 0.901940530440344, 
0, 0, 0, 0.49875846971932, 0.638132215623317, 0.284421465635037, 
0.430773772829807, 0.878124112445614, 1.81255811883429, 1.23935495713342, 
0, 0, 0, 1.21015042910123, 1.4667118400015, 0, 0, 0, 0, 0, 0.879212578134009, 
0, 0, 3.08754539644397, 4.33581847497276, 4.23510698055329, 3.13098741509461, 
1.60544390058555, 5.04103524661431, 0.689730074993515, 0.706279840297326, 
0.782903143128343, 0, 0, 0, 4.405143914813, 1.12450720938112, 
0.840133627739043, 3.24145115394522, 3.40678513155224, 0, 0, 
0, 0, 3.56721810119882, 8.83877713244252, 21.1527642849427, 19.4980153787179, 
15.9649659711042, 5.76128276179861, 1.99724791800018, 1.97757470202845, 
0, 14.3066338416113, 28.8998328531994, 16.1083439388234, 19.1092761244185, 
14.1768984984248, 1.48845599688968, 0, 0, 0, 0, 13.104887343265, 
64.9056914516374, 14.5366802729679, 4.46137698223648, 1.65166004964987, 
2.37338798800842, 1.61689697099761, 0, 0, 0.999047510564758, 
42.5900427910431, 15.9524792832342, 31.7005543589199, 10.3639739052832, 
7.05599340520667, 9.67782366659116, 0, 2.4972154281252, 0, 3.43579555279173, 
49.2140057538931, 27.8548911945265, 21.6095500589894, 25.8900342701069, 
22.0513065750742, 6.62022215419197, 4.18256353714112, 4.08636095855633, 
0, 0.996285409215464, 39.3231756441109, 28.4531765021343, 12.1720720654782, 
16.0513650682579, 22.7399091343956, 6.61806133325629, 1.55432008760563, 
3.71172971467294, 0, 4.33762400745458, 39.5718964080361, 28.3273479274069, 
28.2332553695346, 18.0191685042479, 12.0857809490243, 13.2032310578977, 
6.05666605057292, 6.43281649470415, 1.99584037628554, 0, 37.3559043964818, 
31.8214735009037, 26.2327241922133, 31.2618098032084, 19.8342462991249, 
17.2705579028513, 6.08802097982686, 3.14427353245256, 2.53003885826171, 
1.1237634537666, 50.2414200239854, 49.3341020273702, 57.2071937249476, 
82.2053022451725, 83.9243071861702, 56.3040978753667, 47.6041252645921, 
43.1371012068966, 16.1719231707898, 0.999031118399131, 65.3160797108596, 
73.5540364953218, 62.9781964178388, 49.9434276507694, 20.2255679469091, 
16.2890464508035, 28.0371815893823, 63.8504790174541, 23.0817047673006, 
15.8170874576168, 29.2761165953052, 14.1012466120153, 29.3816046984626, 
22.3281913237617, 18.3140291045116, 22.8561147324, 12.0043344667879, 
2.97138954313448, 2.82116127827512, 1.62377340839354, 17.631379775485, 
21.6016400342391, 6.20897187448808, 5.71023453405888, 5.91124701171411, 
6.91440403332761, 1.9936923479342, 0, 0.993108421301319, 0.990571235260077, 
10.3641779773059, 11.2613745642583, 11.3133411953907, 2.93647067192285, 
3.00728673898038, 0.925810935356894, 2.5605601165259, 0.996936443692931, 
0.997728488213865, 0.968364255811479, 10.5569086278751, 4.86388444264934, 
9.36632460321847, 5.58955899863683, 2.75563393561128, 2.32078389007747, 
1.48689567346757, 1.07947508128747, 0, 1.15166751518813, 12.1308175696932, 
8.35355980646295, 1.30662810704894, 10.2455993122558, 2.58138031380035, 
3.91043383739726, 0, 4.87479192598339, 0.996120667961501, 0, 
8.04210509693785, 0.0922090526354234, 4.92003437600319, 3.77354206439439, 
2.71886376791327, 3.69152509048583, 3.9186350384801, 6.45485178716465, 
3.80094172257323, 0, 1.94640726251663, 5.34879758339352, 9.78150878976768, 
1.16696642004036, 0.616400699416219, 6.51372543680701, 0.813336189565843, 
0.80138483642759, 1.96604043437611, 0.990359939080161, 0, 2.20515593045158, 
7.06343464233008, 8.0650246198412, 1.52994510213271, 5.41003365237567, 
5.71514269109604, 6.22109005621634, 0.92142473009486, 0.950370203328543, 
8.29352444655214, 13.246767837159, 8.96412396876526, 10.2746466015538, 
13.0158245228718, 5.25544134000631, 3.8204391474457, 3.89158169724823, 
5.270302488281, 0.968747066407032, 39.7959424906321, 16.9997168166898, 
12.8158233193607, 5.51326554057969, 10.3246978817939, 8.72901222181983, 
8.56533719033887, 4.36179377009017, 3.03656352013994, 0.928411308369946, 
6.41208249647691, 3.15352695448019, 1.31173299687888, 5.25818704433176, 
0.745521607293084, 1.95151459461774, 1.4982003817538, 0, 5.40053965286139, 
0, 2.96319527858895, 1.2825673874281, 0, 0, 0, 0, 0, 0, 0, 0, 
2.4240452353507, 0, 0, 0.94340693818278, 0, 0, 0, 0, 0, 0, 2.50710419913852, 
0.777666718772135, 0.678580770330974, 0.842349344723235, 0, 0, 
0.988776894840826, 0, 0, 0, 0.538952608850801, 0, 0.798582362035237, 
0.39738524945429, 0, 0, 0, 0, 0, 0, 1.350347634435, 0, 0.873497322392041, 
0, 0, 0.925722539902502, 0.971590727189689, 0, 0.983150297541965, 
0, 4.00340396405177, 0, 0.673470128387175, 0, 0.892060452547684, 
0.907408023810664, 0, 1.42569854100323, 0.823558250750973, 0.995227873511386, 
1.03817537552302, 3.07180774846142, 1.69442689745485, 0, 0, 0, 
0, 0, 0, 0, 3.46689266069844, 0, 2.55285245618944, 1.33815460963325, 
0, 0.563702718411749, 0, 0, 0, 0, 0.34484450784708, 1.34085836702528, 
3.82299078011328, 0, 1.58033314061799, 0, 0, 0.483469637332479, 
1.22955499926134, 1.87973738462652, 7.18959385546719, 8.86809061045337, 
3.107098846201, 8.34452216784713, 17.47085224335, 4.04029303621287, 
5.12139031351311, 0.976450467139427, 0, 0, 9.08458420236475, 
8.23820797788207, 5.27293731448838, 7.70558535852565, 9.76800349368013, 
5.8855536782282, 0.984972473101782, 0, 0, 1.40852193127102, 18.7933196984158, 
16.8682815604228, 20.6136376731632, 5.58561923410924, 3.55484791010282, 
0.993951149017718, 5.63629904125176, 0.993605582403568, 0.993789927957158, 
0, 51.2047100955538, 48.9960332997108, 33.9703975139349, 32.8249825881784, 
14.797666896005, 12.3568585140722, 0.752023712995021, 2.08615541727151, 
0, 0.984442907415579, 32.8197585382177, 43.0241974915573, 23.2803392212506, 
20.8799147811193, 14.0221258715831, 11.0854919646217, 9.57362166482107, 
5.24007483971584, 0, 0.996093363918331, 18.9447539353475, 35.0578905613498, 
29.7484532978363, 45.4783508747888, 15.3969962544051, 6.50031657616211, 
0, 0.950458962819615, 0, 0, 31.9850002458842, 27.6188667782433, 
48.723121949299, 25.5228150177656, 10.8314201952565, 4.90865243952593, 
2.93722293536201, 0, 0, 0, 61.5731347684054, 45.5746130607067, 
49.9376681133247, 34.2750347438422, 25.9762933194308, 16.7414503804228, 
5.64814871258959, 0, 2.65623365430121, 5.95478179100937, 77.5261086135286, 
28.4849832489748, 36.5284334774637, 18.4591401122959, 13.4778923834468, 
4.9171472068603, 15.2381713629931, 12.7161693683169, 18.168711016902, 
0, 31.6669125835369, 34.2708876731553, 12.1723988501782, 7.93950649217512, 
9.04378961892778, 9.21981655461928, 11.0178928207072, 24.3982137751189, 
2.89708282069189, 9.60565168056993, 8.65622585444949, 2.98154866903998, 
3.41777655051322, 1.97319056136621, 0.94937223839797, 7.70208203857221, 
1.34617652547275, 3.45872554184077, 0, 4.4508831986296, 5.46708882494732, 
4.91013091606268, 4.21922872320583, 1.98386611428636, 5.16625258456538, 
0.987883258623551, 1.9976523126893, 0.999873556204156, 0, 0, 
12.5182132684178, 4.26280547021245, 5.74391352663491, 1.98195316835276, 
2.6269268326561, 0, 2.62897806890156, 1.44925105375924, 0.997861706753207, 
3.82959009095785, 2.35700936011199, 2.77169897650709, 5.10202314696777, 
2.92700819742691, 0, 0, 3.48100354952622, 0.995602040944279, 
3.81615035999827e-17, 0, 4.31638807554654, 3.30048582663178, 
2.36477493964976, 1.2194348708156, 0, 0.977365966195705, 0.980450888150537, 
4.12474257865495, 4.77606563803705, 0, 3.99346558838731, 1.92838026171232, 
2.04366128234741, 1.19472055726191, 0.96138692753422, 0.996387846404434, 
0.99984541806601, 1.99778604393487, 1.82983998160516, 0, 4.9192038146885, 
7.92507625677077, 1.46985355828565, 0.947911926201679, 0.977791694572914, 
2.56733368633665, 2.98750221825888, 4.95313936806017, 0.999824591532346, 
0.999860578437574, 7.89583704573002, 4.21926507588364, 5.27405984411569, 
0.930355986587347, 3.37633605324755, 0.959422878091389, 5.39561891897167, 
0.99979420782063, 3.43956122273547, 0, 11.2897779582773, 5.55081251620991, 
1.89935990450622, 5.48241800480934, 3.96533149375221, 2.47265415952356, 
1.51454440712737, 4.52972428406733, 0, 0, 12.0225011724791, 7.91153025532304, 
7.74127222674597, 5.40718453325574, 2.31909328020232, 0.967844388059724, 
1.58662292436851, 2.95377056095829, 0, 1.32011358340892, 1.23898315508515, 
4.64223717911343, 10.803663754388, 3.79777236669677, 2.90177625630225, 
6.26233219742414, 2.15630091677322, 1.0269012183681, 2.652993309602, 
0, 4.79223471757205, 3.56584123462602, 4.46102417902991, 0, 0, 
0, 3.45383379137909, 0, 0, 0, 7.6940281404084, 2.16693413514323, 
0.912362179624299, 0, 0, 0, 0, 0, 0, 0, 4.04266557774871, 2.89142920171261, 
2.51496262475256, 1.7200965225835, 1.68325682775461, 0, 0.965732442398325, 
0, 0, 0, 5.24350559925279, 0, 0.871401061436242, 0, 0, 0, 0, 
0, 0.98237536600977, 0, 2.24585045686569, 0, 0, 0, 1.89046700450081, 
0.955387570975228, 0, 0, 0, 0, 1.92879102561478, 0, 0.85080423779011, 
0, 0, 3.14190536142735, 0.957326114259015, 0, 1.87494654529317, 
0, 2.51070357997405, 0, 0, 3.82656952506661, 0, 1.97744993737216, 
1.35170330459035, 2.10822587715001, 1.94175372195215, 0, 3.44028639125129, 
0.736000964355409, 4.13448395152413, 2.56520703114232, 0, 0.67688875457109, 
0, 0, 0.895273495394896, 2.11444857264905, 4.6913689580074, 2.61739843083101, 
2.02129367682276, 1.94034548557071, 1.14399056570653, 0.914111255570579, 
2.93002043793117, 0.658155262074711, 0, 1.03109777529725, 1.29326425441671, 
0, 2.60117431368295, 1.4589249137808, 2.24477749564096, 1.91566874727331, 
0, 0, 0, 0, 1.06219501204736, 2.5510807060407, 0, 0, 0, 0, 0, 
0, 0, 0, 2.42767674970179, 0.945237214566666, 0, 0.976107085399507, 
0.969920813527252, 0, 0, 0, 0, 0, 0, 0, 0.93785433616945, 0.961161147540572, 
0, 1.71049738415906, 0, 0, 0, 0, 6.88034161147193, 0, 1.17465767888389, 
0, 0, 0, 0, 0, 0, 0.999924944405542, 1.02767874847245, 0, 0, 
0.986076896519975, 1.09467281900344, 0, 0, 0, 0, 0, 1.9996056906427, 
0.957470962203237, 5.99048309631712, 0, 0, 0, 0.963964162563571, 
0, 0, 0, 0.905614591737151, 1.94993903396177, 0, 0, 0, 0.9831267705121, 
0, 0, 0.957717657370635, 0.999854683957083, 4.25432608501379, 
0, 3.92625475060199, 2.08421272201628, 0.954005180455871, 0, 
0, 1.40744037658218, 0, 0, 1.53049385580521, 2.08742786864719, 
0, 0.932204272613856, 2.85214691068464, 1.98483874347024, 0, 
0.961287463317641, 0, 1.98060310648977, 4.71580376952648, 2.45680217392638, 
4.23297195640639, 1.66711483861856, 8.55927110011886, 0, 2.86175747962418, 
0, 1.99859847695584, 0, 10.7902518650229, 5.19643266972784, 5.49022041375391, 
3.87564070714987, 1.97021116872284, 2.569496014327, 3.0938907898396, 
0, 1.52568220270555, 0, 3.56642421421062, 3.78317296836553, 1.24625184436421, 
2.56910784425913, 1.39054014844563, 0, 1.13881208408365, 0, 0, 
0, 9.29905752890718, 3.63237435901733, 0, 3.51829977646971, 3.53387411335125, 
1.96353319280354, 3.02149973739282, 0.991690625183937, 0, 0, 
6.15301568357459, 2.08395759245509, 2.90321862868917, 0, 0, 0, 
0, 0, 1.03875859391059, 0, 1.84169053709974, 4.73464927546807, 
3.29482551730069, 0.944335712537982, 0.507120916270719, 0.965749301458801, 
0, 0, 0, 0.985332869216024, 3.790383181121, 1.90315101755466, 
1.88124756614634, 4.80363467975665, 0.957311201571222, 0, 1.23919628456523, 
0, 0.971781981798635, 0, 2.24551148926806, 4.45565726905827, 
3.05226227772063, 4.87828075884357, 1.71435827787767, 2.47823794098275, 
0, 3.81420654848258, 0, 0, 8.18359075023045, 3.8306499422253, 
9.34550385300705, 7.47922380273676, 2.86490515329822, 8.30720244519111, 
1.84250369206152, 1.53819735622243, 4.49805322022522, 0, 9.08548645995745, 
9.48033745775673, 8.00233814829216, 4.92717440172683, 6.70758201374066, 
3.14257697237739, 2.00773554254841, 5.93062856056231, 2.20908700882117, 
2.37707842086298, 0.929097265699501, 2.27399907283748, 3.87463347029989, 
2.98148887238646, 0.964537049063816, 0.546244710822329, 0.929891454534624, 
0, 4.18303394061368, 0, 1.93109040667433, 0.96703083847716, 3.61958470410199, 
0.989369761025982, 0, 0.92902872459704, 1.74414458556912, 0.999984315170976, 
0, 1.29328432849758, 2.15231795162314, 0, 0, 0, 0, 1.20696993263499, 
0, 0, 0, 0, 3.55494631584638, 1.22110410865143, 0, 0, 2.89766372381781, 
0, 0, 0, 0, 0.999978032485793, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
3.75588953719639, 1.9652117432372, 0, 0, 1.90896550198933, 1.05673226937358, 
0, 0, 0, 1.0806963934049, 1.90293599928232, 4.30123369433736, 
3.44486079748022, 0, 1.53901328346065, 0, 0.995258983026488, 
0, 0, 0, 0.971769684923127, 0, 3.43197182515592, 0.373833602675237, 
0.985323639234126, 0, 0, 0, 1.90456390426759, 2.03931597894925, 
1.20841118866124, 3.70992816438235, 0.96245342999819, 1.74961008372083, 
1.55352276800139, 0.953196661970729, 3.03009393868467, 3.39782428391117, 
0, 0, 6.02393376353993, 1.09666131187397, 2.38937959355831, 0, 
0, 0.962010717241348, 1.99444124276567, 2.76550894052218, 0, 
5.11814487789578, 4.83873314353696, 4.72195723779525, 1.154396463663, 
10.2943490938617, 0.972294997078382, 2.75530214691473, 6.03013806540127, 
3.45677517401991, 2.65640204328229, 0, 5.4699088709503, 1.34591989994092, 
0.968027480801877, 0, 0, 6.70770899556017, 0, 0, 0, 1.40005778014759, 
4.9685716699152, 0.964452984786725, 2.02817154286552, 3.79655870499958, 
0, 0, 1.99939834563455, 0, 1.11769698014686, 0, 2.92639096424273, 
0.960819654345003, 3.20326023047262, 2.98447113073958, 2.13486892971564, 
0, 0, 0, 0, 0, 5.01391492552988, 3.89381198885916, 4.0407120562477, 
0, 0, 0, 0, 0, 1.9869535468726, 0.999715915177586, 5.41238247180703, 
2.34295927530292, 0.971687168536445, 2.8402490316314, 0, 2.44204751644768, 
1.01737799984193, 0, 0, 0, 9.15994429595625, 2.95567612083482, 
3.7946491804776, 4.1972740003978, 0, 0, 0, 3.27363007153705, 
0, 0, 2.3650899333948, 3.4654534716139, 2.87316208732025, 2.90255161855036, 
0.951283393576656, 0.964774392916014, 0.974787639975603, 0, 3.92230230979189, 
0, 0.912985056400291, 3.19872449231427, 0, 1.08754522577537, 
0, 2.58897933848872, 3.08756564150939, 0, 1.99256396650957, 0, 
0.953961014651861, 5.36456555485762, 0, 0.963654884581226, 0.976052104686089, 
2.88404913119628, 0, 1.97262935782497, 0, 13.112154695384, 15.7420452392062, 
12.1139749436912, 8.51502077674635, 10.215560049328, 3.94212774397323, 
6.21638830408711, 9.54554150125157, 2.65272407542105, 0, 0, 7.28242120460745, 
2.62092925211906, 3.37937614003384, 4.48664633024967, 2.97395869257669, 
0.90177461691305, 0, 0, 0, 0, 8.88056667768184, 5.67466072077061, 
10.162571440047, 1.79061431445435, 3.49648224076267, 0, 0, 0.983500346904769, 
0, 2.16673991048653, 10.8264240708011, 6.36210039345802, 3.85302279034079, 
1.21682158835164, 3.86187414679975, 0, 0.6968253531738, 0, 3.31670805240398, 
0, 2.57226229891071, 14.1151750398631, 8.28131476454812, 5.75721084625946, 
4.49791269861466, 1.99870134751065, 3.37965980653243, 3.33007022263459, 
1.23269822194761, 0, 9.96789006551518, 9.77042061342099, 6.09148023318591, 
2.62741129752051, 2.42251547310543, 4.56362272727148, 1.01220534816484, 
1.99943789419644, 0, 1.28270015222995, 3.88111769031741, 4.23324651330711, 
2.72818062103148, 3.36910391583055, 3.88687761171111, 0.959378080510268, 
0.984367102117628, 3.19673890153704, 1.30739763527238, 1.31568427900589, 
0.961647393887926, 0, 8.84706868850713, 9.65991022590421, 9.33027688158077, 
4.52796461920258, 4.99113584797472, 6.3100863090063, 0.930182319749625, 
0.997738507945235, 16.4949719389613, 13.1173637465167, 4.16760218871829, 
3.36259239621625, 3.12016934198718, 0.950808245379981, 8.03656059640706, 
0, 0, 0.984586202630374, 1.18876313692371, 3.80221536706476, 
1.17809069954397, 7.37884624981007, 2.04809686124246, 5.26070383815465, 
4.10525262696822, 1.94417564835417, 0, 7.5467782450164, 6.66135564843135, 
7.65330567683705, 8.82660119406034, 12.7620453377787, 6.5203397742796, 
4.03717654573231, 4.87555460284932, 4.0799236317848, 2.82173777487444, 
1.99864679819265, 12.3493057972168, 9.21592430729054, 9.4533728837409, 
4.99122464321143, 5.2424259448338, 0.137555288870447, 3.25868003822806, 
0, 0, 0, 5.82216684076162, 7.55730229371656, 1.44244779819369, 
2.91260512815927, 7.25020872134978, 0, 1.11095823631732, 0, 0, 
0, 7.56539736693699, 1.84712378243518, 1.21152922835192, 0.346486014723377, 
3.83923578701349, 1.79184651611372, 1.89759007970377, 0.904002689890386, 
0, 0, 3.69349440196439, 3.42677518904899, 6.17144968272382, 5.04785414368672, 
1.87490702289048, 0, 0.843948954087595, 3.10713958170869, 0, 
0.984514608172213, 10.1890570425796, 1.44509019411814, 6.23657133058806, 
8.9097168137993, 0.488670963907921, 1.12998711975737, 2.91462546931082, 
0, 0.721656083695695, 0, 9.53552176555011, 9.13383198944105, 
8.19327871114069, 9.63116644551394, 1.95497726208689, 0, 0.902587791262123, 
1.76826660603099, 0, 0, 7.74333803221342, 6.04027278229041, 4.43333070307042, 
4.11600508389756, 6.12372769376276, 4.36855044471812, 1.66883248603149, 
2.76274930599563, 0.964383472037774, 0, 13.6220474925181, 4.67390878492096, 
7.01684700963481, 1.57859320333416, 6.18621342719189, 2.09441900011574, 
1.36680475312131, 2.51365689323432, 3.45090731960153, 0, 8.98443322364179, 
9.62072892969595, 9.77158854256769, 8.36425664511965, 10.260525607343, 
1.40116902998478, 0.625131226095529, 2.76385178680168, 0, 2.82105334776624, 
10.0928670526034, 1.02076302876308, 2.19163113441855, 6.76004516959769, 
2.4418591663028, 1.20140682616419, 4.65661274997991, 0, 3.9516249587788, 
0, 6.36902935425214, 4.92422280445982, 0.974238064101365, 0, 
2.4750146503001, 0.968352109509518, 0, 0, 0, 0, 1.87084669995694, 
3.87699919748805, 4.60530297888363, 2.41260516837438, 0.578852366783212, 
3.02612668557832, 0, 1.98302807441197, 0, 2.52699703577198, 4.20132353808182, 
2.18575636907279, 2.09026417842781, 3.97626927137869, 3.42219350816816, 
0.988094728368959, 1.07924327925727, 0, 3.22757678786679, 0, 
3.43126766875724, 0.851210544487606, 2.89214809022198, 2.71842730194829, 
0, 0, 0, 1.50978219541475, 2.98389861747693, 0, 3.76193784385437, 
0, 0, 0, 1.16413645843205, 0.952506846190063, 0, 0, 3.12452510083192, 
0, 0.834802767618972, 3.37074694441816, 0, 1.3567014123249, 0, 
3.91962024499435, 0.956035878848859, 4.69106225063999, 0.984410939885691, 
0, 0, 0.916059026609338, 4.84000542559541, 0, 0.879388307105516, 
5.93225667870926, 0.935156263908553, 2.06165373501296, 1.97296935777811, 
0, 2.7925707226163, 1.82393218524556, 9.43118494964909, 3.41492221129637, 
0, 0, 5.7041284083204, 0, 2.68688669006632, 0, 7.08333072454642, 
5.0298957155205, 8.25492128580248, 0.965855061618335, 5.92219128992516, 
1.94062444831046, 0, 3.18397518144321, 2.28238484719099, 4.80419586123132, 
9.08308248200623, 12.5932217373465, 1.44309012247177, 2.92098827399943, 
2.35627264064876, 4.48697594612611, 3.87547864009079, 5.0502503414917, 
2.60932997518683, 0, 6.7539780276728, 5.31947497519283, 0, 1.6489523335622, 
3.84144936676518, 0, 0, 1.29987396935994, 0, 0.998237864990874, 
3.490565668328, 12.9983612730399, 0, 0, 3.86500095297136, 0, 
0, 0, 0.159507090492868, 0, 9.32873090941809, 2.68903354807362, 
1.02327995215196, 0, 1.89895748883235, 0, 0.864550320580367, 
0, 0.924843894290621, 0, 11.2266296252627, 2.94128260043058, 
0, 3.12432060564047, 1.74578951569473, 0, 0, 0, 0, 0, 10.0194666259687, 
4.88658584266307, 5.19008718663892, 0, 2.21200973625404, 0, 2.22654957328142, 
0, 0, 1.01064787837761, 15.6049550852696, 11.3198704825562, 4.61512970277058, 
4.54359915016935, 0.698781181092853, 0.828939939166291, 2.46036742384658, 
1.76640473651669, 1.13773333518371, 0, 11.3287207812387, 9.66406681026291, 
7.97839043459637, 3.96565339604752, 4.10012718055008, 2.59434023765199, 
1.76671102186168, 1.92055863436908, 0, 0, 6.95923136260711, 9.38617742677518, 
6.51542870176691, 5.08833303304505, 0, 5.46677596703476, 0, 0, 
0, 0, 6.8023460815751, 4.02803959353747, 2.41250164382844, 0, 
2.12048368507537, 0.818033837717772, 0.811284326585444, 0, 0.75254158345358, 
23.2289785766658, 21.0100448141169, 21.2248118978531, 24.1950726625076, 
29.4512787398759, 22.5266274899942, 11.9949835948994, 13.0229707758029, 
8.46814686219639, 15.4830893824874, 0.989801832029214, 32.6856594628373, 
45.9900358334495, 20.5818101951894, 7.4619946430567, 13.6559167837799, 
8.25196782534908, 6.36342059587942, 1.17587798371825, 0, 0, 11.9474523277693, 
24.9697700606624, 9.67550435206904, 7.11378436835738, 1.85978655403155, 
7.16140442326668, 3.31115530311662, 3.00960657586999, 2.9219441306962, 
4.58154143356613, 13.2680765838075, 10.2192471367363, 6.87190748875279, 
4.95712688765273, 1.95202587674276, 0.988352328547076, 5.62085996659517, 
0, 1.52548807537542, 0, 16.9518685774395, 3.22284113772795, 10.6853871171277, 
11.8180239441546, 11.0612377434916, 4.09753441859766, 0, 0, 1.3330570250013, 
0, 21.0105841245838, 6.93097115172881, 6.83369941646182, 6.16394697395613, 
3.92427719895935, 0.992586804341805, 0.881133590770816, 0, 1.15863606761497, 
2.57794900272213, 20.205128470535, 14.8240498478195, 22.7445542624752, 
14.4328474436363, 13.805667542437, 5.19995576642317, 0, 2.51037466381274, 
3.67222819037276, 0, 25.8818222774883, 25.6243925484878, 25.1202066112919, 
8.8364558989751, 10.6517754995285, 1.95183659030236, 8.37760928819357, 
2.07848236962436, 0, 3.61297674170164, 24.3143961270682, 18.8422069062725, 
15.4661641953917, 17.4939243623818, 14.8379437676341, 7.85301446143669, 
4.56928545296468, 17.1142036578476, 6.9969931167736, 0.974516701605537, 
41.0546051779138, 41.2396948100422, 30.9451525899379, 9.28680568901145, 
11.2823224196075, 7.07138014241619, 8.35740168349519, 16.4705314584203, 
10.1367989734677, 1.42632054584933, 0.789045953721911, 1.92820417322732, 
2.93437112886675, 0, 0, 3.49043128923743, 4.65871498719733, 3.45341327000616, 
0.158885742341816, 0, 6.56456537259497, 0.904175354072654, 0, 
0.43482422901976, 3.4600185457799, 0.563496810536907, 0.654303603073351, 
0, 0, 0, 0, 0, 1.82084680387626, 0, 0, 1.62126587005415, 0, 1.95199148233014, 
0.832390075760339, 0, 0.158114620705607, 1.64514121473996, 0.796231510323514, 
0.694508567907091, 0.855314216203357, 0, 0.897125897072109, 0, 
1.72944620154472, 0, 0, 1.79048039317216, 2.45639842769965, 0, 
0.369159043755667, 0, 0, 0.998407734756953, 1.2025457550827, 
2.26135165518941, 0, 1.83108368963263, 0, 1.67359476873574, 1.77095110246616, 
0, 2.26997995807978, 0, 0, 0, 0.753282090138475, 0, 1.87439410440902, 
2.07137979669494, 0, 2.02315425480291, 1.22797105429285, 0.839735964555958, 
0, 0, 0, 0, 0, 1.48874280980535, 0, 3.40433610747778, 0.533033649160837, 
0.870955724562227, 0, 0, 3.31064622729148, 2.03366334956491, 
0.0952993850034861, 5.51790578537878, 0, 1.59799625292199, 2.5681072490802, 
0, 0.599601570572549, 0.913431865600578, 1.08486493170755, 2.76740470827554, 
0, 4.72369248143339, 2.32782882773936, 1.6574316925009, 0, 1.12188495211598, 
1.49739503307722, 7.10084009175291, 1.79606566193654, 0, 0.482403611516955, 
1.06534397066927, 1.62412327110963, 4.31113577120195, 5.75729945799922, 
0.870308202919181, 0, 0, 0.797778605139102, 2.34682286864638, 
1.99369144517311, 0, 1.72642875679735, 0, 0.905305722427236, 
0, 0.612232983613017, 0, 2.67349947102764, 1.97715947913304, 
0.781822197763554, 2.03547445755438, 0, 0, 0, 0, 1.01915993685572, 
0, 4.56931340948164, 2.2133080914496, 0, 3.57642799066638, 1.93408563145307, 
0, 0, 2.5232264434448, 0, 0, 0.659894028438038, 1.00040242767402, 
0, 4.34321706384974, 2.70448896614546, 0, 0, 0, 2.13683529606351, 
0.954061917605477, 0.668461954409201, 2.64436855470797, 0.863575760375821, 
0, 0, 1.03860401646941, 0, 0, 0.961985798281919, 0, 3.08682513962986, 
3.46507748687802, 0, 1.0093053071988, 0, 0, 1.09460200639388, 
0.941249054291113, 0, 0, 0.756572351926487, 0.644786259757739, 
1.36743370740754, 0.801193331099489, 4.68690815900379, 0, 0.850361213334639, 
0, 0, 0, 6.68622684835199, 9.82979237055641, 2.50924854221481, 
1.97747162732127, 0.745176167697714, 0.821491369401391, 0.872517785038846, 
0, 2.60339182458295, 3.38426631023116, 2.2856673711622, 0.996068757761497, 
2.21366008239101, 0, 0.75349092857244, 0, 0.843978403877401, 
1.00798815899338, 0, 1.92488216454101, 9.33460881510809, 1.99647518906631, 
1.99663758367329, 2.55985933782258, 1.06896773817672, 0, 2.44417560302444, 
0, 0.999169522192542, 0, 4.77002773982726, 4.26437928218937, 
1.03552012149485, 0.997283851194522, 0, 0.99954323168083, 0, 
0, 0, 2.30570157376949, 4.1096417095646, 15.9146418840034, 2.44212756024836, 
3.06788515278813, 0, 0, 4.29684930321504, 0, 0, 0, 4.97991354372101, 
0, 0, 0, 0.872661605262595, 0, 0, 0, 0, 0, 1.56144456436146, 
0, 0, 0, 0, 0, 0, 0.999729605788351, 0, 0, 3.26889538202259, 
1.19551448126251, 0, 0, 3.04414534369391, 0, 3.36186617559095, 
2.95821037051476, 0, 0, 2.28999736446406, 0.983345573615624, 
3.20525331938106, 1.81037670006673, 2.89256881135482, 0, 3.12899089602515, 
1.13840374860369, 0, 0, 0, 1.03947314900628, 0.993849097268162, 
2.59574730986084, 2.00117142612139, 0, 3.34606913145116, 0, 0.999760053350693, 
0.999412090343048, 0.969797867849145, 4.05901678496279, 0, 0, 
0, 1.99603732030656, 0, 0, 0, 0, 5.85377090058466, 2.39662414247961, 
2.91631435941761, 0.998553900797001, 0, 0.998949806330498, 0.99568529945038, 
0, 0, 9.17883144374971, 7.36055299950464, 8.12648573591866, 3.38768366977465, 
6.67442666442732, 3.61224252379088, 2.78114671316271, 0.775714655724731, 
1.9976334256516, 1.67106101677856, 0, 3.60103841963151, 5.44238480608601, 
1.63476588991628, 6.71581910408752, 2.8961100774501, 0, 1.30875078688017, 
2.88291780404226, 0, 0, 2.3001105917914, 2.55582613131659, 7.54373053922483, 
1.87683125449634, 0, 2.48755379550636, 0, 0, 0, 0, 1.5701632388473, 
0, 1.67141244468936, 0, 0, 2.5601220940136, 0, 0, 1.62540774655234, 
0, 6.99874771763349, 2.50348317902946, 0.469722354531482, 0, 
1.53889450657043, 2.50553233532469, 4.05133380600267, 0, 0, 0, 
3.65418919040281, 2.78341230444998, 4.8812816013675, 0.795752275777101, 
1.01146427448391, 1.05376501651966, 0, 1.14877523639873, 0, 0, 
6.84469308182106, 4.90836973075789, 5.86829458843499, 3.74622668534054, 
1.78529861560868, 2.54729685206486, 0.6620767621895, 0, 0.965868364267561, 
1.10549485748535, 4.04368788446442, 6.30857441941922, 0.844772079121093, 
1.13412052956315, 7.36261131872262, 7.76086880824449, 1.91598477449492, 
0, 0, 1.43102794841854, 4.39877719092151, 0.88156369043143, 6.13625868036563, 
0, 0, 0, 0.909237630153276, 3.81700924871632, 2.69044413665303, 
0, 1.49205200031738, 7.42040225987871, 0.790618172840474, 3.18794006298108, 
1.85627637696188, 2.33611056950919, 1.88719544901294, 4.63590044072067, 
1.54082444664815, 4.53847996038677, 7.4314992242876, 9.88018621864825, 
14.825991904057, 12.8531546111169, 18.6113045275637, 8.93363933297143, 
6.07184279422142, 0.568402340690452, 3.44188021541822, 2.02120569425354, 
2.5491315296733, 9.18051951134506, 4.51733188197222, 4.15142534131288, 
2.52931296591146, 2.86811079561114, 1.89193801858452, 2.22661966574791, 
0, 0, 11.9623730908976, 16.6521433303046, 6.55610594902141, 0.879735813128128, 
1.80815995699322, 2.8906014752376, 0, 0, 3.13768124451457, 0.968797910660136, 
10.1391086550208, 5.76229608453743, 5.56872977986076, 2.88419821433969, 
1.94625387471673, 2.55103809878809, 6.82909804739107, 0, 0, 0, 
5.90643695079338, 9.61516021037681, 4.64970867723366, 9.25178870935806, 
1.90803075121065, 1.93719238099673, 2.89472873789369, 2.0796674652523, 
1.82252869622845, 1.75923677600088, 13.7373468506303, 4.86617715562842, 
7.49105281334692, 1.72611168777162, 8.42449190781769, 6.43610489242695, 
6.89492343003825, 9.03908730807451, 0.995927244702099, 0, 9.98125470006923, 
16.6280581566555, 7.12105495653256, 3.57809928182247, 8.70298111575223, 
4.07347955099947, 0, 0.981484468152907, 2.16272786478334, 0, 
11.1484112742438, 9.7182969717503, 8.59918761099931, 4.87140139102763, 
7.50633576902789, 6.113112357942, 2.66976344222481, 1.82715461771679, 
2.08771708036399, 0, 13.31558346016, 14.3704433150601, 16.0698930767042, 
8.22420772981209, 6.94608169314167, 3.96980603827904, 0, 0, 0.914378457543915, 
0, 19.6438144115647, 19.3259174156127, 8.68113260887304, 0.853815576089381, 
0, 10.6327282704209, 5.56816393815464, 13.1878515236813, 3.74118856131506, 
137.148095067884, 150.280845347556, 87.4866735457687, 51.4497446617674, 
54.501044477412, 20.1417047400245, 17.380990671328, 16.6163649569682, 
31.4144028767403, 18.5422706586845, 4.88618014968206, 91.1690742489211, 
82.9692888103547, 43.0967030504917, 17.5317878580385, 6.43740733856962, 
1.41188083357728, 6.58056989352143, 4.00791373266771, 4.08291290881012, 
0, 27.3296523344606, 56.5804156704766, 12.8984529823484, 9.10063633016695, 
4.89784318396786, 4.766506298415, 0, 4.7745906519025, 0, 2.27763448861482, 
59.284795397713, 19.6151791346435, 25.253671580945, 17.8726286471045, 
4.04791808805037, 2.18206459404342, 0, 0.999278664608825, 1.00275921565778, 
1.87195105593701, 33.5372324232029, 12.5409917919114, 13.7209228151719, 
6.03016664350123, 7.65685897597177, 0, 1.88033838381596, 0, 1.12301660340431, 
4.85485661248384, 48.766565211374, 32.4262549065606, 10.3734240483445, 
7.4185108103643, 11.4686819636891, 3.34524680096379, 0, 1.81843426180621, 
0, 3.37830455433971, 76.6781913765357, 24.8586914755619, 29.4670375071665, 
29.2640974003136, 10.1889561526865, 1.85117670927986, 0, 0.954328526936796, 
0.916689699044685, 0.992092326119036, 40.198830017863, 21.4988458617573, 
17.4771855786618, 8.77576553412164, 0.687296862376238, 2.45229121714727, 
1.73619297442391, 0, 0, 2.71932913884794, 12.4649762208083, 4.15170131492955, 
1.39587488778131, 0, 5.39384810347355, 1.54693508581638, 0, 1.03373365852815, 
1.19811015500175, 2.06680715409871, 22.3838034409758, 2.64763992069039, 
3.10362837453775, 3.37603345708775, 0, 0, 0, 0, 0, 4.0312461233118, 
1.66136896233283, 1.50119027540905, 11.592059120273, 1.68171124381397, 
12.5902097800341, 2.74354179145018, 3.77803568046182, 1.99612076067103, 
3.53041763297909, 1.4879480984933, 2.47115894626838, 12.8749830066992, 
10.0339414109481, 2.89397947153916, 3.14829322628393, 6.19960828728696, 
0, 2.11632020098165, 0.976599302151271, 0, 3.83972000875065, 
15.3091807804553, 0.926064415864112, 2.87569306523241, 0.971787179184151, 
0, 0, 0, 1.64588177796165, 0.986260733184229, 13.4304127308814, 
1.88623101549877, 4.31560904508637, 1.89615529854669, 0.976243575307969, 
2.78584917019949, 0, 0, 1.2128747311541, 0.989193362033089, 7.93633089770986, 
1.94972978143459, 3.46848148410448, 4.51297359415484, 1.95179763545259, 
1.05179190340917, 3.1640982806174, 0.999702692025875, 1.17978626198547, 
0, 7.94726089474967, 3.44059164148543, 0.939523753478048, 4.70375174207081, 
2.98794322861808, 0.977470689674146, 2.69146307316433, 2.69172105297955, 
0, 1.26591433500946, 8.90988929357255, 4.7252319880244, 3.40846430667203, 
6.87479338678926, 1.94003959531919, 2.47213491421359, 3.41692717642207, 
0.992661323235376, 0, 0.99423785601936, 0.768322101503216, 1.87642609174331, 
2.95336131568193, 0.946002911581441, 5.58507804284629, 0.981998173193118, 
2.48193802651745, 2.3048245664795, 2.99743951530215, 0, 3.62139044224961, 
7.53248353811314, 0.985211931977437, 16.4840344078636, 9.33575189192444, 
12.1831540063677, 3.92198176817294, 2.45824302667272, 1.98824193578352, 
4.20649061730899, 15.1040574834812, 22.7324134126007, 11.8798390670568, 
4.4670263667637, 3.40558021832637, 4.83935467716528, 5.99634197285295, 
5.24627224489729, 5.51175194773945, 2.0579850669177, 1.60525043520067, 
2.4492296226341, 4.52113176187232, 10.5096292997774, 8.73402983490624, 
3.99258873739299, 7.33062742762807, 0.788026497687747, 0, 0, 
13.3069229715214, 16.2742120666469, 5.74538673725755, 7.70627647447668, 
1.90802986064229, 0, 0, 3.71453891133762, 0, 0, 6.07176391913037, 
3.97196362902114, 0.830461323313107, 6.91441222228583, 0, 0, 
2.03512873039755, 0.96401669443267, 2.22559050870273, 0.966624190096832, 
11.7492556044527, 2.85792580639632, 1.7540348594651, 2.8195678292447, 
0.921841832687131, 3.68623780387584, 5.85870396445779, 0, 0.996956368839757, 
0, 4.93801574954316, 0.863785728028779, 3.07640636487708, 1.00341229438453, 
5.62555544809656, 3.27585193030436, 0, 0, 0, 0, 5.58720517023135, 
1.75216398438566, 1.87533529954832, 1.0013798889236, 1.85442355647094, 
4.20724785171951, 0, 0, 0.975698872455474, 0, 5.99852621577895, 
1.03394256517314, 7.32236656946311, 0, 2.50802705372723, 0, 0, 
2.2858139114704, 1.46114910074173, 0, 4.07969079044991, 1.78853653644508, 
2.40832590559105, 4.96071049613532, 3.95256777313379, 4.85326533511314, 
3.04345224154831, 2.49681431254168, 2.96641893084457, 0, 12.2570743964177, 
2.81468502620302, 8.16713643844059, 9.77082264565926, 19.0091971900631, 
3.61537228072022, 13.2278302153454, 9.1140780572802, 5.89749516939394, 
0, 8.5076366060129, 19.4252615475713, 13.4149754541565, 8.61159269532386, 
13.6803637760646, 5.94630397047269, 4.14347304345115, 6.77609912498458, 
3.82724862320431, 5.09070648540375, 11.3708317862466, 11.6032382908614, 
11.6685850979924, 22.4853902784216, 20.9289184255627, 10.3659818158208, 
9.79267131085165, 1.87918316631307, 4.36806996710093, 1.00279567907459, 
23.0828478314518, 18.8903682957147, 8.42899640881905, 10.9071454256849, 
8.69356307631388, 6.2291218637114, 2.08289262896653, 0.92053528574895, 
2.23211558153088, 0, 14.0082737408222, 20.6603106142508, 12.2729606652049, 
0, 6.47209047145971, 0.866205316846864, 0.749805915240526, 0, 
1.20704631682133, 0, 17.8681135959265, 14.5307359073818, 8.02470547455547, 
8.60918303364736, 5.88592881506472, 0.755607675655323, 1.77555559614545, 
2.47331578136328, 0.896565742079603, 4.11658158483972, 17.111500907963, 
3.63922022086961, 15.2414267779717, 6.53680335804636, 3.73602312358324, 
5.51167040884364, 4.55195847437086, 3.00899489245041, 3.67660385671568, 
2.46536751507602, 6.74653760478725, 4.90910403190808, 5.76877942304103, 
11.108458300355, 9.51028810210034, 2.16763070626175, 4.64412563683974, 
0, 0.825404102854921, 4.78935752227833, 13.0805848402548, 7.49706645618684, 
4.63919153700878, 7.75850505495144, 4.66932565698499, 3.71236869840435, 
0, 1.81461073903049, 0.81836811607867, 2.38002052575294, 8.72670006608183, 
9.57963603529964, 1.19286347135426, 12.2268144351752, 12.7926862376877, 
8.69585937386575, 7.25349146868993, 7.20714750114843, 0.755282255869604, 
3.25685361665342, 11.8619734201328, 16.140622832355, 22.8116240322081, 
6.13124800947795, 16.4669126242429, 12.7733778616817, 13.2644187702148, 
8.08528329728458, 7.84208354537676, 0.921772017090861, 46.0508041973134, 
23.9244841512798, 20.7412865073152, 12.9042876640416, 6.81616888608797, 
7.0868705182656, 10.1747182209431, 14.6738794967417, 4.58868793507869, 
9.1492595476533, 11.2933989173614, 28.9146353329331, 42.4304607383084, 
56.4813410485071, 43.0082955395507, 26.6560020120628, 17.5279792881717, 
7.02383703536081, 0.426099061965878, 6.78190542679508, 82.2113975537591, 
100.537294268027, 46.6222686214988, 34.7262679646031, 26.545282392881, 
25.1882072366354, 2.14497798723466, 0.543797108680009, 0, 0, 
20.1410944453534, 25.8217463747391, 21.0531113930819, 19.3917007835787, 
12.5618937907157, 4.10839608329301, 0, 0.306905527412433, 0, 
2.22944705829534, 36.5800339133782, 23.4269647386107, 39.05843660334, 
32.5065933950972, 5.31385154694938, 7.76293116046413, 3.51144519563609, 
0, 1.75475898357554, 3.71743850042727, 33.3594959754937, 20.7541305152259, 
31.6562277237709, 26.7555333414378, 29.1218481419199, 3.74270832457214, 
6.02411453997867, 2.29616918490862, 4.47144654015751, 4.29060007413067, 
28.8469087274091, 21.4564078316195, 30.7528581635528, 23.4210160639959, 
15.895973785853, 28.4780426829414, 1.34991800278342, 7.42549511454687, 
0.690762534544636, 1.48832518780068, 28.9559797372787, 19.8696168246619, 
23.8265205617731, 22.9481863432805, 32.7642409135504, 12.9148712441483, 
5.8658911333144, 5.80552171178457, 4.9633961026406, 0.0553188290355487, 
19.6693250726971, 36.7494502363344, 37.9872209740261, 33.9712396587286, 
35.9638626385723, 37.2014903311141, 35.6146610211748, 9.80290694075768, 
11.0628159934034, 1.55966883969441, 91.7682477526294, 40.8104963448296, 
80.7821077784469, 52.7642156122856, 35.5215337799523, 47.5954758603859, 
57.5415368995597, 110.161369819528, 63.6048044962607, 4.17553606377464, 
141.120258215411, 125.806921646202, 97.7983030916063, 76.1670131087609, 
38.2229354866862, 21.7716913485644, 50.1462356902423, 82.2390807535279, 
61.9835753391291, 32.2024746191043, 46.5912602482075, 104.651011592005, 
160.523999047612, 133.516066828089, 147.833723432064, 113.719786219811, 
60.2799172788116, 26.1450549311169, 13.6510212628904, 29.6664332602351, 
242.536524482525, 189.260333141627, 137.768027035039, 87.7985119755161, 
56.4285769870615, 34.1418521690987, 17.4168812452515, 14.2908965543534, 
13.065338338724, 29.356153887117, 197.667923626447, 122.732263452077, 
75.8368577140861, 41.0292699778265, 36.6485823913462, 35.8661157703685, 
50.6828409828566, 18.9294394371777, 22.1763008025229, 26.1439181367569, 
111.969287733149, 45.1141968042733, 70.5304195217491, 68.728957277835, 
71.3535026717876, 56.7635358938605, 35.1883729740525, 42.8466950285289, 
25.8859563874123, 12.3184941466701, 33.0575469803582, 23.6469087927199, 
32.2237298061024, 24.6328592545032, 29.8891381299053, 44.1480673103176, 
38.9734531308144, 60.2784390142375, 58.0198994455857, 2.05042457447063, 
49.2136389563618, 20.2796268681427, 27.386755967988, 34.6038315138696, 
29.6401411543744, 73.0449783167315, 88.5417622658063, 54.2972241084437, 
48.2603777996481, 5.26787854676332, 36.6044069893624, 30.3416825109591, 
26.904172441477, 36.8150402181288, 45.1684588691817, 58.659462325268, 
41.0474982226624, 39.0872340984404, 46.4696253371579, 13.4950617287212, 
30.6462302301011, 27.0047669698651, 28.4784229586538, 49.1670124623495, 
38.6605901611398, 64.4338023151966, 44.2794116741609, 66.5311602646354, 
72.4950340320543, 14.4781689352736, 103.666508299968, 71.6665472958087, 
81.0378993367318, 65.3831156294, 91.8758136340775, 63.9106635711156, 
56.2074058912528, 52.3909498320587, 68.1106980340605, 17.8579646659356, 
167.816596119811, 145.050864253031, 77.501490886222, 97.6324405283533, 
80.5450685710663, 82.1032730663515, 48.4339810981628, 28.9266228990228, 
32.1676507172862, 4.25040355668684, 7.42474403578934, 0, 3.09565827293319, 
0, 10.824727003501, 5.60432033131942, 0.416589722531437, 0, 1.2320588672932, 
0.357844736752203, 6.51503148503919, 2.57867434963693, 1.16137352039093, 
5.94870724809541, 2.41937689051721, 1.18577074852205, 0, 0.206055969790053, 
0, 0, 0.959761875221349, 2.33394673736749, 0.252666199684488, 
0, 0, 0, 3.89428804227664, 0, 2.72923934048799, 0, 1.19853202937462, 
0, 0, 0, 0.579878916931005, 1.52314591973696, 0, 0, 0, 0.299532871132043, 
4.55613811171431, 0.812007844368854, 0, 1.5005081501804, 0, 1.0806093511111, 
1.68413503171484, 2.75705966927304, 1.13828042097738, 0.8125667437799, 
2.71072291150065, 0, 2.43953324171124, 0.810142544138497, 3.64486095758132, 
0, 0, 0, 0, 0, 7.99804111753055, 0, 1.72463940474664, 0, 0, 1.10275427367343, 
0.723812954886652, 0, 1.8952356587698, 1.42935078400734, 0.168349084712624, 
0, 0.262452920223762, 0, 2.36328343269493, 0, 0, 0, 0, 0.451791070119006, 
0, 0, 0, 0, 2.38851424547917, 0, 3.19182778580257, 3.5984774227494, 
0, 0, 0.478215114877406, 10.1095738008285, 9.28721945304422, 
1.29168008601401, 0, 3.87861890957482, 0, 0, 1.53286843051617, 
5.29831168798779, 6.89400399697019, 1.134251188901, 6.63459443482869, 
24.2541456200532, 15.521957437138, 10.5843420359563, 4.32960694851253, 
4.33812675698886, 0.969924664135594, 0.558280651136316, 3.80279735712139, 
5.98420998691321, 8.47794176331851, 11.1359195100787, 11.0911192208098, 
1.96940803361265, 0, 1.99979032650804, 0, 0, 3.96867940747638, 
56.8720237166306, 22.7686798020202, 3.70705472901882, 0, 2.00217623332833, 
0.902847540004246, 1.99882812645925, 0, 1.82452778415858, 26.4908750335685, 
4.85781529841099, 11.6821803489048, 1.98084069812182, 3.05249253919903, 
1.29750122745969, 0, 0, 0, 0, 35.3585384627609, 25.0433458748984, 
15.7629048576807, 11.7494635692714, 10.8859940115626, 3.51665896045552, 
0, 0.930249889419812, 0, 4.92659722651864, 14.0144109637227, 
30.3236160063693, 11.2195480394222, 10.1671530341863, 7.83083625614026, 
5.0646483645868, 1.13005051120202, 0, 0, 4.64240456877078, 13.7374431315963, 
19.1579440302675, 12.241778634659, 19.0963120030739, 7.74018715249117, 
2.5749760419434, 4.05832242430116, 7.20623342506513, 0.951832509244829, 
0, 15.5499123127529, 12.3186763160118, 11.0851603744193, 12.241553873929, 
16.4266369974682, 8.77069126863775, 3.30220826383735, 8.32821530539731, 
2.76601290142502, 1.5592558636758, 35.0543002059425, 16.5548574166685, 
53.0763357603202, 79.545404708057, 23.0776733428395, 32.014871967276, 
21.4367221745908, 15.008191799057, 2.02182907633624, 2.9901199841667, 
32.1545175252184, 61.8209403327799, 45.6593426633149, 25.7115874436194, 
17.3185544107747, 5.852202361063, 12.8831187020347, 8.74016969003828, 
9.99004548824544, 0, 0, 2.63415219893508, 1.15198796608873, 0, 
0, 0.310548770049299, 0, 0.831312605467187, 1.5580686032526, 
0, 0, 3.57394782263398, 0, 0.422304383541795, 1.20792840044971, 
0, 0.909927716107691, 0, 0, 0, 0, 0.913667786481584, 0, 3.03432558567967, 
0, 0.811389266552932, 0, 0, 1.65448381912852, 0, 3.07745407188648, 
0, 0, 0, 0, 0, 0.823895743327127, 0, 0, 0, 1.60538423263416, 
1.00634176368792, 0, 0, 0, 1.61754608809313, 0, 0, 0, 0, 1.35233688459087, 
0, 0, 0, 0, 0, 0, 0, 2.13807015600315, 0, 2.08248273537457, 0, 
3.05920663733824, 1.54619752350669, 0.794074876848297, 0, 0, 
5.27377795259407, 0, 0, 1.61562472442788, 0.733229829335257, 
0.742088121646461, 0, 0, 4.93479434557679, 0, 2.57496380202211, 
0, 0, 3.54668949502293, 1.47310767425611, 0.100229477707034, 
0, 2.36483464748833, 0.390696150926821, 0.55849635324616, 0, 
0.591365348634985, 0, 0.616098469115779, 3.8025557953071, 0, 
1.92237877367086, 0.434157569712971, 3.50207221356405, 0, 0, 
0.708622096728081, 210.030975341797, 191.442153930664, 76.9443664550781, 
58.8173599243164, 63.1499633789062, 57.6645393371582, 140.5419921875, 
166.122192382812, 166.122192382812, 180.825103759766, 7.0678014755249, 
78.6141967773438, 63.6353797912598, 39.9118843078613, 9.83613204956055, 
18.1592330932617, 23.6139602661133, 31.1159515380859, 47.2389678955078, 
39.1199226379395, 6.32862186431885, 68.1208114624023, 107.728591918945, 
32.5777435302734, 19.07177734375, 17.0079536437988, 11.9401512145996, 
6.63515949249268, 16.5225276947021, 31.7274799346924, 1.52561867237091, 
114.25267791748, 80.4463500976562, 56.0293769836426, 22.8511524200439, 
7.09695291519165, 8.28136157989502, 14.1009283065796, 2.04019451141357, 
10.0094976425171, 3, 281.984710693359, 158.807662963867, 83.4046173095703, 
73.2398452758789, 23.7526531219482, 11.9456729888916, 2, 3, 3, 
9.94169616699219, 240.521286010742, 140.32844543457, 83.1177291870117, 
76.2493515014648, 47.8173675537109, 12.8526964187622, 3.36329555511475, 
5.28842735290527, 3.5658130645752, 8.29394912719727, 241.048446655273, 
174.643814086914, 159.081069946289, 81.6945648193359, 55.0057487487793, 
10.0331287384033, 5.77385187149048, 2.35777425765991, 2.7336573600769, 
6.01656436920166, 215.134963989258, 217.899353027344, 169.133224487305, 
61.2319030761719, 46.7882118225098, 22.56272315979, 13.8928918838501, 
4.85424089431763, 7.47835826873779, 9.96930313110352, 191.186874389648, 
115.883857727051, 74.5503692626953, 36.0978355407715, 35.391788482666, 
25.9204978942871, 3.53666114807129, 7.41453266143799, 4.23012447357178, 
3.42712044715881, 137.934417724609, 76.1870574951172, 55.825325012207, 
36.795280456543, 41.3957672119141, 13.7431554794312, 8.52959537506104, 
1, 1, 325.968627929688, 325.968627929688, 132.338088989258, 114.123115539551, 
126.67699432373, 103.928855895996, 208.723770141602, 307.63916015625, 
307.63916015625, 307.63916015625, 13.5679693222046, 140.021240234375, 
134.522918701172, 88.6134262084961, 32.1855087280273, 20.583366394043, 
40.7936553955078, 74.8364715576172, 73.5725708007812, 63.0246963500977, 
5.87072849273682, 125.446617126465, 186.36279296875, 93.8478393554688, 
46.3958015441895, 13.0408382415771, 16.5485363006592, 22.0314521789551, 
28.9872360229492, 25.9912719726562, 6.59744691848755, 201.923355102539, 
138.066772460938, 97.3709335327148, 50.7099227905273, 20.5934104919434, 
6.50300455093384, 10.3837776184082, 9.90621566772461, 18.3000392913818, 
8.72202491760254, 391.085174560547, 296.359252929688, 176.069351196289, 
91.1117172241211, 78.4037933349609, 7.98056745529175, 6.53783369064331, 
5.27393913269043, 4.32350730895996, 16.7869892120361, 457.777709960938, 
255.205871582031, 183.079452514648, 134.153884887695, 61.1934967041016, 
18.8619976043701, 7.58270740509033, 6.03013515472412, 1, 15.1051445007324, 
457.777709960938, 333.930541992188, 255.236053466797, 163.216781616211, 
79.1546325683594, 25.6583766937256, 6.58740139007568, 3.5177435874939, 
4.85598945617676, 27.7132949829102, 400.338897705078, 343.039581298828, 
243.72297668457, 118.45263671875, 92.9027481079102, 31.0515422821045, 
17.1158485412598, 2.18419075012207, 1.84594464302063, 5.20428133010864, 
363.848724365234, 233.134338378906, 139.076141357422, 93.9275283813477, 
63.5216903686523, 13.0997934341431, 19.9269618988037, 4.75150203704834, 
2, 10.6825017929077, 168.8798828125, 165.351425170898, 93.768798828125, 
76.0554962158203, 66.3529052734375, 31.3254814147949, 3.89081883430481, 
2.63696956634521, 2.08974862098694), dim = c(10L, 10L, 40L), dimnames = list(
    NULL, NULL, c("MPO", "HistoneH3", "SMA", "CD16", "CD38", 
    "HLADR", "CD27", "CD15", "CD45RA", "CD163", "B2M", "CD20", 
    "CD68", "Ido1", "CD3", "LAG3 / LAG33", "CD11c", "PD1", "PDGFRb", 
    "CD7", "GrzB", "PDL1", "TCF7", "CD45RO", "FOXP3", "ICOS", 
    "CD8a", "CarbonicAnhydrase", "CD33", "Ki67", "VISTA", "CD40", 
    "CD4", "CD14", "Ecad", "CD303", "CD206", "cleavedPARP", "DNA1", 
    "DNA2"))))

expect_equal(as.array(images_comp$Patient4_006)[1:10,1:10,],
             structure(c(1.0431410074234, 0.999999999999995, 0, 0, 1, 0, 1, 
0, 0, 0, 1, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.0698881149292, 
0, 0, 0, 0, 0, 0, 2, 1, 0, 0, 0, 2.20362424850464, 1, 0, 0, 1, 
0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 1, 0, 0, 1, 0, 0, 1, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 1.2838659286499, 1, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 6.15238520588108, 21.5940361022949, 29.9155101776123, 23.3937034606934, 
22.4542732238769, 46.4859237670898, 31.1181564078178, 43.2582171489389, 
0, 2.04408587352125, 1.31647515296936, 0, 5.8349494934082, 4.37537908554077, 
8.20199966430664, 8.69351959228515, 13.6173230260428, 9.00832939147949, 
1.98400064879446, 3.12125628497432, 0, 4.33680868994202e-19, 
3.68852233886719, 6.35607347439413, 6.26256895065308, 5.54542732238769, 
12.291187286377, 9.00999546051025, 3.80466437339783, 1.98400064879446, 
1.05021327374645e-18, 1.5454273223877, 2, 2.60266542434692, 2.66866777332443, 
6.57737827301025, 8.03528213500976, 1, 4.77771091461182, 0.992000324397229, 
1.64138238444698e-17, 0, 0, 0, 1.16624537842285e-16, 0, 0, 0, 
5.50106570272985, 2.28952193260194, 0, 0.993652828904905, 0, 
1.05043304461634, 2.86023664474487, 2.97600097319169, 7.9797101020813, 
3.17337989807129, 3.9494252204895, 0, 0, 0.709752045986858, 0, 
2.94609355926514, 7.20777576402045, 12.3281364440918, 16.1423887016262, 
4.53745524967703, 0, 0.992000324397229, 2.60565374598256e-16, 
1, 0, 6.09085464477539, 4.11614179611206, 7.7524242401123, 10.177159164534, 
8.97804450988769, 1, 2, 0, 0, 1, 3.94291643525986, 17.53346824646, 
11.0975189208984, 16.4426116943359, 10.5228043444165, 0, 0, 2.22305059615379e-15, 
1.84535535504253, 0, 0.992000324397229, 4.28785610198975, 7.29118776321411, 
8.11791101037718, 8.0941858291626, 1.22124532708767e-14, 3.20854735374451, 
0, 1.32693525358316, 1.4357852111509, 4.08612172030681, 3.71720716437306, 
2.63094080945218, 0, 0, 0, 0, 0.881779457574253, 0, 0.051515536377956, 
0.607087389652441, 3.48624684303342, 6.84495715001546, 0, 4.47851024600072, 
0, 0, 0, 1, 0.66876768568946, 0, 3.10656246678781, 0.595463788958862, 
0.896241357252764, 0.190895059285768, 3.65833803626564, 0, 1.38683568069631e-16, 
0.861219366031974, 0.971395888335697, 0.766278522215154, 0, 0.409346066714036, 
2.63797034173662, 3.16176702499747, 1.67152810356095, 0, 0, 1, 
0.999999999999999, 0, 0, 0, 3.02136850357056, 0, 0, 2.72944287496511, 
0, 0, 1, 0, 0.743148416553818, 0, 3.44865867355519, 1.71502789701214, 
0.940210558859212, 4.79116916656495, 1.12222254276276, 0, 1.52507174015045, 
0.735438395606829, 0, 3.28124326193227, 0, 0, 0.748148381710053, 
0, 2.30775779731911e-17, 1.1187465381658, 0, 1.45303628532784, 
0.630367109671548, 1.30382598052581, 0, 1.60373623314854, 4.17629625320792, 
3.69789222718, 0, 0, 0.97487189293265, 0, 0.151976471179612, 
1.00343375000323, 2.74623316186912, 0, 9.02108478546143, 4.49629688262939, 
1.2660973072052, 0, 4.38885039422132e-16, 0, 1.6149470249572, 
0.345245392325916, 0, 0.273135511095619, 0, 2.31759056390502e-15, 
0, 1.1089129447937, 9.96425164601078e-15, 1.10891294479372, 1.54015696048736, 
0, 0, 5.34988719991247e-15, 1.16408447221402e-15, 1.15532583500055e-15, 
0, 0, 2.31023526191712, 1.79717352111197e-15, 9.15933995315754e-16, 
8.88178419700125e-16, 0, 0, 2.32973362823685e-15, 0, 1.50053580671994e-16, 
0, 1.10328413072125e-15, 2.13024042849952e-15, 1.9151347174784e-15, 
1.69417262077332, 0.999999999999997, 0, 1.13060602546788e-15, 
1.47855067253113, 1.67747760126957e-15, 1.17961196366423e-16, 
0, 0, 1.99840144432528e-15, 1.11022302462516e-15, 0, 0, 1.4584687624275e-15, 
7.25114412958305e-16, 8.2052420413703e-16, 9.0009984522613e-16, 
0, 6.65266453037106e-16, 0, 7.0082828429463e-16, 9.87057657830803e-16, 
2.89336290386702e-16, 4.35068647774983e-15, 2.32799890476088e-15, 
8.59528377292196e-16, 0, 0, 0, 9.55832635263221e-16, 0, 1, 3.31939337128162e-15, 
0, 2.89959029009524e-15, 0, 6.5225602696728e-16, 1.55271845761254e-15, 
1.75640751942652e-17, 0, 0, 3.58046925441613e-15, 0, 0, 0, 0, 
8.90678298477604e-16, 4.4825605319005e-16, 0, 8.88178419700126e-16, 
1.60982338570648e-15, 0, 2.44249065417535e-15, 0, 9.19403442267708e-16, 
0, 1.11889664200504e-16, 1.07810986042023, 9.38485400503453e-16, 
8.81673206665213e-16, 9.61036805691152e-16, 3.09040987245268e-15, 
1.47104550762833e-15, 2.80308556556702, 1.97140085697174, 2, 
0, 4.02672686861116e-16, 6.97358837342677e-16, 2.08166817117217e-17, 
1, 2.19615992058664e-15, 2.11636264069171e-15, 0, 0, 0, 0, 0, 
0.775508801336946, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 1.67714415858495, 0, 0, 1.96056291944141, 
0, 0, 0, 0, 0, 0, 0, 0.8966478726323, 0, 0, 0, 1.27456875598643e-06, 
0, 2.04885730711943, 0, 0, 0, 0, 0, 1.1409670868568, 1.12058342035575, 
0, 0, 0, 2.28771017920555, 0, 1.2987910350456, 0, 0, 5.44463169065426, 
0, 0, 0, 0, 0, 0, 0, 0, 0.996174781389508, 0, 0, 0, 2.54913751197471e-06, 
0, 0, 0.908703724790065, 1.85862501576732, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0.918167274899182, 0, 0, 2.35025567748421, 0, 0, 0, 
0, 0, 0, 0, 0, 0.992620217843248, 3.71107050044092, 2.99065549962508, 
26.0992804725768, 46.723998883169, 48.0446766968363, 3.49428005778252, 
1.50424768661648, 2.30328092589097, 0, 0, 0, 0.99480013184276, 
0, 2.0643580648551, 0, 2.78392919726839, 4.06286151819183, 0, 
0, 0, 1.71920868204171, 0.989820953035748, 0, 1.65705846304526, 
4.59930073700623, 0, 1.97995785371582, 1.03060848716999, 2.0856383448293, 
1.16233220356877, 0, 0, 3.08137762233116, 0, 0, 0, 0.981157329036994, 
1.1500124133057, 4.88150833764574, 0.985927035393028, 9.92620317499116, 
0, 0, 0, 0.977261540460999, 3.64866885712838, 0.976624441703048, 
5.94664644371681, 0.742538628525145, 2.63834708174338, 6.32686517725265, 
1.59474797324535, 1.43991593859482, 0, 0, 0, 0.996084610972154, 
18.5148827614085, 7.08912778933402, 0, 0, 0, 2.35114287764918, 
0, 3.15972411046486, 0, 5.29471050275239, 10.287923493941, 15.6280660262738, 
0, 0, 0, 0, 0, 1.08100238770433, 0.985258966485847, 8.49704859188724, 
12.3240445231508, 8.82495575033763, 1.11380722534883, 0.992114891068184, 
1.99504603076122, 0, 4.13761502476452e-07, 2.34996574303253, 
2.7485662517485, 5.96725715780123, 8.6612782621781, 12.4448418774053, 
3.38376871732203, 11.8921981901292, 6.63759289229189, 0.997436558966224, 
0.99344873889235, 2.16086332413571, 6.43814789245425, 10.4307068622984, 
7.86226418065221, 7.47290125618037, 0, 0, 0, 1.32209572724313, 
3.23282895138826, 15.3172211620649, 10.1692050723327, 6.24193927783342, 
10.3776392328837, 5.55487266534121, 0.996358810003295, 0, 0, 
1.34036637510126, 4.1666428608825, 0, 11.2634745662229, 5.16549869171901, 
4.61567392707054, 0, 0.972194385894232, 0, 1.96464096148577, 
1.4100677016441, 1.93910649304904, 1.80791530078056, 0.970946518972311, 
2.87496557657718, 1.62107267540661, 1.34405946127585, 0, 0, 0, 
0, 0.962840440450023, 3.58119072966319, 0.959648800791917, 0.965751921674072, 
9.27691432097835, 5.54975307394619, 1.84689806170758, 0, 0, 0, 
0, 0, 1.6918612049593, 0, 1.94533380663924, 0, 0, 1.83550505756162, 
0, 1.86693106661863, 0, 2.66067900420716, 0, 0, 0, 0, 0.971346292123234, 
0, 0, 0, 0, 0, 0, 2.39327313280866, 0, 0, 0, 0, 0, 0, 0, 0.973960463202073, 
0, 0, 1.73010725209785, 1.90655187676347, 0, 0, 0.947615448828071, 
0, 0, 0, 0, 0, 1.45783138648969, 0, 0.90524187650237, 0, 2.4606499431827, 
0.976138861971448, 0, 0.901081989761877, 0, 2.35464711177813, 
0.773778021600606, 0, 2.03906003198086, 0, 0, 0, 1.50232516726984, 
0, 4.92772679122885, 7.26411112569211, 3.15271674450656, 0.935364249484465, 
0, 0, 0.991990371399239, 0, 0, 0, 1.89501716957646, 1.70413586146648, 
1.00293645605634, 0, 0, 0.975831705570756, 0, 0, 0, 0, 0, 0, 
0.974384982329685, 0.968927904636651, 0, 0, 0.646676354236437, 
0, 0, 0, 0, 0, 0, 2.28104982551146, 0, 0, 0, 0, 0, 0.990076442625835, 
0, 0, 0, 0, 0, 0, 0.986000384175726, 0, 0, 0, 0, 0, 1.92687267167022, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.10638735122659, 0, 0, 0, 0, 0, 
0, 0, 0, 0.917315309164282, 0.946975265738423, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 7.24611587337121, 
18.8255828483467, 21.3181829104965, 16.1719854674103, 6.02110324645206, 
11.6937361196224, 4.04307943110539, 1.18181862326194, 3.67546403797968, 
0, 1.96778853770038, 1.42583793208273, 2.41217087725159, 1.58592155992732, 
3.2909401120439, 7.17218104462502, 4.62403172322747, 2.59801747037862, 
6.02719222197665, 2.35463423842924, 2.44448898464802, 2.93586688433001, 
1.93943426137485, 2.99428616215787, 1.95495545638223, 4.06528874253507, 
0, 6.34798407362015, 15.1171523237721, 0, 0, 0, 0.959514048124899, 
4.30377183378545, 0.954422186837734, 9.94529362488725, 4.45941146022137, 
7.82857645827302, 0.936191529654334, 0.98986150461869, 0, 2.80867290072567, 
0, 2.49795480663307, 0.946384241105425, 4.17251450834921, 0, 
19.9525844087676, 1.84196500624386, 3.31844998099537, 1.68832648619568, 
0, 2.8908650741501, 2.9269927108032, 0.583335744643326, 1.92567918648416, 
3.46481703890456, 6.03600253434178, 4.38322558523872, 0, 0, 0, 
1.98494992504955, 4.55405302465032, 5.58293958686381, 7.48533354214908, 
6.77959369102088, 1.9991439731888, 0, 0, 2.67563848844028, 0, 
0, 3.84147726359843, 1.95498688991774, 10.5151578080411, 2.71881118592146, 
0, 0, 0, 2.34111188646542, 0, 0.993467830526802, 3.59405612853078, 
6.20163865115175, 0.964116214897337, 4.67372338101189, 0, 0, 
0, 0, 0.987344567087694, 3.23849830603649, 5.86086847278653, 
2.10992679507859, 10.3859569153925, 7.19787238323684, 0, 0, 0, 
0, 0, 0, 0.937549979023569, 0.96590486926234, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0.97802586915424, 0, 0, 0.982543929885304, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0.946846680511873, 0, 0, 0, 0, 0.985471696305035, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.07874421675303, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0.979353489058951, 0, 1.21908487271677, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.959348879880003, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.7056740662025e-16, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 4.51316315136747, 2.9797545287526, 5.93877716564675, 
11.7246465885551, 19.1468714910557, 19.264942085153, 15.5140764585581, 
2.17084262841158, 6.22173716021972, 0, 1.08399262407033, 0.989133966417504, 
4.15869450242979, 3.03229239055042, 3.15159609866891, 3.56686149478445, 
4.68392740201527, 0, 3.85686265913818, 1.98038560243083, 1.48464253988189, 
0.982039090218478, 2.23503224919863, 2.73318157399547, 5.88957662234597, 
4.24507783747301, 4.48071687281385, 0, 6.07327338009078, 2.12786314323814, 
2.08662196958612, 2.44915215732457, 0, 4.75175598337228, 3.62180706894688, 
2.95024115849102, 5.17527484800005, 9.96980546296528, 6.44134626957465, 
0, 5.58078945239677, 1.51836954428729, 0, 0, 0, 0.986981351119341, 
6.00525730054618, 2.41837295615882, 0, 2.41843247746165, 0.808652539436696, 
0, 1.85294625622782, 1.2223880262433, 0, 0, 0.997675119674935, 
3.32910984435427, 0.905703052747756, 1.78218402447711, 0.701829259626598, 
0, 0, 2.4355657418854, 0.992012883925268, 0, 1.95885798878004, 
0.902292783735391, 2.99579789383886, 0, 0.999678266502685, 0.523763042124772, 
1.05605617008153, 0, 0, 3.75901684638467, 2.76375289011377, 3.04903628824869, 
2.60027998225451, 0, 2.99025866182936, 0.999687072934815, 0, 
0, 0, 1.2343057270941, 1.95802305622734, 1.11684197764861, 0.948551176351896, 
2.99897023175916, 0, 1.98644300018451, 0, 0.983174462571218, 
0, 2.3721675196565, 0.943860973211598, 1.89387530785292, 1.66697888085344, 
0, 0, 1.98490541110802, 4.71649413132305, 7.85668515169288, 9.79624925106196, 
0.908998539817826, 2.18147470258401, 4.03041107753703, 2.64286829426888, 
0.999350756456367, 0, 0.995212851619672, 0, 0, 3.71871662825662, 
2.43476378950136, 3.24646455429481, 0.461698423959009, 0.981089303338565, 
0.987919582722419, 0, 0.995219331402824, 0.988969312413052, 1.08595705797038, 
2.86495813100093, 0, 1.73562075464739, 0, 0, 0.990197657868176, 
5.87425959378804, 2.84227736491564, 0, 0, 0.982904421623294, 
0, 1.01248977039672, 1.08766082889005, 4.79464698555775, 10.8819039466998, 
2.42042405787973, 1.53263713554463, 1.72751432276255, 0.999239365724674, 
0, 0, 3.13812173583936, 1.30117244615611, 0, 14.8931886905445, 
20.0848993553902, 0.999213742862738, 1.98902667202202, 0, 1.19220065030322, 
0, 0, 0.984447390979039, 5.27333315972821, 21.3628747266946, 
26.8366843082295, 5.23967274031368, 6.87295931237028, 0.9890304446657, 
0, 3.0721109851285, 2.24747481975278, 7.17478376796265, 0.985801416470356, 
0.999298030417987, 0, 0.997242122989395, 0, 0, 1.57045274916292, 
2.04982639274863, 1.30546993770187, 5.20310170732832, 1.98779455245146, 
0, 0.986652059734956, 0, 0, 0, 1.4120659312188, 0, 0.9832167268394, 
4.29874165728505, 3.56541253846067, 0, 7.05499541032829e-16, 
0.988384952889795, 0, 1.21984202935272, 0.999228382182158, 0.981760668529461, 
5.25619438681806, 7.49336663914548, 6.03583040133114, 0.999311419899188, 
0, 0, 1.30368610778958, 0.741806950160405, 0.652672217048198, 
0, 1.85182284765465, 0, 1.09955810673795, 0, 0, 0, 0, 0, 0, 0.924807623138432, 
1.25380993965351, 1.17825127299054, 0, 2.16145864158658, 0, 0, 
0, 0, 0.901218077048699, 0, 0, 0, 0, 0, 0.844925303200818, 0, 
0, 2.93287771468146, 1.09036478004269, 2.65397933432439, 1.5764515200239, 
0, 2.98764954820413, 0, 0, 0, 0, 0, 2.39372541031224, 1.81889789306775, 
3.01443149932707, 0, 0, 0, 0, 0, 1.80325661030423, 0, 0, 0.99711840033643, 
0, 0.962881112707068, 1.94509262315938, 0.563291430370153, 2.50007626671538, 
0, 0, 0, 0, 0, 0, 0, 0.952139781332805, 0, 0, 0, 0, 0, 0, 0, 
0.951723952627109, 0, 0, 0, 0, 0, 0, 5.60154800388797e-07, 0, 
2.94201161977877, 4.18115085471754, 0, 0, 0, 0, 1.88826941159817, 
0, 0.966799336742368, 0, 0.954139659151126, 0, 0, 3.22362369284714, 
0, 0, 0, 0, 0, 0, 0.98110099463274, 1.59538541531699, 3.14671225702721, 
0, 0, 0, 2.62113029610151, 1.99970895265624, 1.66738700253592, 
0, 0, 0, 1.98697387796344, 1.48409420610417, 1.13248741279485, 
0, 0, 0, 0, 2.46123993988353, 0, 0, 1.99966109899963, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 2.1367233419886, 0, 0, 1.01054819472431, 
0, 0.996191340652805, 0, 0, 1.69385169038649e-20, 1.92632088814965, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.999778432861994, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0.999838008978001, 1.99973329631259, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.999873556204156, 0, 
0, 0, 0, 0.999775842739993, 0, 2.91258064308903, 1.9997754387581, 
0, 3.49878859161763, 15.8233156032798, 22.1811662192759, 28.1748128891705, 
31.5065116074696, 25.3594665902708, 19.6520190620747, 0.993873123385241, 
2.0446210894342, 0, 1.9953764441461, 6.6631438095452, 4.99813297029995, 
2.85308122213786, 9.07174422153508, 8.06126866472671, 6.73060735759212, 
0.991449561437307, 0, 0, 1.31897928849872, 2.51728127573262, 
7.96057661697546, 7.11527594359703, 6.06961711265027, 3.99515767040455, 
4.99944816473209, 0, 0, 0, 0, 2.99966889883925, 2.19698057111063, 
11.5429332240176, 9.31998718006339, 4.22251154625989, 5.73480870089277, 
0.934376019516758, 0, 0, 0, 0, 0.999889632946417, 0, 2.12070400096001, 
0, 0, 2.99544986651897, 0, 0, 0, 0, 1.98617085329044, 5.11549847316868, 
0, 0, 2.26869003028722, 0.87131489299817, 0, 0, 0, 0, 7.72997314933957, 
5.7803028015817, 0.986358894460269, 3.15247596662261, 2.22862177425179, 
0, 0, 0, 1.86785322453224, 1.99977926589283, 2.42825202883175, 
0, 0, 1.70327268833705, 0.98351834672948, 0, 0.993946096131344, 
0, 0, 0, 0, 0, 0, 0.974009410096742, 0, 0, 0, 0, 0, 0, 0, 0, 
1.04474557978464, 0, 1.13502744266145, 0, 0, 0, 0, 0, 0, 2.7832797488093, 
0, 0, 0, 0, 0, 0, 0, 0.966822049552195, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.995053024336076, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.999947070082766, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.994984743129632, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0.99916674138475, 0, 0.999947070082766, 
0, 0, 0, 0.999906592556335, 0, 0, 0, 4.89725086550715e-17, 0, 
0, 0, 0, 0, 1.01156191570681, 0, 0, 0, 0, 0, 0.993872561879868, 
1.63615870391508, 1.18235783382443, 4.24267181095237, 0, 0.747932533597037, 
0.727257463898566, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.39139128602099, 
0, 0, 0, 0.715299461934668, 1.33892101254097, 0, 0, 3.33689524345218, 
0, 0, 0, 0, 0, 0.999914153916643, 0, 0, 0, 0, 0, 1.3903844788749, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.989897286537944, 0, 0, 0, 
0.975931446340035, 0, 0, 0, 0.958050020837507, 2.02841592986568, 
0, 0, 0, 0, 0, 0, 0, 2.72805636429105, 0, 0, 0, 0, 0, 0, 0, 1.10718676412045, 
0.996026042355679, 0, 0, 0.997292694835001, 0, 0, 0, 0, 0.995653023257284, 
0, 0.996816869162073, 0, 0, 0, 0, 0, 0, 0, 0, 5.14861810800076, 
0, 0, 0, 2.17118320276056, 2.05783869952293, 0, 0, 0.745060033946956, 
0, 0.913615780813207, 3.06646470911311, 0.956793283772368, 0, 
0, 0, 0, 0.997454260133457, 0, 0.965011559357622, 1.92350870372552, 
0, 0, 0, 0, 0, 0, 0, 0.928707180118975, 0, 0.965415788183191, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.67921457652671, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.70257314343934, 1.56538934304896, 
0, 1.8704970239841, 0, 0, 0, 0, 0, 1.09971653760062, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 3.167851561276, 1.51538536778242, 
4.9810143324321, 15.5639021681699, 26.6546211523591, 22.2911626617351, 
28.3929970574318, 8.52277750907837, 4.40717196815305, 4.6345609649098, 
0, 0, 2.99528928718392, 2.48211455556608, 3.798437526151, 3.73699695417994, 
5.77292661761956, 1.67314600939249, 0, 4.99055303055779, 0, 1.91793132201949, 
1.77730418616115, 0.990732416885309, 7.224389203511, 11.2166097252925, 
3.69528797059293, 3.9919912086893, 0.969112678860469, 0.981514495348186, 
2.46134429890155, 6.1674055437237, 0.999726765112071, 1.054836414676, 
3.23729936370579, 8.70904250147266, 13.8390964184999, 9.29760033244939, 
3.29269247903994, 9.22118815755061, 0, 0, 0, 0, 3.67045268658101, 
4.31003022904568, 3.26925253725948, 4.67648389636175, 1.21465638308958, 
5.11904523457071, 3.1368157181666, 1.3743277959963, 1.01858896384065, 
0, 2.35500816730256, 3.88691744059274, 5.09927578813576, 6.8233039606109, 
0.999582853780703, 0, 0, 0, 0, 0, 1.99533793779137, 3.7878135082608, 
0, 0, 6.26123762139148, 2.75783113309082, 0.999624663266662, 
2.65312576564575, 0, 3.54817361341127, 0, 0.995345192646356, 
9.21246142505304, 0.992543795074951, 5.05308864045898, 2.86025543062592, 
2.08651120151054, 0.988294468007717, 0, 0, 1.31055258334889, 
1.99943052204727, 3.50180920688368, 4.89564377770953, 2.99517846214979, 
4.36489612128204, 0.999679867835925, 0, 0, 0.993976120871325, 
0, 3.27805025191507, 3.77180079450803, 1.99700251612555, 7.10272309489461, 
4.54439232989107, 15.3286834343821, 1.96939093932629, 0, 0.78933635884004, 
4.32250013656867, 18.3157478718181, 17.3998445158776, 25.1292857373081, 
14.1568236564521, 12.9304025829288, 0.899170935565527, 2.47757940449948, 
0.958796729751309, 3.63587642420001, 3.23322307146582, 1.94816314886932, 
0, 5.88611343050354, 3.83380482306317, 3.14418011764666, 0, 0, 
2.83910865438245, 1.98633076137845, 0, 1.84871579051125, 11.0207425847597, 
2.22122440428598, 6.20638655306173, 3.98519471940261, 0, 2.08303511063292, 
0, 0, 0, 6.05901836265917, 6.70899814836141, 3.21984708826934, 
1.95482161831511, 5.67304240805247, 0, 0, 0, 0.99983527539689, 
0, 3.23917822514566, 0, 1.93660819717552, 0, 1.11968245684848, 
0, 0, 0.977413040299881, 3.86271364933245, 4.27722149887101, 
4.3737524160965, 2.29516318457578, 0.90826151500871, 0, 0, 0, 
0, 0, 1.2527115652439, 0.973078241398699, 3.64738135448745, 0.962128369712078, 
2.02336108488841, 3.82246821611957, 0, 0, 0, 0, 0, 1.99967055079378, 
0.98614520989518, 0.875979347236624, 0, 0, 5.21222267723891, 
0, 0, 0.999640396451219, 0, 0, 0, 0, 0, 0.980316746502899, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0.938652070816976, 14.0026377373376, 
4.68661483165998, 0, 3.5634593594624, 0.593199951875648, 8.48445625399473, 
2.39273238997098, 1.40650974881006, 1.46577969589183, 0, 0.991937496662977, 
0, 2.91465115463414, 2.15768408505984, 0, 2.07763520936468, 0, 
2.07119394827887, 0, 2.9027907641646, 0, 0, 0, 0, 0, 0, 0, 0, 
1.96416474231715, 0, 0, 0, 0, 0, 0, 0, 0, 2.02644609931999, 0.973372960584389, 
0, 0.992294943297586, 0.663869287250416, 0, 0, 0, 0, 0, 0, 0, 
1.20813099375312, 0, 0, 0, 0, 0, 0, 0, 0, 0.856504473162063, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0.878910769478323, 0, 0, 0.999951208403361, 
0, 0, 0, 0, 0, 0, 2.1486810663296, 0, 1.63395392874941, 1.98653630203706, 
0, 0, 2.83582906290605, 0, 2.23475965166747, 0, 1.24460969789098, 
0.708714290184693, 2.29271437408225, 0, 0, 0, 0, 0.983178095609999, 
0, 0, 0, 0.933670995049245, 0, 0.960287670660678, 0, 0, 1.84662439979044, 
1.02245759443099, 0.666032628001255, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 1.3131353175956, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.23409296832478, 
0.979667968989189, 0, 0, 0.96901503078141, 0, 0, 0, 0, 0, 0, 
0, 1.88955125752693, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.83180533996275, 
0, 0, 0, 0, 0.968678576694835, 0, 0, 0, 0, 0, 0.998812107279932, 
0, 0, 0, 0, 0, 0, 2.14499738477321, 0, 0, 0, 0, 0, 0, 0, 0, 2.80202187060682, 
3.44915067525821, 2.09554264326067, 0, 1.66831898544138, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 2.28214115313041, 0, 0, 0, 0.977001730881877, 
0.976116309503424, 0, 0, 0, 0.998550898897792, 4.92130561647616, 
0, 0.656070812560455, 11.6447428916346, 18.482630121462, 25.3453771786383, 
15.1596953173453, 0, 0, 0, 0, 1.42638644211838, 2.97882550658672, 
3.72656520282957, 2.18437157738958, 5.71885603784535, 6.52983154196244, 
0, 0, 0, 0, 0, 0.961467267470709, 0.785543321096881, 2.57548804556656, 
4.41821699044523, 7.25856722965087, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0.997974932422509, 0, 0, 2.74692697986733, 0, 
0, 0, 1.95143270779694, 0, 0, 0, 0, 0, 0, 0, 0.997827027257564, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.95775359852547, 
2.09983597762197, 0.941609130330623, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0.944167058208164, 0, 0, 0, 0, 0, 0, 0, 31.4318296197299, 
4.90006107655631, 0, 5.2391040594978, 46.7104394620885, 44.3041717434284, 
26.0417188989614, 36.083867293626, 16.6215721715233, 10.2809195971614, 
5.34204061417555, 2.96119129580351, 1.69360711021496, 1.24676524367323, 
4.06212405231416, 0.872477832306313, 7.88125477473249, 8.28855805807616, 
8.9909225008127, 7.18917929332734, 4.72667833757463, 1.12079030442333, 
4.20765329148485, 1.97576435885675, 2.85670391585506, 1.62347409117766, 
9.74302613564692, 2.96380942151817, 4.04966481530511, 7.35810919654629, 
2.43614832573262, 0, 1.163738822599, 0.99667686042224, 0, 1.76869499757306, 
3.20260162647791, 2.99418315883933, 0, 1.77209378557568, 0.940991688589516, 
0, 0, 0, 0, 0, 0, 0, 0.97251736819629, 0, 0.819097882311817, 
0.910078505881108, 0, 0, 0, 0, 0, 0, 0, 0, 2.18805508260398, 
0.965221178531987, 2.77232371757229, 1.55205780534423, 3.71263930965656, 
3.85456915972365, 6.0465771363823, 2.95013567979468, 2.75396718319826, 
1.62939508021048, 0, 1.99330288067077, 0, 1.43595471375114, 0, 
1.92625967988049, 0, 1.13727187781519, 6.18567531610731, 4.79197314636521, 
0, 1.06646712510723, 0, 0, 0, 0, 0, 0, 2.98310486956947, 0.949122171268763, 
4.68837087695326, 4.80405084947483, 2.48120208353503, 0, 0, 0, 
2.1892731124322, 0, 1.08983769886659, 4.72857072189587, 0, 0, 
0, 1.9735894185054, 1.64481349402564, 0.33164350749378, 0, 0, 
3.94235419657538, 0.445613817253004, 0, 0, 0.903295152586684, 
0, 0, 0, 0.528766566812821, 0, 0, 3.66855779771802, 0, 0, 0, 
0, 0, 0.903995646170433, 1.46178050499445, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.10186863144375, 
0, 0, 0, 0, 2.29845497815299, 0, 0, 1.09301773087694, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 4.36479621169232, 0, 0, 0, 0, 0, 0, 0, 0, 0.930336425257488, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.949407971673896, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 1.18780282695461, 0, 3.69592624949848, 
1.18096185528684, 2.93363705627718, 0, 1.94618073450162, 3.42682971488453, 
0.761474441680742, 0, 0.952776689979379, 1.26110331845976, 0, 
4.30412262532874, 1.32125491801121, 1.7858825731149, 0, 0, 1.79268395183242, 
0.918020463377231, 0, 0, 0, 0, 0, 0, 0, 0, 0.840478206552524, 
0.958194372513741, 0, 0, 0, 0, 0.952561280852965, 0, 2.01677302275281, 
0.940540860436682, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.98114176171866, 
0, 0, 0, 0, 0, 1.05862634911252, 0.955823219980241, 0, 0, 0, 
0.96677408271133, 0, 0, 0, 0, 0, 0, 1.18767595974687, 0, 0, 1.26683907747477, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.65866223696564, 0, 
0, 0, 0.94502696392076, 1.22530994691587, 0, 0, 0, 0, 0, 0, 0, 
33.4154532760582, 33.4102805059015, 5.33280258187478, 37.9211175322267, 
106.247751423818, 106.240665751083, 51.7390341720925, 11.6314534826595, 
5.44761163301194, 6.70147970818632, 6.9469232649681, 5.88344746114685, 
0, 0, 2.51739722319925, 3.13786878055455, 0.99150089309517, 1.30675173781788, 
0, 0, 16.1518122999958, 15.8938395549744, 1.01288579352005, 5.88831438201313, 
3.77738243945759, 7.69216784185123, 0.999214020257949, 3.40488763215289, 
3.61398754500689, 0.996042744699365, 0, 6.54168662343328, 5.5485756663406, 
0.999962837783221, 8.14956748081956, 4.00872714843006, 4.89436536085107, 
1.99127086166506, 5.6160035370312, 3.48306776016461, 0, 5.42394404978703, 
4.18249370098574, 8.37175373014102, 3.3853118042728, 7.67864266452161, 
0.999852552588472, 0.999698714476848, 2.17620364842816, 1.1762500396855, 
0.999852678999973, 4.33119013552781, 8.39142194579294, 11.0775493494673, 
4.81006860406447, 15.2273337940777, 2.12392066465841, 10.824583307373, 
0, 0, 0.999880982684424, 1.50302413057812, 1.13894400777654, 
1.99980443648994, 1.60050124079071, 4.01282776649487, 2.67936661391756, 
6.93378774666281, 6.27392511647608, 13.6668956851369, 0, 0, 0.994572816519341, 
1.96048023396197, 1.14365778522261, 0, 0, 0, 0, 11.155805662549, 
0, 0, 0, 0, 0, 0, 0, 0.988369969352124, 0.999902103799036, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.31233483097074, 0, 0, 4.73967418594567, 
1.64155170314431, 0.653481923842659, 0, 0, 3.95354379622929, 
1.9196755277819, 0, 2.70122305611337, 0, 0, 0, 0, 2.30017342900036, 
0, 0.809850127367835, 0, 0, 0, 0, 0, 0, 0, 1.65063776610238, 
0, 0, 0.991070961647296, 0, 0, 0, 0, 0.918992474044233, 0, 2.1775690152556, 
0, 0, 0, 3.52793314309243, 0.968108696343155, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.940192060841979, 0, 1.30572080457366, 
0, 0, 1.63116900531255, 0.4656706209481, 1.59264336849674, 0, 
0, 0.957145965789483, 0.916984323952578, 0.997144804202777, 0, 
0, 0, 0, 0, 0, 0, 0, 1.99304079353503, 0.9054470456427, 0.999551974458954, 
0, 0, 0, 0.989233049887892, 0, 0, 0, 0, 0, 0, 0, 0, 1.69909638417751, 
0, 0, 0, 0, 2.25458554122459, 2.19799743216038, 0.96254433085122, 
1.44101305628546, 0, 0, 0.936886612040744, 0, 5.63764195355749, 
0, 1.49370903202726, 2.91840701189367, 0, 0, 0, 0, 0, 1.19979880641546, 
1.29501244082809, 2.02719375694743, 2.8789562583123, 1.60290425826675, 
0, 0.995010879079432, 0, 0, 0, 0, 0, 0.998580721222466, 0, 0, 
0, 2.781103536498, 0, 0, 1.96722374894254, 0.995591347968341, 
3.10143176891242, 1.0164266720591, 3.97721280668029, 2.36842009689824, 
0, 0, 0, 0, 0, 2.99600250451671, 0.987693488724008, 3.24347532845531, 
1.11193399227521, 1.50842654772643, 0, 0, 0, 0, 0, 0.997923763791959, 
0, 0, 2.69928480939489, 2.47736948845946, 0, 0, 0, 1.4008773197761, 
0, 0, 0, 0, 3.24783662127711, 0.978554350724261, 0, 0, 0, 0.998725317575341, 
0, 2.3940293855828, 1.90210038036328, 0.995831291607588, 0, 3.02828953636355, 
0, 0, 0, 0, 0.978824146116992, 0, 0, 0.952853229475935, 0, 0, 
1.17763083469681, 2.99122399770869, 0, 0, 0, 0, 0, 0, 0, 0, 0.441067153817445, 
0, 1.50558562492054, 0, 0.920244302255254, 3.00568600672966, 
2.30204555822923, 0, 0, 0, 0, 0, 0, 0, 0, 1.17783376934357, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.926115850315807, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.967953391816184, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0.889820294771646, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 3.07852379931472, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1.88429459352315, 
0, 0, 4.24942916521734, 2.73793779367354, 2.95965597305516, 0, 
3.06749780101469, 3.98940987989387, 7.37509900684099, 3.45031325301922, 
3.40796072499491, 3.7683352043852, 2.0218276937933, 0, 0, 0, 
0.999918787391957, 1.11484074008827, 0, 4.19823362678763, 0, 
2.28540558008734, 1.2845178706014, 0, 0, 0, 0, 0, 0, 1.51739224424414, 
1.02248430489901, 1.99916136313595, 0, 0, 0, 0, 0, 1.74756581069485, 
2.78114170284978, 0.999909578360571, 0.998298291573362, 1.99783172524901, 
0, 0, 0, 0, 0, 0.999841843194212, 0, 5.7810436593439, 0, 0.99985424857627, 
0, 0, 0, 0, 0, 0.999876487032337, 0, 0, 0, 1.1204900278832, 0, 
0, 0, 0, 0, 0, 1.88022905819878, 0, 2.77752108811725, 1.12145911775166, 
1.88031629497625, 0, 0, 0, 0, 0, 0, 0.999140874751457, 3.25208343520479, 
2.5390686029246, 0, 0.999951523352297, 0, 2.15454376866197, 0, 
0, 0, 0, 0, 0, 2.24240183578702, 0.998432074014728, 0, 0, 0, 
0, 0, 0, 0, 0, 1.96920655061374, 0, 0.974083716777066, 2.24059539585887, 
6.65559088308297, 6.97682226426685, 1.66854620318998, 1.43166037642046, 
0, 3.15575182533912, 0.98846959414499, 0.993033237214696, 0, 
0, 0, 0, 0.989991968277154, 1.96155061514719, 1.98088511408594, 
1.33696183595385, 2.43913050308992, 0.97978505541792, 1.18694567033143, 
1.99798569334919, 0, 1.02439384250597, 4.08318826238862, 0, 0, 
0.987222837092533, 2.08707113360467, 2.04067449018448, 2.31433112772646, 
0, 0.985605961809665, 0.985853942984443, 0, 0, 1.89765148672369, 
2.49845483004182, 2.35081417523805, 1.05667658838825, 0.999808616602025, 
0, 0, 0, 0, 0, 0.991072147477504, 0, 3.35338092730933, 0, 1.48731054897576, 
0, 0, 0, 0, 1.12037447282068, 4.11426448708962, 1.26679482096048, 
2.94803089051801, 0.995681857912983, 0, 0, 0.997767255448351, 
0, 0, 1.99709517672123, 4.50197041487667, 0, 0, 0, 0, 0, 0, 0, 
0, 0.98844324853052, 1.76725538859253, 1.19646661074547, 0, 0, 
0.996467860954983, 0, 0, 0, 1.72220871747615, 3.01623503018616, 
1.98908263030213, 0.992486204601948, 0.97931303338059, 1.76521690231805, 
2.45264621655165, 0.997020924589585, 0, 0.999760235416918, 0, 
4.25329094114522, 1.31610416547833, 0.99509084081943, 0, 0, 0, 
0, 3.89183179948756, 5.64185106880616, 4.87555467676608, 0, 1.98274271111091, 
0.962132727812604, 0, 1.27026815405767, 1.01740155953841, 0.995219802928146, 
3.42106069358606, 0, 1.50678885825327, 3.4502024176138, 2.86698939343741, 
0, 0, 7.3861030493793, 1.50916025584975, 0, 0, 0, 2.18012402438444, 
1.01793578138283, 11.1864873393219, 0, 1.79898149174958, 0, 0, 
0.995967459609849, 0.984803042857088, 0, 1.98621434923127, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0.978698317187126, 2.79328544992986, 
1.52395141556545, 3.1723676502549, 0, 0, 0, 0, 0, 3.37952230647265, 
0.988383604079917, 0.982437817921392, 1.93987614742549, 3.20626643948841, 
0, 0.972696382362366, 2.25039169143944, 0, 0, 1.81374438956508, 
6.61435616477, 0, 3.68683522046531, 6.2777535083013, 0, 0, 0, 
1.25512564140941, 2.77341479974202, 1.61771187836422, 0.981997282272236, 
0, 1.64890396256316, 1.14074474849808, 1.67394743850709, 0.99029849245532, 
1.24338060315466, 0, 0, 0, 1.62970099883945, 1.64661472173042, 
4.10948996384609, 3.15625516357471, 1.61070290226884, 0.938197294697314, 
0, 0, 0, 0, 0, 4.16429848969917, 1.7419401113677, 0.986612161786603, 
0, 2.38205194942861, 0, 6.61365292185319, 12.1058237247656, 8.51494489049488, 
6.21504783646444, 2.07488782922631, 0.704234415898973, 1.96069321746438, 
0, 2.33416872396778, 2.25964131205269, 0.938435851073227, 0, 
2.11522900714576, 1.90621036871933, 3.2152056716248, 8.17327003103642, 
2.15697902125163, 0, 0.54898479122221, 0, 2.95698427270827, 2.80246338115297, 
1.06206500824805, 0.969384698897638, 2.23150378137383, 1.3169176206724, 
0, 0, 1.75441376433719, 0, 0.938390325761255, 0.899786629693412, 
3.35551699042575, 3.09663473907796, 6.33616081247219, 2.57720711177884, 
6.94001391186278, 2.99697119833475, 0.998981024169865, 0, 0.99901784873127, 
0, 0.999005832549863, 0, 6.87166403739955, 6.01768767028031, 
4.29654147672372, 4.64483304373122, 1.99398726341667, 0.998913200666599, 
1.99803569746254, 0, 1.72942443471894, 2.02728819485299, 1.93824982826823, 
6.10513455737838, 2.09582959817504, 6.10481115182454, 2.77321162623532, 
2.12327274901291, 1.32762040466299, 1.3607276162022, 3.4808091498275, 
2.88220696355097, 4.19069919879696, 4.3906987701622, 2.07284062031964, 
1.52825654878118, 0.970655712791457, 0.947117491392737, 1.01888149783153, 
0, 1.46134598198897, 3.06365467722344, 2.81731542212604, 4.75202661162304, 
1.92860343497074, 3.8511254387255, 1.93776895139921, 1.8160407218428, 
3.35867051207904, 1.99803171095899, 0, 1.64654450768798, 3.19549388860279, 
4.00814611474614, 0, 1.86309126995396, 11.075120662102, 5.08792556924926, 
1.99064653652117, 0, 0, 0, 0, 0.892967677496454, 1.20119057752017, 
1.19262491053158, 3.41213958535129, 0.994130620729843, 0.793367240662847, 
0.604886886086116, 2.9967958398827, 0, 6.02022397786514, 4.19901193553249, 
1.03017558898285, 0, 1.28185241552402, 0, 0, 2.2631655834343, 
2.65294697077045, 0, 0, 1.46007645926665, 0.930463342189122, 
0, 0, 0, 1.00437845228419, 0.510711362555227, 0, 2.25005486616679, 
0, 0, 0.993077726439144, 0, 0.941248669636833, 0, 0, 0.964311697765234, 
0, 0, 1.13016243613949, 4.30636459353531, 3.57132450826716, 0, 
0, 0, 0, 0, 0, 2.97865582330496, 0, 0, 0.848398552130235, 0, 
0, 0, 0, 0, 1.55636866243707, 0.929551357023995, 0, 0, 0, 0, 
2.23676404126471, 0, 0, 0, 0, 0, 0, 0.842174715820737, 0, 0, 
0.700577831456621, 1.23042993305238, 0, 0, 0, 1.56256329511322, 
4.36348485257111, 1.70457235572827, 0, 0, 0, 0, 0, 0, 0, 1.93775117664558, 
1.42317038161708, 0, 0.970757342551931, 0.931413115100071, 0, 
0, 0.935001206409392, 0, 0, 0, 0, 0, 0, 0.905808599050091, 0, 
0.945849296489454, 0.91359457807558, 1.21283017435112, 0, 0, 
2.79146499521884, 0.387189988050044, 0.929521537274529, 0, 0, 
1.44104945533444, 0, 1.18564923414369, 3.01240606076012, 0, 0, 
0, 0, 0.999354726339745, 0, 0, 0.927257684834755, 0, 0, 0, 0, 
0, 1.17285059555911, 0, 0, 0, 0, 0, 0, 1.60932783804365, 1.83812769793869, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 1.2518786527419, 0, 0, 1.44260862169506, 
3.15051049445906, 0, 0, 0, 0, 0, 0, 0, 1.97372473553402, 1.80164697667349, 
1.29531397717503, 0, 0, 0, 0, 0.923607564628052, 0.97667474380616, 
1.21686146100582, 0.961398135500419, 1.42612742357176, 0, 1.39658092453636, 
0, 1.08880727774716, 0, 0.894967881600154, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0.879520967439305, 0.633465771849723, 0, 0, 0, 0, 0, 
0, 0, 1.40103725699798, 0, 0, 0, 0, 3.35682201121014, 1.73766618320794, 
0, 0.977532655619623, 1.04079947547073, 1.99747161284596, 3.21117340571384, 
0.931459074693856, 0.990298866364604, 0, 0, 2.136417711047, 1.23606304359644, 
0, 1.44295316681811, 0, 2.03673167870392, 0, 0, 0, 0, 5.81671991494834, 
1.17078423320217, 0, 1.13698593480704, 0, 0, 0, 0, 0.971230541729794, 
0, 3.34098498528969, 1.8733624053565, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0.999860525146206, 0, 0, 0, 0, 0, 0, 0, 0, 0.922909863337154, 
0.999807188904527, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.999787870087739, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.44191162073474, 0, 0, 0, 0, 0, 
0, 2.80616475654686, 3.31165745856995, 0, 0, 0, 0, 0, 0.999219950272601, 
0, 0, 0.999588859071891, 1.37098107014227, 0, 0, 0.999860525146206, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 1.20601779375684, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0.993540612511925, 0, 0, 0, 0.988197364689472, 
0, 0, 0, 0, 0.592429848963767, 0, 0, 0, 0, 0, 0, 0, 0, 0.980355461953614, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.996238836810277, 
0, 0, 15.0173282623291, 13.4620170593262, 42.1626129150391, 240.756408691406, 
271.958068847656, 167.18391418457, 645.640441894531, 1053.37634277344, 
1053.37634277344, 1013.830078125, 11.2385807037354, 28.0888786315918, 
34.9261703491211, 28.310131072998, 92.0345153808594, 89.1191253662109, 
218.02766418457, 341.580352783203, 415.107208251953, 247.743347167969, 
14.8698120117188, 15.7808856964111, 6.42949390411377, 7.85898780822754, 
26.8741321563721, 110.951995849609, 134.279434204102, 109.45092010498, 
202.168670654297, 225.066589355469, 40.2493553161621, 20.5769634246826, 
8.92189788818359, 8.1583423614502, 13.4620161056519, 20.1734886169434, 
45.0107231140137, 57.3078918457031, 106.583236694336, 73.5074005126953, 
41.5899276733398, 21.340518951416, 3.35357522964478, 9.19086456298828, 
8.92840194702148, 3, 1, 2.42298936843872, 6.54662418365479, 8.54011917114258, 
37.2732391357422, 10.6572504043579, 7.17135143280029, 5.81777572631836, 
6.47070550918579, 2.42949390411377, 14.4468231201172, 16.3643989562988, 
14.6485614776611, 29.6159915924072, 52.0432548522949, 31.3708591461182, 
7.4273099899292, 7.16484642028809, 9.80258274078369, 17.9457302093506, 
34.3621711730957, 64.6614227294922, 89.5203628540039, 33.6463279724121, 
18.4793472290039, 16.9674282073975, 1.21474695205688, 5.72015953063965, 
7.72015953063965, 26.4836692810059, 27.9999504089355, 45.019416809082, 
88.2036895751953, 67.9889755249023, 43.2818832397461, 14.9045209884644, 
7.39260244369507, 8.98262214660645, 8.73316860198975, 25.7830200195312, 
53.4445381164551, 82.2665939331055, 142.164489746094, 114.602729797363, 
8.90670299530029, 2.04771614074707, 0, 3, 5.45769643783569, 40.1539268493652, 
67.6874465942383, 59.2558135986328, 84.9694290161133, 155.804336547852, 
36.9108619689941, 29.9179229736328, 71.9752960205078, 430.499572753906, 
478.354095458984, 255.524749755859, 1166.32055664062, 1969.42944335938, 
1969.42944335938, 1816.35815429688, 18.2149200439453, 40.422779083252, 
41.5035362243652, 41.3402481079102, 136.143905639648, 198.958114624023, 
381.441436767578, 638.81494140625, 712.309814453125, 482.273284912109, 
19.5966491699219, 24.5617866516113, 5.35966491699219, 21.9801445007324, 
38.6888847351074, 194.694213867188, 275.070281982422, 185.235290527344, 
331.374359130859, 369.085205078125, 87.4073486328125, 43.7493515014648, 
9.0551643371582, 17.0039749145508, 19.8424549102783, 42.0317802429199, 
78.9205932617188, 83.8473205566406, 145.503982543945, 126.830123901367, 
73.4324951171875, 24.2352199554443, 14.4002676010132, 11.0644330978394, 
8.97440528869629, 8.60194301605225, 8.19461727142334, 10.0882625579834, 
6.40379619598389, 13.5048570632935, 88.2917251586914, 32.9969177246094, 
13.2497806549072, 18.1800556182861, 9.25154685974121, 20.1857929229736, 
27.4536666870117, 45.3733558654785, 58.0176658630371, 60.3645324707031, 
102.807609558105, 51.4686737060547, 12.5304517745972, 11.1469573974609, 
18.1306304931641, 40.1218070983887, 66.2802352905273, 119.925445556641, 
164.036666870117, 68.928092956543, 23.668140411377, 18.4461612701416, 
12.2497825622559, 16.1434268951416, 10.5176544189453, 50.7678871154785, 
82.2842254638672, 70.8473281860352, 162.089630126953, 150.731719970703, 
66.1902160644531, 25.9435195922852, 10.4514570236206, 14.6368064880371, 
11.9011487960815, 49.3129005432129, 120.026504516602, 156.520797729492, 
259.156280517578, 235.951934814453, 27.7784690856934, 5.55604648590088, 
10.1690225601196, 4.24227809906006, 6.70653247833252, 68.4563293457031, 
109.67741394043, 129.018997192383, 162.575958251953, 324.702667236328
), dim = c(10L, 10L, 40L), dimnames = list(NULL, NULL, c("MPO", 
"HistoneH3", "SMA", "CD16", "CD38", "HLADR", "CD27", "CD15", 
"CD45RA", "CD163", "B2M", "CD20", "CD68", "Ido1", "CD3", "LAG3 / LAG33", 
"CD11c", "PD1", "PDGFRb", "CD7", "GrzB", "PDL1", "TCF7", "CD45RO", 
"FOXP3", "ICOS", "CD8a", "CarbonicAnhydrase", "CD33", "Ki67", 
"VISTA", "CD40", "CD4", "CD14", "Ecad", "CD303", "CD206", "cleavedPARP", 
"DNA1", "DNA2"))))

expect_equal(as.vector(sm),
             c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.089800815578703, 1, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00817725959460128, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 1, 0.00840197838654618, 0.00183423284439564, 0.00250886255698254, 
0.00178118357422369, 0, 0.00418544093176505, 0, 0.00386388524516777, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0.00690371985672871, 1, 0.00236966473153582, 
0.00175827941548428, 0.00119895001011792, 0, 0.00225418851885459, 
0, 0.00213191165634509, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00387729147926425, 
0.0238089076180446, 1, 0.0125676321997274, 0.00286780666719878, 
0, 0.00456531849917259, 0, 0.00509414354823181, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0.00296253907586717, 0.00755359982202801, 1, 0.00253718760464586, 
0, 0.00170215203255029, 0, 0.00152191026458912, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0.000608446823877157, 0.00261535938745646, 0.00355982156191235, 
0.0457684971772144, 1, 0, 0.006567639570538, 0, 0.00349648357257007, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00266172543325263, 1, 0.00085938391511373, 
0.00185479629066368, 0, 0, 0, 0, 0.000944757164967089, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0.00114183228399322, 0.0035443860306795, 0.0286472001303271, 
1, 0.00901742865308882, 0.00210233724477877, 0, 0, 0, 0.00105966731262025, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00702440365785264, 0.00417092486958, 
1, 0.0017462298724691, 0, 0, 0, 0.00124899337376736, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0.000900633533339882, 0.0023830282341776, 0.00595367523099312, 
0.0214650480563327, 1, 0, 0, 0, 0.000790265191762635, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00202467726065181, 1, 0, 0.00679574014271024, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00457226914072469, 0, 0.0059909910323965, 
0, 0.00217687592117622, 1, 0, 0.00684187069791371, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0.0110327239212793, 0.00219081161212213, 
1, 0.000789541649039636, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00325333845482819, 
0, 0.00292858510770294, 0, 0, 0.0102751924699099, 0.00259819838946671, 
1, 0.000181017428430451, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0.00271832081524553, 1, 0.00935603644274335, 0, 0, 0.00126946221709797, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00391156184865328, 1, 0.00458165794645774, 
0, 0.00240416415245864, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0.00773852502803069, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0.000580573313249273, 0.0133979135403376, 1, 0.000297475878854262, 
0.0080468852315735, 8.93874270046589e-05, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00774884656790671, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00888308241903331, 1, 0.00345854566922552, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0.00754787230484107, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.0022618328527385, 
0.0080523992739149, 0.00362981823644658, 1, 0.0028276605561954, 
0.000438365190483715, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0.00703672100922362, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0.010862681419341, 1, 0.0213514263504963, 
0.00369945701363305, 0.00131775648776964, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00713528435152699, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.0343035158915032, 1, 0.0175660888587467, 
0.00256205154843573, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00947514946668493, 
0.0524676741118703, 1, 0.0125509318716494, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00644195340884335, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00477164490697559, 0.0106878436409966, 
0.0202503576346224, 1, 0.000933303485781944, 0.000306277099250257, 
0, 0, 0, 0.000114858247162931, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0.00426350293876318, 1, 0.000385421792177724, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00296074713548995, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00513325623620369, 1, 
0.0108062514624979, 0.00641273937497195, 0, 0.00332922977208095, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.0201942393143331, 1, 0.0123847225179567, 
0, 0.00278961327951157, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.0056488710404519, 
0.0320560884070506, 1, 0.00082661870834845, 0.00549362591142682, 
0.000117845655183374, 7.37038922501214e-05, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0.00567803265278255, 1, 0.000840165980182432, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.000908759110604764, 0.00268703565147154, 
0.00573747878715237, 0.00557857151678915, 1, 0.00227755336289802, 
0.000358712133044413, 0.000400522505827078, 8.39430610998884e-05, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.000749398742096892, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00828200399037447, 1, 
0.00414138281655197, 0.00318813646000227, 0.000330015837181456, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.0607749170733726, 1, 
0.041622859688858, 0.00116604217401947, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0.00492381829984483, 0.0306144247914806, 1, 
0.00428667657380126, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.00423793916595943, 
0.00528055412998493, 0.053812154877771, 1, 0.00887413545217428, 
0.00254737062186887, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0.0244107212270934, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.000890844496472596, 
0.000839298907287718, 0.00482128403229703, 0.00483132293412562, 
0.0077938456309546, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))

expect_equal(rowData(spe)$channel_name, c("Y89Di", "In113Di", "In115Di", "Pr141Di", "Nd142Di", "Nd143Di", 
"Nd144Di", "Nd145Di", "Nd146Di", "Sm147Di", "Nd148Di", "Sm149Di", 
"Nd150Di", "Eu151Di", "Sm152Di", "Eu153Di", "Sm154Di", "Gd155Di", 
"Gd156Di", "Gd158Di", "Tb159Di", "Gd160Di", "Dy161Di", "Dy162Di", 
"Dy163Di", "Dy164Di", "Ho165Di", "Er166Di", "Er167Di", "Er168Di", 
"Tm169Di", "Er170Di", "Yb171Di", "Yb172Di", "Yb173Di", "Yb174Di", 
"Lu175Di", "Yb176Di", "Ir191Di", "Ir193Di"))
```

## Session Info

<details>
   <summary>SessionInfo</summary>
   
```{r, echo = FALSE}
sessionInfo()
```
</details>

