# Image and cell-level quality control

The following section discusses possible quality indicators for data obtained
by IMC and other highly multiplexed imaging technologies.
Due to the complexity of the data, the quality metric range across the image
and single-cell levels and the chapter is sectioned as such.
In general, we commonly do not exclude individual cells from images but rather
whole images to keep the spatial structure of the tissue intact.

## Read in the data

We will first read in the data processed in previous sections:

```{r read-data, message=FALSE}
images <- readRDS("data/images.rds")
masks <- readRDS("data/masks.rds")
spe <- readRDS("data/spe.rds")
```

## Segmentation quality control

The first step after image segmentation is to observe its accuracy.
Without having ground-truth data readily available, a common approach to 
segmentation quality control is to overlay segmentation masks on composite images
displaying channels that were used for segmentation. 
The [cytomapper](https://www.bioconductor.org/packages/release/bioc/html/cytomapper.html) 
Bioconductor package supports exactly this tasks by using the `plotPixels` function.

Here, we select 3 random images and perform image- and channel-wise
normalization (channels are first min-max normalized and scaled to a range of
0-1 before clipping the maximum intensity to 0.2). For more information to image
normalization, refer to Section \@ref(read-data).

```{r overlay-masks, message=FALSE}
library(cytomapper)
set.seed(20220118)
img_ids <- sample(seq_len(length(images)), 3)

# Normalize and clip images
cur_images <- images[img_ids]
cur_images <- normalize(cur_images, separateImages = TRUE)
cur_images <- normalize(cur_images, inputRange = c(0, 0.2))

plotPixels(cur_images,
           mask = masks[img_ids],
           img_id = "sample_id",
           missing_colour = "white",
           colour_by = c("CD163", "CD20", "CD3", "Ecad", "DNA1"),
           colour = list(CD163 = c("black", "yellow"),
                         CD20 = c("black", "red"),
                         CD3 = c("black", "green"),
                         Ecad = c("black", "cyan"),
                         DNA1 = c("black", "blue")),
           image_title = NULL,
           legend = list(colour_by.title.cex = 0.7,
                         colour_by.labels.cex = 0.7))
```

We can see that nuclei are centered within the segmentation masks and all cell
types are correctly segmented, A common challenge here is to segment large (e.g.
epithelial cells - in cyan) _versus_ small (e.g. B cells - in red). However, the
segmentation approach here appears to correctly segment cells across different
sizes.

An additional approach to observe cell segmentation quality and potentially also
antibody specificity issues is to visualize single-cell expression in form of a
heatmap. Here, we sub-sample the dataset to 2000 cells for visualization
purposes and overlay the cancer type from which the cells were extracted.

```{r segmentation-heatmap, message=FALSE, fig.height=7}
library(dittoSeq)
library(viridis)
cur_cells <- sample(seq_len(ncol(spe)), 2000)

dittoHeatmap(spe[,cur_cells], genes = rownames(spe)[rowData(spe)$use_channel],
             assay = "exprs", cluster_cols = TRUE, scale = "none",
             heatmap.colors = viridis(100), annot.by = "indication",
             annotation_colors = list(indication = metadata(spe)$color_vectors$indication))
```

We can differentiate between epithelial cells (Ecad+) and immune cells (CD45RO).
Some of the markers are specifically detected (e.g., Ki67, CD20, Ecad) and markers
that are more broadly detected (e.g. HLADR, B2M, CD4). 

## Image-level quality control

Image-level quality control is often performed using tools that offer a
graphical user interface such as [QuPath](https://qupath.github.io/) and
[FIJI](https://imagej.net/software/fiji/). Viewers that were specifically
developed for IMC data can be seen
[here](https://bodenmillergroup.github.io/IMCWorkflow/viewers.html). In this
section, we will specificaly focus on quantitative metrics to assess image
quality.

It is often of interest to calculate the signal-to-noise ratio (SNR) for
individual channels and markers. Here, we define the SNR as:

$$SNR = I_s/I_n$$

where $I_s$ is the intensity of the signal (mean intensity of pixels with true
signal) and $I_n$ is the intensity of the noise (mean intensity of pixels
containing noise). Finding a threshold that separates pixels containing signal
and pixels containing noise is not trivial and different approaches can be
chosen. Here, we use the `otsu` thresholding approach to find pixels of the
"foreground" (i.e., signal) and "background" (i.e., noise). The SNR is then
defined as the mean intensity of foreground pixels divided by the mean intensity
of background pixels. We then plot the SNR versus mean signal intensity
(together with their 95% confidence interval).

```{r image-snr, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggrepel)
library(EBImage)
cur_snr <- lapply(images, function(img){
    mat <- apply(img, 3, function(ch){
        # Otsu threshold
        thres <- otsu(ch, range = c(min(ch), max(ch)))
        # Signal-to-noise ratio
        snr <- mean(ch[ch > thres]) / mean(ch[ch <= thres])
        # Signal intensity
        ps <- mean(ch[ch > thres])
        
        return(c(snr = snr, ps = ps))
    })
    t(mat) %>% as.data.frame() %>% 
        mutate(marker = colnames(mat)) %>% 
        pivot_longer(cols = c(snr, ps))
})

cur_snr <- do.call(rbind, cur_snr)

cur_snr %>% 
    group_by(marker, name) %>%
    summarize(mean = mean(value),
              ci = qnorm(0.975)*sd(value)/sqrt(n())) %>%
    pivot_wider(names_from = name, values_from = c(mean, ci)) %>%
    ggplot() +
#    geom_errorbar(aes(y = log2(mean_snr), xmin = log2(mean_ps - ci_ps), 
#                      xmax = log2(mean_ps + ci_ps))) +
#    geom_errorbar(aes(x = log2(mean_ps), ymin = log2(mean_snr - ci_snr), 
#                      ymax = log2(mean_snr + ci_snr))) +
    geom_point(aes(log2(mean_ps), log2(mean_snr))) +
    geom_label_repel(aes(log2(mean_ps), log2(mean_snr), label = marker)) +
    theme_minimal(base_size = 15) + ylab("Signal-to-noise ratio") +
    xlab("Signal intensity")
```

We observe PD1, LAG3 and cleaved PARP to have high SNR but low signal intensity
meaning that in general these markers are not abundantly expressed. The Iridium
intercalator (here marked as DNA1 and DNA2) has the highest signal intensity 
but low SNR. This might be due to staining differences between individual nuclei
where some nuclei are considered as background. We do however observe high
SNR and sufficient signal intensity for the majority of markers.

Another quality indicator is the image area covered by cells (or biological tissue).
This metric identifies ROIs where little cells are present, possibly hinting
at incorrect selection of the ROI. We can compute the percentage of image 
are covered by cells using the metadata contained in the `SpatialExperiment`
object:

```{r cell-density}
colData(spe) %>%
    as.data.frame() %>%
    group_by(sample_id) %>%
    summarize(cell_area = sum(area),
           no_pixels = mean(width_px) * mean(height_px)) %>%
    mutate(covered_area = cell_area / no_pixels) %>%
    ggplot() +
        geom_point(aes(sample_id, covered_area)) + 
        theme_minimal(base_size = 15) +
        ylim(c(0, 1)) + 
        theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8)) +
        ylab("% covered area") + xlab("")
```

We observe that two of the 14 images show unusually low cell coverage. These
two images can now be visualized using `cytomapper`.

```{r low-density-images, message=FALSE}
# Normalize and clip images
cur_images <- images[c("Patient4_005", "Patient4_007")]
cur_images <- normalize(cur_images, separateImages = TRUE)
cur_images <- normalize(cur_images, inputRange = c(0, 0.2))

plotPixels(cur_images,
           mask = masks[c("Patient4_005", "Patient4_007")],
           img_id = "sample_id",
           missing_colour = "white",
           colour_by = c("CD163", "CD20", "CD3", "Ecad", "DNA1"),
           colour = list(CD163 = c("black", "yellow"),
                         CD20 = c("black", "red"),
                         CD3 = c("black", "green"),
                         Ecad = c("black", "cyan"),
                         DNA1 = c("black", "blue")),
           legend = list(colour_by.title.cex = 0.7,
                         colour_by.labels.cex = 0.7))
```

These two images display less dense tissue structure and `Patient4_007` shows
signs of under-segmentation potentially due to irregular nuclear shape or 
missing markers to detect certain cell types (e.g., fibroblasts).

Finally, it can be beneficial to visualize the mean marker expression per image
to identify images with outlying cell type compositions. This check does not
indicate image quality _per se_ but can highlight biological differences. Here,
we will use the `aggregateAcrossCells` function of the 
`rBiocStyle::Biocpkg("scuttle")` package to compute the mean expression per 
image. For visualization purposes, we again `asinh` transform the mean expression
values.

```{r mean-expression-per-image, message=FALSE, fig.height=7}
library(scuttle)

image_mean <- aggregateAcrossCells(spe, 
                                   ids = spe$sample_id, 
                                   statistics="mean",
                                   use.assay.type = "counts")
assay(image_mean, "exprs") <- asinh(counts(image_mean))

dittoHeatmap(image_mean, genes = rownames(spe)[rowData(spe)$use_channel],
             assay = "exprs", cluster_cols = TRUE, scale = "none",
             heatmap.colors = viridis(100), 
             annot.by = c("indication", "patient_id", "ROI"),
             annotation_colors = list(indication = metadata(spe)$color_vectors$indication,
                                      patient_id = metadata(spe)$color_vectors$patient_id,
                                      ROI = metadata(spe)$color_vectors$ROI))
```

We observe extensive biological variation across the 14 images. Some images
contain a high fraction of macrophages (CD206), B cells (CD20), neutrophils
(CD15) or proliferating cells (Ki67). These differences will be further studied
in the following chapters.

## Cell-level quality control

In the following paragraphs we will look at different metrics and visualization
approaches to assess data quality (as well as biological differences) on the 
single-cell level. 

Similar to the signal-to-noise ratio (SNR) calculated above on the pixel-level, 
a similar measure can be derived on the single-cell level. Here, we will use 
a two component Gaussian mixture model for each marker to find cells
with positive and negative expression. As above the SNR is defined as:

$$SNR = I_s/I_n$$

where $I_s$ is the intensity of the signal (mean intensity of cells with positive
signal) and $I_n$ is the intensity of the noise (mean intensity of cells
lacking expression).

```{r cell-snr, message=FALSE, warning=FALSE}
library(mclust)

set.seed(220224)
cur_snr <- lapply(unique(spe$patient_id), function(patient){
    
    cur_spe <- spe[,spe$patient_id == patient]
    mat <- apply(assay(cur_spe, "exprs"), 1, function(x){
        cur_model <- Mclust(x, G = 2)
        mean1 <- mean(x[cur_model$classification == 1])
        mean2 <- mean(x[cur_model$classification == 2])
        
        signal <- ifelse(mean1 > mean2, mean1, mean2)
        noise <- ifelse(mean1 > mean2, mean2, mean1)
        
        return(c(signal/noise, signal))
    })
    rownames(mat) <- c("snr", "ps")
    
    t(mat) %>% as.data.frame() %>% 
        mutate(marker = colnames(mat)) %>% 
        pivot_longer(cols = c(snr, ps))
})

cur_snr <- do.call(rbind, cur_snr)

cur_snr %>% 
    group_by(marker, name) %>%
    summarize(mean = mean(value),
              ci = qnorm(0.975)*sd(value)/sqrt(n())) %>%
    pivot_wider(names_from = name, values_from = c(mean, ci)) %>%
    ggplot() +
#    geom_errorbar(aes(y = log2(mean_snr), xmin = log2(mean_ps - ci_ps), 
#                      xmax = log2(mean_ps + ci_ps))) +
#    geom_errorbar(aes(x = log2(mean_ps), ymin = log2(mean_snr - ci_snr), 
#                      ymax = log2(mean_snr + ci_snr))) +
    geom_point(aes(log2(mean_ps), log2(mean_snr))) +
    geom_label_repel(aes(log2(mean_ps), log2(mean_snr), label = marker)) +
    theme_minimal(base_size = 15) + ylab("Signal-to-noise ratio") +
    xlab("Signal intensity")
```

Next, we will observe the distributions of cell sizes across the individual images.
Differences in cell sizes can indicate segmentation biases due to differences
in cell density or can indicate biological differences due to cell type compositions (tumor cells tend to be larger than immune cells).
We will also observe the minimum cell sizes to exclude very small cells.

```{r cell-size, message=FALSE}
colData(spe) %>%
    as.data.frame() %>%
    group_by(sample_id) %>%
    ggplot() +
        geom_boxplot(aes(sample_id, area)) +
        theme_minimal(base_size = 15) + 
        theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8)) +
        ylab("Cell area") + xlab("")

summary(spe$area)
```

The median cell size is `r median(spe$area)` pixels with a median major axis
length of `r median(spe$major_axis_length)`. The largest cell has an area of 
`r max(spe$area)` pixels which relates to a diameter of `r sqrt(max(spe$area))`
pixels assuming a circular shape. Overall, the distribution of cell sizes is
similar across images with image `Patient4_005` and `Patient4_007` showing
reduces average cell size. These images contain fewer tumor cells which can 
explain smaller average cell size.

We observe very small cells an will remove them from the dataset. The chosen
threshold is arbitrary and needs to be adjusted per dataset.

```{r remove-small-cells}
sum(spe$area < 5)
spe <- spe[,spe$area >= 5]
```

Another quality indicator can be the number of cells per image divided by the
image size. This measure relates to the percentage of image area covered by
cells as explained above.

```{r no-cells-per-image, message=FALSE}
colData(spe) %>%
    as.data.frame() %>%
    group_by(sample_id) %>%
    summarize(cell_count = n(),
           no_pixels = mean(width_px) * mean(height_px)) %>%
    mutate(cells_per_mm2 = cell_count/(no_pixels/1000000)) %>%
    ggplot() +
        geom_point(aes(sample_id, cells_per_mm2)) + 
        theme_minimal(base_size = 15)  + 
        theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8)) +
        ylab("Cells per mm2") + xlab("")
```

The number of cells per mm$^2$ varies across images which also depends on the
number of tumor/non-tumor cells. As we can see in the following sections, some
immune cells appear in cell dense regions while other stromal parts are less
dense.

The data presented here were stained on individual slides. Also, samples were
processed in different locations. These (and other) technical aspects can
induces staining differences between samples or batches of samples. Observing
potential staining differences can be crucial to assess data quality.
We will use ridgeline visualizations to check differences in staining patterns:

```{r ridges, message=FALSE, fig.width=7, fig.height=25}
multi_dittoPlot(spe, vars = rownames(spe)[rowData(spe)$use_channel],
               group.by = "patient_id", plots = c("ridgeplot"), 
               assay = "exprs", 
               color.panel = metadata(spe)$color_vectors$patient_id)
```

We observe variations in the distributions of marker expression across patients.
These variations arise partly from differences in region selection for
measurement (it appears that Patient3 contains a higher number of CD11c+ and
HLADR+ cells) as well as staining differences between samples. While most of the
selected markers are specifically expressed in immune cell subtypes, we can see
that E-Cadherin (a marker for tumor cells) shows similar expression across all
patients.

Finally, we will use non-linear dimensionality reduction methods to project
cells from high-dimensional (40) down to a low-dimensional (2) space. For this
the `r BiocStyle::Biocpkg("scater")` package provides the `runUMAP` and `runTSNE`
function (among others). To ensure reproducibility, we will need to set a seed; 
however different seeds and different parameter settings (e.g. the `perplexity`)
parameter in the `runTSNE` function need to be tested to avoid interpreting
visualization artefacts. For dimensionality reduction, we will use all channels
that show biological variation across the dataset. However, marker selection 
can be performed with different biological questions in mind.

```{r dimred, message=FALSE}
library(scater)

set.seed(220225)
spe <- runUMAP(spe, subset_row = rowData(spe)$use_channel, exprs_values = "exprs") 
spe <- runTSNE(spe, subset_row = rowData(spe)$use_channel, exprs_values = "exprs") 
```

After dimensionality reduction, the low-dimensional embeddings are stored in the 
`reducedDim` slot.

```{r show-dimred-slot}
reducedDims(spe)
head(reducedDim(spe, "UMAP"))
```

Visualization of the low-dimensional embedding facilitates assessment of 
potential "batch effects". The `dittoSeq::dittoDimPlot` and `scater::plotReducedDim`
functions allow flexible visualization. They return `ggplot` objects which
can be further modified. The `plotReducedDim` is the prefered way of visualizing
marker expression on the cells due to increased control of the color scheme.

```{r visualizing-dimred, message=FALSE}
# visualize patient id 
p1 <- dittoDimPlot(spe, var = "patient_id", reduction.use = "UMAP") + 
    scale_color_manual(values = metadata(spe)$color_vectors$patient_id) +
    ggtitle("Patient ID on UMAP")
p2 <- dittoDimPlot(spe, var = "patient_id", reduction.use = "TSNE") + 
    scale_color_manual(values = metadata(spe)$color_vectors$patient_id) +
    ggtitle("Patient ID on TSNE")

# visualize region of interest id
p3 <- dittoDimPlot(spe, var = "ROI", reduction.use = "UMAP") + 
    scale_color_manual(values = metadata(spe)$color_vectors$ROI) +
    ggtitle("ROI ID on UMAP")
p4 <- dittoDimPlot(spe, var = "ROI", reduction.use = "TSNE") + 
    scale_color_manual(values = metadata(spe)$color_vectors$ROI) +
    ggtitle("ROI ID on TSNE")

(p1 + p2) / (p3 + p4)

# visualize marker expression
p1 <- dittoDimPlot(spe, var = "Ecad", reduction.use = "UMAP", assay = "exprs") +
    scale_color_viridis(name = "Ecad") +
    ggtitle("E-Cadherin expression on UMAP")
p2 <- dittoDimPlot(spe, var = "CD45RO", reduction.use = "UMAP", assay = "exprs") +
    scale_color_viridis(name = "CD45RO") +
    ggtitle("CD45RO expression on UMAP")
p3 <- dittoDimPlot(spe, var = "Ecad", reduction.use = "TSNE", assay = "exprs") +
    scale_color_viridis(name = "Ecad") +
    ggtitle("Ecad expression on TSNE")
p4 <- dittoDimPlot(spe, var = "CD45RO", reduction.use = "TSNE", assay = "exprs") +
    scale_color_viridis(name = "CD45RO") +
    ggtitle("CD45RO expression on TSNE")

(p1 + p2) / (p3 + p4)
```

## Save objects

The modified `SpatialExperiment` object is saved for further downstream analysis.

```{r save-objects-quality-control}
saveRDS(spe, "data/spe.rds")
```

## Session Info

<details>
   <summary>SessionInfo</summary>
   
```{r, echo = FALSE}
sessionInfo()
```
</details>