# Cell phenotyping 

A common step during single-cell data analysis is the labeling of cells based
on their phenotype. Defining cell phenotypes is often subjective and relies
on previous biological knowledge. The [Orchestrating Single Cell Analysis with Bioconductor](https://bioconductor.org/books/3.14/OSCA.basic/cell-type-annotation.html) book
presents a number of approaches to phenotype cells detected by single-cell RNA
sequencing based on reference datasets of prior knowledge of gene sets.

In highly-multiplexed imaging, target proteins are manually selected based on
the biological question at hand. It narrows down the feature space and
facilitates the manual annotation of clusters to derive cell phenotypes. We
will therefore discuss and compare a number of clustering approaches to group cells
based on their similarity in marker expression in Section \@ref(clustering). 

Unlike single-cell RNA sequencing and CyTOF data, single-cell data derived from
highly-multiplexed imaging data often suffers from "lateral spillover" between
neighboring cells. This spillover caused by imperfect segmentation often hinders
accurate clustering to define specific cell phenotypes in multiplexed imaging
data. Tools have been developed to correct lateral spillover between cells
[@Bai2021] but the approach requires careful selection of which markers to
correct. In Section \@ref(classification) we will train and apply a random
forest classifier to classify cell phenotypes in the datasete. This approach has
been previously used to identify major cell phenotypes in metastatic melanoma
and avoids clustering of cells [@Hoch2021].

## Load data

Read in the previously generated `SpatialExperiment` object.

```{r read-data-pheno, message=FALSE}
spe <- readRDS("data/spe.rds")
```

## Clustering approaches {#clustering}

### Rphenograph

```{r rphenograph-1, message=FALSE}
library(igraph)
library(dittoSeq)
mat <- t(assay(spe, "exprs")[rowData(spe)$use_channel,])

out <- Rphenograph(mat, k = 30)

clusters <- factor(membership(out[[2]]))

spe$rp_clusters <- clusters

dittoDimPlot(spe, var = "rp_clusters", reduction.use = "UMAP", size = 0.2) +
    ggtitle("Phenograph clusters expression on UMAP")
```

### Shared nearest neighbour graph

### FlowSOM

## Classification approaches {#classification}

### Manual labelling of cells

### Training a classifier

### Classifier performance

### Classification of new data

## Session Info

<details>
   <summary>SessionInfo</summary>
   
```{r, echo = FALSE}
sessionInfo()
```
</details>
