---
editor_options: 
  markdown: 
    wrap: 72
---

# Single cell visualization {#single-cell-visualization}

The following section describes typical approaches on how to visualize
single-cell data.

This chapter is divided into three parts. Section \@ref(cell-type-level)
will highlight visualization approaches downstream of our cell type
classification from Section \@ref(classification). We will then focus on
visualization methods that relate single-cell data to the sample level
in Section \@ref(sample-level). Lastly, Section \@ref(rich-example) will
provide a more customized example on how to integrate various
single-cell and sample metadata into one heatmap using the
[ComplexHeatmap](https://bioconductor.org/packages/release/bioc/html/ComplexHeatmap.html)
package.

Visualization functions from popular R packages in single-cell research
such as
[scater](https://bioconductor.org/packages/release/bioc/html/scater.html),
[DittoSeq](https://bioconductor.org/packages/release/bioc/html/dittoSeq.html)
and
[CATALYST](https://bioconductor.org/packages/release/bioc/html/CATALYST.html)
will be utilized. We will recycle methods and functions that we have
seen in previous sections, while also introducing new ones.

Please note that this chapter aims to provide an overview on **common**
visualization options and should be seen as a stepping-stone. However,
many more options exist and the user should customize the visualization
according to the biological question at hand.

## Load data

First, we will read in the previously generated `SpatialExperiment`
object.

```{r read-data-batch-correction, message=FALSE}
spe <- readRDS("data/spe.rds")
```

For visualization purposes, we will define markers that were used for
cell type classification and markers that can indicate a specific cell
state (e.g. Ki67).

```{r}
# Define cell_type_markers 
type_markers <- c("Ecad", "CD45RO", "CD20", "CD3", "FOXP3", "CD206", "MPO", "SMA","CD8a","CD4","HLADR","CD15","CD38","PDGFRb")

# Define cell_state_markers 
state_markers <- c("CarbonicAnhydrase","Ki67","PD1","GrzB","PDL1","ICOS","TCF7","VISTA")

# Add to spe
rowData(spe)$type_markers <- rownames(spe) %in% type_markers
rowData(spe)$state_markers <- rownames(spe) %in% state_markers
```

## Cell-type level {#cell-type-level}

In the first section of this chapter, the grouping-level for the
visualization approaches will be the cell type classification from
Section \@ref(classification). Other grouping levels (e.g. cluster
assignments from Section \@ref(clustering)) are possible and the user
should adjust depending on the chosen analysis workflow.

### Dimensionality reduction visualization

As seen before, we can visualize single-cells in low-dimensional space.
Often used non-linear methods for dimensionality reduction are tSNE and
UMAP, which aim to preserve the distances between each cell and its
neighbors in the high-dimensional space.

Interpreting these plots is not trivial, but local neighborhoods in the
plot can suggest similarity in expression for given cells. See
[Orchestrating Single-Cell Analysis with
Bioconductor](https://bioconductor.org/books/release/OSCA/) for more
details.

Here, we will use `dittoDimPlot` from
[DittoSeq](https://bioconductor.org/packages/release/bioc/html/dittoSeq.html)
and `plotReducedDim` from
[scater](https://bioconductor.org/packages/release/bioc/html/scater.html)
to visualize the fastMNN-corrected UMAP colored by cell type and
expression, respectively.

Both functions are highly flexible and return `ggplot` objects which can
be further modified.

```{r umap}
library(patchwork)
library(cowplot)
library(scater)
library(ggplot2)
library(viridis)
library(dittoSeq)

## UMAP colored by cell type and expression - dittoDimPlot
p1 <- dittoDimPlot(spe, var = "celltype", 
             reduction.use = "UMAP_mnnCorrected", size = 0.2,
             do.label = TRUE) +
  scale_color_manual(values = metadata(spe)$color_vectors$celltype)+
  theme(legend.title = element_blank()) +
  ggtitle("Classification cell labels on UMAP, integrated cells")


p2 <- dittoDimPlot(spe, var = "Ecad", assay = "exprs",
             reduction.use = "UMAP_mnnCorrected", size = 0.2, colors = viridis(100),
             do.label = TRUE)+
    scale_color_viridis()
  
p1+p2

# UMAP colored by expression for all markers - plotReducedDim
plot_list  <- lapply(rownames(spe)[rowData(spe)$type_markers == TRUE], function(x){
                      p <- plotReducedDim(spe, dimred = "UMAP_mnnCorrected",
                                          colour_by = x,
                                          by_exprs_values = "exprs",
                                          point_size = 0.5)
                      return(p)
                    })

plot_grid(plotlist = plot_list)
```

### Heatmap visualization

Next, it is often useful to visualize single-cell expression per cell
type in form of a heatmap. For this, we will use the `dittoHeatmap`
function from
[DittoSeq](https://bioconductor.org/packages/release/bioc/html/dittoSeq.html).

Furthermore, we sub-sample the dataset to 4000 cells for ease of
visualization and overlay the cancer type and patient ID from which the
cells were extracted.

```{r celltype heatmap, message=FALSE}
library(dittoSeq)
library(viridis)
cur_cells <- sample(seq_len(ncol(spe)), 4000)

#Heatmap visualization - DittoHeatmap
dittoHeatmap(spe[,cur_cells], genes = rownames(spe)[rowData(spe)$type_markers == TRUE],
             assay = "exprs", order.by = c("celltype"),
             cluster_cols = FALSE, scale = "none",
             heatmap.colors = viridis(100), annot.by = c("celltype","indication","patient_id"),
             annotation_colors = list(indication = metadata(spe)$color_vectors$indication,
                                      patient_id = metadata(spe)$color_vectors$patient_id,
                                      celltype = metadata(spe)$color_vectors$celltype)
             )
```

Similarly, we can visualize the mean marker expression per cell type for
all cells using `aggregateAcrossCells` from
[scuttle](https://bioconductor.org/packages/release/bioc/html/scuttle.html)
and then `dittoHeatmap`. We will annotate the heatmap with the number of
cells per cell type.

```{r celltype mean-expression-per-cluster, message=FALSE, fig.height=7}
library(scuttle)
## by cell type
celltype_mean <- aggregateAcrossCells(as(spe, "SingleCellExperiment"),  
                     ids = spe$celltype, 
                     statistics = "mean",
                     use.assay.type = "exprs", 
                     subset.row = rownames(spe)[rowData(spe)$type_markers == TRUE]
                     )

#No scaling
dittoHeatmap(celltype_mean,
             assay = "exprs", cluster_cols = TRUE, 
             scale = "none",
             heatmap.colors = viridis(100),
             annot.by = c("celltype","ncells"),
             annotation_colors = list(celltype = metadata(spe)$color_vectors$celltype,
                                      ncells = plasma(100)))

#Min-max expression scaling
dittoHeatmap(celltype_mean,
             assay = "exprs", cluster_cols = TRUE, 
             scaled.to.max = TRUE,
             heatmap.colors.max.scaled = viridis(100),
             annot.by = c("celltype","ncells"),
             annotation_colors = list(celltype = metadata(spe)$color_vectors$celltype,
                                      ncells = plasma(100)))
```

As illustrated above for not- and min-max-scaled expression values,
different ways of scaling can have strong effects on visualization
output and we encourage the user to test multiple options.

Overall, we can observe cell-type specific marker expression (e.g. Tumor
= Ecad high and B cells = CD20 high) in agreement with the gating scheme
of Section \@ref(classification).

### Violin plot visualization

The `plotExpression` function from
[scater](https://bioconductor.org/packages/release/bioc/html/scater.html)
allows to plot the distribution of expression values across cell types
for a chosen set of proteins. The output is a flexible `ggplot` object.

```{r celltype violin, message=FALSE}
#Violin Plot - plotExpression
plotExpression(spe[,cur_cells],features = rownames(spe)[rowData(spe)$type_markers == TRUE], x = "celltype", exprs_values = "exprs", colour_by = "celltype")+
    scale_color_manual(values = metadata(spe)$color_vectors$celltype)
```

### Scatter plot visualization

Moreover, a protein expression based scatter plot can be generated with
`dittoScatterPlot` (returns a `ggplot` object). We overlay the plot with the 
cell type information.

```{r celltype scatter, message=FALSE}
#Scatter plot
dittoScatterPlot(spe, x.var = "CD3", y.var="CD20", assay.x = "exprs", assay.y = "exprs", color.var = "celltype")+
    scale_color_manual(values = metadata(spe)$color_vectors$celltype)+
    ggtitle("Scatterplot for CD3/CD20 labelled by celltype")
```

We can nicely observe how the "B next to T cell" phenotype (`BnTcell`)
has high expression values for both CD20 and CD3.

**Of note**, in a setting where the user aims to assign labels to
clusters based on marker genes/proteins, all of the above plots can be
particularly helpful.

### Barplot visualization

In order to display frequencies of cell types per sample/patient, the 
`dittoBarPlot` function will be used. Data can be represented as percentages or 
counts and again `ggplot` objects are outputted. 

```{r barplot celltype}
#by sample_id
dittoBarPlot(spe, var = "celltype", group.by = "sample_id")+
    scale_fill_manual(values = metadata(spe)$color_vectors$celltype)

#by patient_id - percentage
dittoBarPlot(spe, var = "celltype", group.by = "patient_id")+
    scale_fill_manual(values = metadata(spe)$color_vectors$celltype)

#by patient_id - count
dittoBarPlot(spe, scale = "count", var = "celltype", group.by = "patient_id")+
    scale_fill_manual(values = metadata(spe)$color_vectors$celltype)
```
We can see that cell type frequencies change between samples/patients and 
that the highest proportion of *plasma cells* can be observed for Patient 2. 

### CATALYST-based visualization

In the following, we would like to highlight some useful visualization functions 
from the [CATALYST](https://bioconductor.org/packages/release/bioc/html/CATALYST.html) package. 

To this end, we will first convert the `SpatialExperiment` object into a 
CATALYST-compatible format. 

```{r}
library(CATALYST)

#save spe in CATALYST-compatible object with renamed colData entries and new metadata information
spe_cat <- spe 

spe_cat$sample_id <- factor(spe$sample_id)
spe_cat$condition <- factor(spe$indication)
spe_cat$cluster_id <- factor(spe$celltype)

#add celltype information to metadata
metadata(spe_cat)$cluster_codes <- data.frame(celltype = factor(spe_cat$celltype))
```

All of the `CATALYST` functions presented below return `ggplot` objects, which 
allow flexible downstream adjustment. 

#### Pseudobulk-level MDS plot

Pseudobulk-level multi-dimensional scaling (MDS) plots can be rendered with the 
exported `pbMDS` function.

Here, we will use `pbMDS` to highlight expression similarities between cell types 
and subsequently for each celltype-sample-combination. 

```{r celltype pbmds}
## pbMDS plot

# MDS pseudobulk by cell type
pbMDS(spe_cat, by = "cluster_id", features = rownames(spe_cat)[rowData(spe_cat)$type_markers == TRUE], label_by = "cluster_id", k="celltype")+
  scale_color_manual(values = metadata(spe_cat)$color_vectors$celltype)

# MDS pseudobulk by cell type and sample_id
pbMDS(spe_cat, by = "both", features = rownames(spe_cat)[rowData(spe_cat)$type_markers == TRUE], k = "celltype", shape_by = "condition", size_by = TRUE)+
  scale_color_manual(values = metadata(spe_cat)$color_vectors$celltype)
```

We can see that the pseudobulk-expression profile of *neutrophils* seems markedly 
distinct from the other cell types, while comparable cell types such as the T 
cell subtypes group together. Furthermore, pseudobulk cell-type profiles from 
SCCHN appear different from the other indications. 


#### Reduced dimension plot on CLR of proportions

The `clrDR` function produces dimensionality reduction plots on centered 
log-ratios (CLR) of sample/cell type proportions across cell type/samples. 

As with `pbMDS`, the output plots aim to illustrate the degree of similarity 
between cell types based on sample proportions. 

```{r celltype - clrDR}
## clrDR plot

#CLR on cluster proportions across samples
set.seed(22)

clrDR(spe_cat, dr = "PCA", by = "cluster_id", k = "celltype", label_by = "cluster_id", arrow_col = "patient_id", point_pal = metadata(spe_cat)$color_vectors$celltype)+
  scale_color_manual(values = metadata(spe_cat)$color_vectors$patient_id)
```
We can again observe that *neutrophils* have a divergent profile also in terms 
of their sample proportions. 

#### Pseudobulk expression boxplot

The `plotPbExprs` generates combined box- and jitter-plots of aggregated marker 
expression per cell type. Here, we further split the data by cancer type.

```{r celltype pbExprs}
plotPbExprs(spe_cat, k = "celltype", facet_by = "cluster_id", ncol = 4, features = rownames(spe_cat)[rowData(spe_cat)$type_markers == TRUE])+
    scale_color_manual(values = metadata(spe_cat)$color_vectors$indication)
```
Notably, CD15 levels are elevated in SCCHN in comparison to all other indications 
for most cell types. 

## Sample-level {#sample-level}

In the next section, we will shift the grouping-level focus from the cell type 
to the sample-level. Sample-levels will be further divided into the 
sample-(reflecting each image) and patient-level. 

Although we will mostly repeat the functions from the previous section \@ref(cell-type-level),
we believe that image- and patient-level centered visualization can provide 
additional quality control and biological interpretation. 

### Dimensionality reduction visualization

Visualization of low-dimensional embeddings, here not corrected and fastMNN-corrected UMAPs, 
and coloring it by sample-levels is often used for "batch effect" assessment 
as mentioned in Section \@ref(cell-quality). 

We will again use `dittoDimPlot`. 

```{r umap}
library(patchwork)
library(cowplot)
library(scater)
library(ggplot2)
library(viridis)
library(dittoSeq)

## UMAP colored by cell type and expression - dittoDimPlot
p1 <- dittoDimPlot(spe, var = "sample_id",
             reduction.use = "UMAP", size = 0.2, colors = viridis(100),
             do.label = TRUE)+
    scale_color_manual(values = metadata(spe)$color_vectors$sample_id)+
  theme(legend.title = element_blank()) +
  ggtitle("Sample ID")

p2 <- dittoDimPlot(spe, var = "sample_id",
             reduction.use = "UMAP_mnnCorrected", size = 0.2, colors = viridis(100),
             do.label = TRUE)+
    scale_color_manual(values = metadata(spe)$color_vectors$sample_id)+
  theme(legend.title = element_blank()) +
  ggtitle("Sample ID")

p3 <- dittoDimPlot(spe, var = "patient_id", 
             reduction.use = "UMAP", size = 0.2,
             do.label = TRUE) +
  scale_color_manual(values = metadata(spe)$color_vectors$patient_id)+
  theme(legend.title = element_blank()) +
  ggtitle("Patient ID")

p4 <- dittoDimPlot(spe, var = "patient_id", 
             reduction.use = "UMAP_mnnCorrected", size = 0.2,
             do.label = TRUE) +
  scale_color_manual(values = metadata(spe)$color_vectors$patient_id)+
  theme(legend.title = element_blank()) +
  ggtitle("Patient ID")

(p1 + p2) / (p3 + p4)
```

As illustrated in Section \@ref(batch-effects), we see that the fastMNN approach
(right side of the plot) leads to mixing of cells across samples/patients and 
thus batch effect correction.

### Heatmap visualization

It can be beneficial to use a heatmap to visualize single-cell expression per 
sample and patient. Such a plot, which we will create using `dittoHeatmap`, 
can highlight biological differences across samples/patients. 

```{r patient heatmap}
#Heatmap visualization - DittoHeatmap
dittoHeatmap(spe[,cur_cells], genes = rownames(spe)[rowData(spe)$type_markers == TRUE],
             assay = "exprs", order.by = c("patient_id","sample_id"),
             cluster_cols = FALSE, scale = "none",
             heatmap.colors = viridis(100), annot.by = c("celltype","indication","patient_id","sample_id"),
             annotation_colors = list(celltype = metadata(spe)$color_vectors$celltype,
                                      indication = metadata(spe)$color_vectors$indication,
                                      patient_id = metadata(spe)$color_vectors$patient_id,
                                      sample_id = metadata(spe)$color_vectors$sample_id
                                      )
             )

```

As in Section \@ref(image-quality), aggregated mean marker expression per sample/patient 
allow identification of samples/patients with outlying expression patterns. 

Here, we will focus on the patient level and use `aggregateAcrossCells` and 
`dittoHeatmap`. The heatmap will be annotated with the number of cells per 
patient and displayed using two scaling options.

```{r celltype mean-expression-per-cluster, message=FALSE, fig.height=7}
library(scuttle)
#by patient_id
patient_mean <- aggregateAcrossCells(as(spe, "SingleCellExperiment"),  
                     ids = spe$patient_id, 
                     statistics = "mean",
                     use.assay.type = "exprs", 
                     subset.row = rownames(spe)[rowData(spe)$type_markers == TRUE]
                     )

#No scaling
dittoHeatmap(patient_mean,
             assay = "exprs", cluster_cols = TRUE, 
             scale = "none",
             heatmap.colors = viridis(100),
             annot.by = c("patient_id","ncells"),
             annotation_colors = list(patient_id = metadata(spe)$color_vectors$patient_id,
                                      ncells = plasma(100)))

#Min-max expression scaling
dittoHeatmap(patient_mean,
             assay = "exprs", cluster_cols = TRUE, 
             scaled.to.max =  TRUE,
             heatmap.colors.max.scaled = viridis(100),
             annot.by = c("patient_id","ncells"),
             annotation_colors = list(patient_id = metadata(spe)$color_vectors$patient_id,
                                      ncells = plasma(100)))

```

### Barplot visualization

Complementary to displaying cell type frequencies per sample/patient, 
we can use `dittoBarPlot` to display sample/patient frequencies per cell type.

```{r barplot patient}
dittoBarPlot(spe, var = "patient_id", group.by = "celltype")+
    scale_fill_manual(values = metadata(spe)$color_vectors$patient_id)

dittoBarPlot(spe, var = "sample_id", group.by = "celltype")+
    scale_fill_manual(values = metadata(spe)$color_vectors$sample_id)
```
`Patient2` has the highest and lowest proportion of *plasma cells* and *neutrophils*, respectively. 

### CATALYST-based visualization

#### Pseudobulk-level MDS plot

Expression-based pseudobulks for each sample can be compared with the 
`pbMDS` function. 

```{r patient-pbmds}
## pbMDS plot

# MDS pseudobulk by sample_id 
pbMDS(spe_cat, by = "sample_id", color_by = "sample_id", features = rownames(spe_cat)[rowData(spe_cat)$type_markers == TRUE])+
  scale_color_manual(values = metadata(spe_cat)$color_vectors$sample_id)
```

There are marked differences in pseudobulk-expression patterns between samples 
and across patients, which can be driven by biological differences and also 
technical aspects such as divergent region selection.

#### Reduced dimension plot on CLR of proportions

The `clrDR` function can also be used to analyze similarity of samples based on 
cell type proportions. 

```{r patient-clrDR}
## clrDR plot

#CLR on sample proportions across clusters
set.seed(22)
clrDR(spe_cat, dr = "PCA", by = "sample_id", point_col = "sample_id",k = "celltype", point_pal = metadata(spe_cat)$color_vectors$sample_id)+
  scale_color_manual(values = metadata(spe_cat)$color_vectors$celltype)
```

There are notable differences between samples based on their cell type 
proportions. 

Interestingly, `Patient3_001`, `Patient1_003`, `Patient4_007` and 
`Patient4_006` group together and the PC loadings indicate a strong contribution 
of *BnT* and *B* cells, which could propose formation of tertiary lymphoid 
structures (TLS). In section \@ref(spatial-viz), we will be able to confirm 
this finding also on the images. 


## Further examples {#rich-example}

### Publication-ready ComplexHeatmap

Rich heatmap based on ComplexHeatmap that combines celltype and sample
information.

```{r}
library(ComplexHeatmap)
library(circlize)
library(tidyverse)

set.seed(22)

### 1. Heatmap bodies ###

# By celltype markers
celltype_mean <- aggregateAcrossCells(as(spe, "SingleCellExperiment"),  
                     ids = spe$celltype, 
                     statistics = "mean",
                     use.assay.type = "exprs", 
                     subset.row = rownames(spe)[rowData(spe)$type_markers == TRUE]
                     )

# By cellstate markers
cellstate_mean <- aggregateAcrossCells(as(spe, "SingleCellExperiment"),  
                     ids = spe$celltype, 
                     statistics = "mean",
                     use.assay.type = "exprs", 
                     subset.row = rownames(spe)[rowData(spe)$state_markers == TRUE]
                     )

# Heatmap body color 
col_exprs <- colorRamp2(c(0,1,2,3,4), c("#440154FF","#3B518BFF","#20938CFF","#6ACD5AFF","#FDE725FF"))


### 2. Heatmap annotation ###

### 2.1  Metadata features

anno <- colData(celltype_mean) %>% as.data.frame %>% select(celltype, ncells)

# Proportion of indication per celltype
indication <- colData(spe) %>% as.data.frame() %>% select(celltype,indication) %>% group_by(celltype) %>% table() %>% as.data.frame
indication <- indication %>% group_by(celltype) %>% mutate(fra = Freq/sum(Freq)) 
indication <- indication %>% select(-Freq) %>% pivot_wider(id_cols = celltype,names_from = indication,values_from = fra) %>% column_to_rownames("celltype")

# Number of contributing samples per celltype
cluster_PID <- colData(spe) %>% as.data.frame() %>% select(celltype,patient_id) %>% group_by(celltype) %>% table() %>% as.data.frame
n_PID <- cluster_PID %>% filter(Freq>0) %>% group_by(celltype) %>% count(name = "n_PID") %>% column_to_rownames("celltype")

# Create two HeatmapAnnotation objects
ha_anno <- HeatmapAnnotation(celltype = anno$celltype,
                            border = TRUE, 
                            gap = unit(1,"mm"),
                            col = list(celltype = metadata(spe)$color_vectors$celltype),
                            which = "row")
    
ha_meta <- HeatmapAnnotation(n_cells = anno_barplot(anno$ncells, width = unit(10, "mm")),
                            n_PID = anno_barplot(n_PID, width = unit(10, "mm")),
                            indication = anno_barplot(indication,width = unit(10, "mm"),gp = gpar(fill = metadata(spe)$color_vectors$indication)),
                            border = TRUE, 
                            annotation_name_rot = 90,
                            gap = unit(1,"mm"),
                            which = "row")

### 2.2 Spatial features

# Add number of neighbors to spe object (saved in ColPair)
n_neighbors <- colPair(spe) %>% as.data.frame %>% group_by(from) %>% dplyr::count() %>% arrange(desc(n))
spe$n_neighbors <- n_neighbors$n[match(seq_along(colnames(spe)),n_neighbors$from)]
spe$n_neighbors <- spe$n_neighbors %>% replace_na(0)

# Select spatial features and average over celltypes
spatial <- colData(spe) %>% as.data.frame %>% select(area,celltype,n_neighbors)
spatial <- spatial %>% select(-celltype) %>% aggregate(by = list(celltype = spatial$celltype), FUN = mean) %>% column_to_rownames("celltype")

# Create HeatmapAnnotation object
ha_spatial <- HeatmapAnnotation(
    area = spatial$area,
    n_neighbors = spatial$n_neighbors,
    border = TRUE,
    gap = unit(1,"mm"),
    which = "row")


### 3. Plot rich heatmap ###

# Create HeatmapList object
h <- Heatmap(t(assay(celltype_mean, "exprs")),
        column_title = "type_markers",
        col = col_exprs,
        name= "mean exprs",
        show_row_names = TRUE, 
        show_column_names = TRUE)+
    Heatmap(t(assay(cellstate_mean, "exprs")),
        column_title = "state_markers",
        col = col_exprs,
        name= "mean exprs",
        show_row_names = TRUE,
        show_column_names = TRUE)+
    ha_anno+
    ha_spatial+
    ha_meta

# Add customized legend for anno_barplot()
lgd <- Legend(title = "indication", at = colnames(indication), legend_gp = gpar(fill = metadata(spe)$color_vectors$indication))
             
# Plot
draw(h,annotation_legend_list = list(lgd))
```

## Session Info

```{r, echo = FALSE}
sessionInfo()
```
