# Single cell visualization {#single-cell-visualization}

The following section describes how to ...

We will first read in the previously processed data and randomly select 3 images
for visualization purposes.

## Overview

## Recycled code from previous chapters 

o visualize single-cell expression in form of a
heatmap. Here, we sub-sample the dataset to 2000 cells for visualization
purposes and overlay the cancer type from which the cells were extracted.

```{r segmentation-heatmap, message=FALSE, fig.height=7}
library(dittoSeq)
library(viridis)
cur_cells <- sample(seq_len(ncol(spe)), 2000)

dittoHeatmap(spe[,cur_cells], genes = rownames(spe)[rowData(spe)$use_channel],
             assay = "exprs", cluster_cols = TRUE, scale = "none",
             heatmap.colors = viridis(100), annot.by = "indication",
             annotation_colors = list(indication = metadata(spe)$color_vectors$indication))
```


Finally, it can be beneficial to visualize the mean marker expression per image
to identify images with outlying cell type compositions. This check does not
indicate image quality _per se_ but can highlight biological differences. Here,
we will use the `aggregateAcrossCells` function of the 
`r BiocStyle::Biocpkg("scuttle")` package to compute the mean expression per 
image. For visualization purposes, we again `asinh` transform the mean expression
values.

```{r mean-expression-per-image, message=FALSE, fig.height=7}
library(scuttle)

image_mean <- aggregateAcrossCells(spe, 
                                   ids = spe$sample_id, 
                                   statistics="mean",
                                   use.assay.type = "counts")
assay(image_mean, "exprs") <- asinh(counts(image_mean))

dittoHeatmap(image_mean, genes = rownames(spe)[rowData(spe)$use_channel],
             assay = "exprs", cluster_cols = TRUE, scale = "none",
             heatmap.colors = viridis(100), 
             annot.by = c("indication", "patient_id", "ROI"),
             annotation_colors = list(indication = metadata(spe)$color_vectors$indication,
                                      patient_id = metadata(spe)$color_vectors$patient_id,
                                      ROI = metadata(spe)$color_vectors$ROI),
             show_colnames = TRUE)
```


The data presented here were stained on individual slides. Also, samples were
pre-processed in different locations. These (and other) technical aspects can
induce staining differences between samples or batches of samples. Observing
potential staining differences can be crucial to assess data quality.
We will use ridgeline visualizations to check differences in staining patterns:

```{r ridges, message=FALSE, fig.width=7, fig.height=25}
multi_dittoPlot(spe, vars = rownames(spe)[rowData(spe)$use_channel],
               group.by = "patient_id", plots = c("ridgeplot"), 
               assay = "exprs", 
               color.panel = metadata(spe)$color_vectors$patient_id)
```

Visualization of the low-dimensional embedding facilitates assessment of 
potential "batch effects". The `dittoDimPlot`
function allows flexible visualization. It returns `ggplot` objects which
can be further modified.

```{r visualizing-dimred, message=FALSE}
library(patchwork)

# visualize patient id 
p1 <- dittoDimPlot(spe, var = "patient_id", reduction.use = "UMAP", size = 0.2) + 
    scale_color_manual(values = metadata(spe)$color_vectors$patient_id) +
    ggtitle("Patient ID on UMAP")
p2 <- dittoDimPlot(spe, var = "patient_id", reduction.use = "TSNE", size = 0.2) + 
    scale_color_manual(values = metadata(spe)$color_vectors$patient_id) +
    ggtitle("Patient ID on TSNE")

# visualize region of interest id
p3 <- dittoDimPlot(spe, var = "ROI", reduction.use = "UMAP", size = 0.2) + 
    scale_color_manual(values = metadata(spe)$color_vectors$ROI) +
    ggtitle("ROI ID on UMAP")
p4 <- dittoDimPlot(spe, var = "ROI", reduction.use = "TSNE", size = 0.2) + 
    scale_color_manual(values = metadata(spe)$color_vectors$ROI) +
    ggtitle("ROI ID on TSNE")

(p1 + p2) / (p3 + p4)

# visualize marker expression
p1 <- dittoDimPlot(spe, var = "Ecad", reduction.use = "UMAP", 
                   assay = "exprs", size = 0.2) +
    scale_color_viridis(name = "Ecad") +
    ggtitle("E-Cadherin expression on UMAP")
p2 <- dittoDimPlot(spe, var = "CD45RO", reduction.use = "UMAP", 
                   assay = "exprs", size = 0.2) +
    scale_color_viridis(name = "CD45RO") +
    ggtitle("CD45RO expression on UMAP")
p3 <- dittoDimPlot(spe, var = "Ecad", reduction.use = "TSNE", 
                   assay = "exprs", size = 0.2) +
    scale_color_viridis(name = "Ecad") +
    ggtitle("Ecad expression on TSNE")
p4 <- dittoDimPlot(spe, var = "CD45RO", reduction.use = "TSNE", 
                   assay = "exprs", size = 0.2) +
    scale_color_viridis(name = "CD45RO") +
    ggtitle("CD45RO expression on TSNE")

(p1 + p2) / (p3 + p4)
```

## Read in the data

We will first read in the data processed in previous sections:

```{r read-data, message=FALSE}
spe <- readRDS("data/spe.rds")
```
## Session Info

<details>
   <summary>SessionInfo</summary>
   
```{r, echo = FALSE}
sessionInfo()
```
</details>
